### 2021-05-06 papers/assembly/I/main.tex
[papers] Add assembly theory I

\documentclass[aps,prd,onecolumn,nofootinbib,letterpaper,preprintnumbers,superscriptaddress,eqsecnum]{revtex4}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{dsfont}
\usepackage{tikz-cd}
\usepackage{cleveref}
\usepackage{txfonts}
\usepackage{tikz, tikz-cd}
\usepackage{subfigure}
\usepackage[version=4]{mhchem}
\usetikzlibrary{backgrounds,circuits,circuits.ee.IEC,shapes,fit,matrix}

\tikzstyle{simple}=[-,line width=2.000]
\tikzstyle{arrow}=[-,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.100]
\pgfdeclarelayer{edgelayer}
\pgfdeclarelayer{nodelayer}
\pgfsetlayers{edgelayer,nodelayer,main}

\tikzstyle{none}=[inner sep=0pt]

\definecolor{lblue}{rgb}{0,250,255}

\tikzstyle{site}=[circle, fill=lblue!20, draw=black, scale=1, minimum size=1cm]
\tikzstyle{catalyst}=[circle, fill=lblue!20, draw=red, scale=1, minimum size=1cm]
\tikzstyle{transition}=[rectangle, fill=gray!30, draw=black, scale=1, minimum size=1cm]
\tikzstyle{morphism}=[rectangle, fill=gray!30, draw=black, scale=1, minimum size=1cm]

\tikzstyle{empty}=[circle,fill=none, draw=none]
\tikzstyle{inputdot}=[circle,fill=black,draw=black, scale=.5]
\tikzstyle{dot}=[circle,fill=black,draw=black]
\tikzstyle{bounding}=[circle,dashed, fill=none,draw=black, scale=9.00]
\tikzstyle{simple}=[-,draw=black,line width=1.000]
\tikzstyle{inarrow}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.000]
\tikzstyle{tick}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\draw (0,-0.1) -- (0,0.1);}},line width=1.000]
\tikzstyle{inputarrow}=[->,draw=black, shorten >=.05cm]
\tikzstyle{sitemap}=[->, dashed, draw=red, ultra thick, shorten >=.05cm]
\tikzstyle{transitionmap}=[->, dashed, draw=blue, ultra thick, shorten >=.05cm]

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{theorem}{Theorem}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newcommand{\upset}[1]{#1\!\!\uparrow}
\newcommand{\downset}[1]{#1\!\!\downarrow}
\newcommand{\N}{\mathbb{N}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\Min}[1]{\min{(#1)}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\powerset}{\mathcal{P}}

\newcommand{\TODO}{\noindent\textbf{TODO:}~}

\begin{document}

\title{Supplementary Information: Quantifying the pathways to life using assembly spaces}
\author{Stuart M. Marshall}
\author{Douglas G. Moore}
\author{Alastair R. G. Murray}
\author{Sara I. Walker}
\author{Leroy Cronin}

\maketitle

\section{Introduction}

This formalism arose as a means of rigorously describing the ``simplest" way of assembling a given object by combining basic building blocks.
With this in mind, we consider a universe of objects together with transitions representing ways in which objects can be combined, mutated or disassembled to yield other objects.
In this setting, the concrete rules or laws relating the transitions with the objects is largely neglected herein, though they are certainly necessary for initially constructing the space for consideration.
We quickly come to the conclusion that a Petri network is appropriate when we consider this kind of process in general, though with specific modifications to allow the types of questions in which we are interested to be well defined.
As such, the fundamental mathematical structure we define and explore herein, referred to as an assembly space, can be described as a sourceless, sinkless Petri net with a chosen basis.
The details of this description will, of course, be made precise below.
With assembly spaces defined, we are then able to define an assembly index for each object in the space, relative to the chosen basis, which characterizes how directly that object can be assembled.
Further, we prove several axioms relating to method of bounding the assembly index for a given object and algorithms for computing or approximating it.

\section{Petri Nets}

The first task we are faced with is how to formally represent the substrates and products of some transition.
We can look to introductory Chemistry for inspiration.
When we consider a process like
\begin{equation*}
    \ce{2H_2} + \ce{O_2} \rightarrow \ce{2H_2O}
\end{equation*}
we are expressing the idea that some chemical process (transition) consumes twice as much $\ce{H_2}$ as $\ce{O_2}$ and yields $\ce{H_2O}$.
The apparent multiplication ($\ce{2H_2}$) and addition ($\ce{2H_2} + \ce{O_}$) are simply formal constructs use to encode the stoichiometry of the reaction.
The addition here is commutative; we could have written $\ce{O_2} + \ce{2H_2}$, and it would have meant precisely the same thing.

We take a similar approach herein, though mathematically explicit. Let $X$ be a set. This may be, for example, a set of types of molecules $\{\ce{H_2}, \ce{O_2}, \ce{H_2O}\}$ or a set of kinds of building materials and products $\{\textrm{wood}, \textrm{glass pane}, \textrm{nail}, \textrm{picture frame}\}$.
We can then construct formal linear combinations of the elements of $X$ where the coefficients are natural numbers, e.g. $\ce{2H_2} + \ce{O_2}$ or $4\textrm{wood} + \textrm{glass pane} + 8\textrm{nail}$, and only finitely many coefficients are nonzero.

The collection of such formal linear combinations is referred to as the \textit{free commutative monoid} on $X$ over the natural number $\N$, and is typically denoted $\N[X]$.
The set $X$, in this context, is referred to as the set of generators of $\N[X]$.
An element $a \in \N[X]$ can be written as
\begin{equation*}
    a = \sum_{x \in X} a_x x
\end{equation*}
with natural number coefficients $a_x$, only finitely many non-zero.
This construction naturally has a monoidal structure, hence the name.
You can add such linear combinations to gether, e.g. $\ce{H_2} + (\ce{H_2} + \ce{O_2}) = \ce{2H_2} + \ce{O_2}$, and there exists an identity element $0$ such that $0 + a = a + 0 = a$ for all $a \in \N[X]$.
It is important to stress at this point that the linear combinations do not need to ``make sense'', at least not yet.
Taking the molecular example, $\ce{H_2}$, $\ce{7H_2} + \ce{O_2}$ and $\ce{H_2} + \ce{H_2O} + \ce{O_2}$ are permissible linear combinations and so are elements of $\N[X]$.
This does not mean that we will, in practice, consider all of them.
Restrictions on which linear combinations are consider will come into the picture when we introduce transitions.

For some of the definitions we will present in coming sections, it will be useful to denote the subset of generators appearing in a given linear combinations. That is for a given element $a \in \N[X]$, the subset generators with non-zero coefficients in $a$, denoted $\pi : \N[X] \rightarrow \powerset{X}$ where 
\begin{equation*}
    \displaystyle \sum_{x \in X} a_x x \mapsto \{ x \in X ~|~ a_x \ne 0 \}.
\end{equation*}
To clarify this point, $\pi(\ce{2H2} + \ce{O_2}) = \{\ce{H_2}, \ce{O_2}\}$.

Before departing from the topic of the free commutative monoid, we want to note that while it may seem that we are being overly formalistic, we gain some power by taking this approach.
Most importantly, we can consider what happens if you ``map'' one set of objects into another. 
As a concrete example, you could imagine mapping each of the molecules $\ce{H_2}$, $\ce{O_2}$ and $\ce{H_2O}$ to the number of Hydrogen atoms they contain, i.e. $2$, $0$, and $2$.
\textbf{I don't like that example very much, but it's good enough for the moment.}
This mapping process can be ``lifted'' into a map on the linear combinations by distributing the map over addition, so that $\ce{H_2} + \ce{O_2}$ maps to $2 + 0 = 2$. More formally, any function between sets $f : X \rightarrow Y$ can be uniquely extended to a function $\N[f] : \N[X] \rightarrow \N[Y]$ such that
\begin{equation*}
    \sum_{x \in X} a_x x \mapsto \sum_{x \in X} a_x f(x).
\end{equation*}
The value of doing this is that it will allow us to coherently define a map between assembly spaces, to be defined, which will then be useful for proving certain theorems regarding bounds on quantities of interest.

\begin{definition}\label{def:petri}
    A \textbf{Petri net} is a $P$ consisting of
    \begin{itemize}
        \item a set of \textit{sites}, $S(P)$
        \item a set of \textit{transitions}, $T(P)$
        \item a pair of maps $\begin{tikzcd}
                T(P)
                \arrow[r, shift left = 1, "\sigma_P"]
                \arrow[r, shift right = 1, "\tau_P", swap]
                &
                \N[S(P)]
        \end{tikzcd}$.
    \end{itemize}
    We call $\sigma_P$ the source map and $\tau_Q$ the target map.
    An element of $\N[S(P)]$ is called a \textbf{marking} of the Petri net.
    Where context is unambiguous we may simply write $\sigma$ and $\tau$, but will generally retain the $T(P)$ and $S(P)$ notation.
\end{definition}

Consider, for example, the Petri $P$ net described by $S(P) = \{ A, B, C, AA, AB, AAAB \}$ and $T(P) = \{ \alpha, \beta, \gamma, \delta \}$ with source and target maps:

\begin{align*}
    \sigma(\alpha) &= 2A           & \tau(\alpha) &= AA         \\
    \sigma(\beta)  &= A + B        & \tau(\beta)  &= AB         \\
    \sigma(\gamma) &= AA + AB + C  & \tau(\gamma) &= AAAB + C   \\
    \sigma(\delta) &= AAAB         & \tau(\delta) &= A + AA + B.
\end{align*}

A natural way of graphically representing this $P$ is with a bipartite multigraph:

\begin{figure}[!h]
    \scalebox{0.6}{
    \begin{tikzpicture}
        \begin{pgfonlayer}{nodelayer}
            \node [style=site] (A) at (0, 0.8) {$A$};
            \node [style=site] (B) at (0, -0.8) {$B$};
            \node [style=site] (C) at (6, -1.6) {$C$};
            \node [style=site] (AA) at (4, 0.8) {$AA$};
            \node [style=site] (AB) at (4, -0.8) {$AB$};
            \node [style=site] (AAAB) at (8, 0) {$AAAB$};
            \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
            \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
            \node [style=transition] (tau3) at (6, 0) {$\gamma$};
            \node [style=transition] (tau4) at (10, 0) {$\delta$};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
            \draw [style=inarrow, bend right=15] (A) to (tau1);
            \draw [style=inarrow, bend left=15] (A) to (tau1);
            \draw [style=inarrow, bend right=15] (A) to (tau2);
            \draw [style=inarrow] (tau1) to (AA);
            \draw [style=inarrow] (B) to (tau2);
            \draw [style=inarrow] (tau2) to (AB);
            \draw [style=inarrow] (AA) to (tau3);
            \draw [style=inarrow] (AB) to (tau3);
            \draw [style=inarrow, bend left=30] (C) to (tau3);
            \draw [style=inarrow] (tau3) to (AAAB);
            \draw [style=inarrow, bend left=30] (tau3) to (C);
            \draw [style=inarrow] (AAAB) to (tau4);
            \draw [style=inarrow, bend right=30] (tau4) to (A);
            \draw [style=inarrow, bend right=30] (tau4) to (AA);
            \draw [style=inarrow, bend left=40] (tau4) to (B);
        \end{pgfonlayer}
    \end{tikzpicture}
}
\end{figure}

\begin{definition}\label{def:petri-map}
    A \textbf{Petri net morphism} from a Petri net $P$ to a Petri net $Q$, denoted $f : P \rightarrow Q$, consisists of a pair of functions $T(f) : T(P) \rightarrow T(Q)$ and $S(f): S(P) \rightarrow S(Q))$ such that the following diagrams commute:
    \begin{equation*}
        \begin{tikzcd}
            T(P)
            \arrow[r, "\sigma_P"]
            \arrow[d, "T(f)", swap]
            &
            \N[S(P)]
            \arrow[d, "\N \lbrack S(f) \rbrack"]
            \\
            T(Q)
            \arrow[r, "\sigma_Q"]
            &
            \N[S(Q)]
        \end{tikzcd}
        \quad
        \textrm{and}
        \quad
        \begin{tikzcd}
            T(P)
            \arrow[r, "\tau_P"]
            \arrow[d, "T(f)", swap]
            &
            \N[S(P)]
            \arrow[d, "\N \lbrack S(f) \rbrack"]
            \\
            T(Q)
            \arrow[r, "\tau_Q"]
            &
            \N[S(Q)].
        \end{tikzcd}
    \end{equation*}
    When possible, we will abuse notation and write $f(s)$ or $f(t)$ for sites $s \in S(P)$ and transitions $t \in T(P)$, in lieu of the more verbose $S(f)(s)$ and $T(f)(t)$.
\end{definition}

\begin{align*}
    f(\alpha) &= f(\beta) = \chi    & g&(A)    = g(B) = X \\
    f(\gamma) &= \psi               & g&(AA)   = g(AB) = g(C) = Y \\
    f(\delta) &= \omega             & g&(AAAB) = Z
\end{align*}

\begin{figure}[!h]
    \scalebox{0.6}{
    \begin{tikzpicture}
        \begin{pgfonlayer}{nodelayer}
            \node [style=site] (A) at (0, 0.8) {$A$};
            \node [style=site] (B) at (0, -0.8) {$B$};
            \node [style=site] (C) at (6, -1.6) {$C$};
            \node [style=site] (AA) at (4, 0.8) {$AA$};
            \node [style=site] (AB) at (4, -0.8) {$AB$};
            \node [style=site] (AAAB) at (8, 0) {$AAAB$};
            \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
            \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
            \node [style=transition] (tau3) at (6, 0) {$\gamma$};
            \node [style=transition] (tau4) at (10, 0) {$\delta$};

            \node [style=site] (W) at (-4, -6) {$W$};
            \node [style=site] (X) at (0, -6) {$X$};
            \node [style=site] (Y) at (4, -6) {$Y$};
            \node [style=site] (Z) at (8, -6) {$Z$};
            \node [style=transition] (tau5) at (-2, -6) {$\phi$};
            \node [style=transition] (tau6) at (2, -6) {$\chi$};
            \node [style=transition] (tau7) at (6, -6) {$\psi$};
            \node [style=transition] (tau8) at (10, -6) {$\omega$};

            \node [text=red, scale=2] (g) at (-1.5, -3) {$g$};
            \node [text=blue, scale=2] (f) at (0.5, -3) {$f$};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau1);
            \draw [style=inarrow, draw=gray!80, bend left=15] (A) to (tau1);
            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau2);
            \draw [style=inarrow, draw=gray!80] (tau1) to (AA);
            \draw [style=inarrow, draw=gray!80] (B) to (tau2);
            \draw [style=inarrow, draw=gray!80] (tau2) to (AB);
            \draw [style=inarrow, draw=gray!80] (AA) to (tau3);
            \draw [style=inarrow, draw=gray!80] (AB) to (tau3);
            \draw [style=inarrow, draw=gray!80, bend left=30] (C) to (tau3);
            \draw [style=inarrow, draw=gray!80] (tau3) to (AAAB);
            \draw [style=inarrow, draw=gray!80, bend left=30] (tau3) to (C);
            \draw [style=inarrow, draw=gray!80] (AAAB) to (tau4);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau4) to (A);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau4) to (AA);
            \draw [style=inarrow, draw=gray!80, bend left=40] (tau4) to (B);

            \draw [style=inarrow, draw=gray!80, bend left=15] (W) to (tau5);
            \draw [style=inarrow, draw=gray!80, bend right=15] (W) to (tau5);
            \draw [style=inarrow, draw=gray!80, bend left=15] (tau5) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=15] (tau5) to (X);
            \draw [style=inarrow, draw=gray!80, bend left=15] (X) to (tau6);
            \draw [style=inarrow, draw=gray!80, bend right=15] (X) to (tau6);
            \draw [style=inarrow, draw=gray!80] (tau6) to (Y);
            \draw [style=inarrow, draw=gray!80, bend left=20] (Y) to (tau7);
            \draw [style=inarrow, draw=gray!80] (Y) to (tau7);
            \draw [style=inarrow, draw=gray!80, bend right=20] (Y) to (tau7);
            \draw [style=inarrow, draw=gray!80] (tau7) to (Z);
            \draw [style=inarrow, draw=gray!80, bend left=50] (tau7.south) to (Y.south);
            \draw [style=inarrow, draw=gray!80] (Z) to (tau8);
            \draw [style=inarrow, draw=gray!80, bend left=30] (tau8) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (Y);

            \draw [style=sitemap, bend right=30] (A) to (X);
            \draw [style=sitemap, bend right=30] (B) to (X);
            \draw [style=sitemap, bend right=30] (AA) to (Y);
            \draw [style=sitemap, bend right=30] (AB) to (Y);
            \draw [style=sitemap, bend right=30] (C) to (Y);
            \draw [style=sitemap, bend right=30] (AAAB) to (Z);
            \draw [style=transitionmap, bend right=30] (tau1) to (tau6);
            \draw [style=transitionmap, bend right=30] (tau2) to (tau6);
            \draw [style=transitionmap, bend right=30] (tau3) to (tau7);
            \draw [style=transitionmap, bend right=30] (tau4) to (tau8);
        \end{pgfonlayer}
    \end{tikzpicture}
}
\end{figure}

\begin{definition}\label{def:subnet}
    % Let $P$ and $Q$ be Petri nets.
    % We say that $P$ is a \textbf{Petri subnet} of $Q$ when $T(P) \subseteq T(Q)$, $S(P) \subseteq S(Q)$, $\sigma_P = \sigma_Q|_{T(P)}$ and $\tau_P = \tau_Q|_{T(P)}$.
    Let $Q$ be a Petri net. A \textbf{Petri subnet} $P$ of $Q$ consists of
    \begin{itemize}
        \item a subset of sites of $Q$, denoted $S(P)$
        \item a subset of transitions of $Q$, denoted $T(P)$
        \item a pair of maps $\begin{tikzcd}
                T(P)
                \arrow[r, shift left = 1, "\sigma_P"]
                \arrow[r, shift right = 1, "\tau_P", swap]
                &
                \N[S(P)]
        \end{tikzcd}$.
    \end{itemize}
    such that $\sigma_P = \sigma_Q|_{T(P)}$ and $\tau_P = \tau_Q|_{T(P)}$.
\end{definition}

\begin{figure}[!h]
    \scalebox{0.6}{
    \begin{tikzpicture}
        \begin{pgfonlayer}{nodelayer}
            \node [style=site] (A) at (0, 0.8) {$A$};
            \node [style=site] (B) at (0, -0.8) {$B$};
            \node [style=site] (C) at (6, -1.6) {$C$};
            \node [style=site] (AA) at (4, 0.8) {$AA$};
            \node [style=site] (AB) at (4, -0.8) {$AB$};
            \node [style=site] (AAAB) at (8, 0) {$AAAB$};
            \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
            \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
            \node [style=transition] (tau3) at (6, 0) {$\gamma$};

            \node [style=site] (W) at (-4, -6) {$W$};
            \node [style=site, fill=green!20] (X) at (0, -6) {$X$};
            \node [style=site, fill=green!20] (Y) at (4, -6) {$Y$};
            \node [style=site, fill=green!20] (Z) at (8, -6) {$Z$};
            \node [style=transition] (tau5) at (-2, -6) {$\phi$};
            \node [style=transition, fill=yellow!20] (tau6) at (2, -6) {$\chi$};
            \node [style=transition, fill=yellow!20] (tau7) at (6, -6) {$\psi$};
            \node [style=transition] (tau8) at (10, -6) {$\omega$};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau1);
            \draw [style=inarrow, draw=gray!80, bend left=15] (A) to (tau1);
            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau2);
            \draw [style=inarrow, draw=gray!80] (tau1) to (AA);
            \draw [style=inarrow, draw=gray!80] (B) to (tau2);
            \draw [style=inarrow, draw=gray!80] (tau2) to (AB);
            \draw [style=inarrow, draw=gray!80] (AA) to (tau3);
            \draw [style=inarrow, draw=gray!80] (AB) to (tau3);
            \draw [style=inarrow, draw=gray!80, bend left=30] (C) to (tau3);
            \draw [style=inarrow, draw=gray!80] (tau3) to (AAAB);
            \draw [style=inarrow, draw=gray!80, bend left=30] (tau3) to (C);

            \draw [style=inarrow, draw=gray!80, bend left=15] (W) to (tau5);
            \draw [style=inarrow, draw=gray!80, bend right=15] (W) to (tau5);
            \draw [style=inarrow, draw=gray!80, bend left=15] (tau5) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=15] (tau5) to (X);
            \draw [style=inarrow, draw=red, bend left=15] (X) to (tau6);
            \draw [style=inarrow, draw=red, bend right=15] (X) to (tau6);
            \draw [style=inarrow, draw=red] (tau6) to (Y);
            \draw [style=inarrow, draw=red, bend left=20] (Y) to (tau7);
            \draw [style=inarrow, draw=red] (Y) to (tau7);
            \draw [style=inarrow, draw=red, bend right=20] (Y) to (tau7);
            \draw [style=inarrow, draw=red] (tau7) to (Z);
            \draw [style=inarrow, draw=red, bend left=50] (tau7.south) to (Y.south);
            \draw [style=inarrow, draw=gray!80] (Z) to (tau8);
            \draw [style=inarrow, draw=gray!80, bend left=30] (tau8) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (Y);

            \draw [style=sitemap, bend right=30, shorten >=2mm] (A) to (X);
            \draw [style=sitemap, bend right=30, shorten >=2mm] (B) to (X);
            \draw [style=sitemap, bend right=30, shorten >=2mm] (AA) to (Y);
            \draw [style=sitemap, bend right=30, shorten >=2mm] (AB) to (Y);
            \draw [style=sitemap, bend right=30, shorten >=2mm] (C) to (Y);
            \draw [style=sitemap, bend right=30, shorten >=2mm] (AAAB) to (Z);
            \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau1) to (tau6);
            \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau2) to (tau6);
            \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau3) to (tau7);
        \end{pgfonlayer}
    \end{tikzpicture}
}
\end{figure}

For a Petri net morphism $f : P \rightarrow Q$, the image $f(P)$ in $Q$ is a Petri subnet with source and target maps $\sigma_{f(P)}$ and $\tau_{f(P)}$ defined by restriction of $\sigma_Q$ and $\tau_Q$, respectively.
Similarly, the preimage of a Petri subnet of $Q$ is a Petri subnet of $P$ with source and target maps defined by restriction of $\sigma_P$ and $\tau_P$.

\begin{definition}\label{def:source-sink}
    Let $P$ be a Petri net and let $t$ be a transition.
    We say that $t$ is a \textbf{source} if $\sigma(t) = 0$, and is a \textbf{sink} if $\tau(t) = 0$.
    $P$ is said to be \textbf{sourceless} if it has no sources.
    Similarly, $P$ is \textbf{sinkless} if it has no sinks.
\end{definition}

It follows immediately from the definition of a Petri map that the image of a sourceless Petri net is sourceless, otherwise the $\sigma$-diagram would not commute.
Similarly, the image of a sinkless Petri net is sinkless.

\begin{figure}[!h]
    \scalebox{0.6}{
    \begin{tikzpicture}
        \begin{pgfonlayer}{nodelayer}
            \node [style=site] (A) at (2, 0.8) {$A$};
            \node [style=site] (B) at (2, -0.8) {$B$};
            \node [style=transition] (tau1) at (0, 0) {$\alpha$};
            \node [style=transition] (tau2) at (4, 0) {$\beta$};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
            \draw [style=inarrow, bend left=15] (tau1) to (A);
            \draw [style=inarrow, bend right=15] (tau1) to (B);
            \draw [style=inarrow, bend left=15] (A) to (tau2);
            \draw [style=inarrow, bend right=15] (B) to (tau2);
        \end{pgfonlayer}
    \end{tikzpicture}
}
\end{figure}

\begin{definition}\label{def:pathway}
    If $P$ is a Petri net, a \textbf{pathway} $\gamma = t_n \ldots t_1$ in $P$ of length $n \ge 1$ is a sequence of transitions $t_i \in T$ such that $\tau(t_i) \ne 0$, $\sigma(t_i) \ne 0$, $m_{i} + \tau(t_i) = n_{i+1} + \sigma(t_{i+1})$ with $\sigma(t_{i+1}) \ne m_{i}$ and $\tau(t_{i+1}) \ne n_{i+1}$. We write $t \in \gamma$ to denote that the transition $t$ appears in the pathway $\gamma$.
\end{definition}

\begin{figure}[!h]
    \scalebox{0.6}{
    \begin{tikzpicture}
        \begin{pgfonlayer}{nodelayer}
            \node [style=site] (A) at (0, 0.8) {$A$};
            \node [style=site] (B) at (0, -0.8) {$B$};
            \node [style=site] (C) at (6, -1.6) {$C$};
            \node [style=site] (AA) at (4, 0.8) {$AA$};
            \node [style=site] (AB) at (4, -0.8) {$AB$};
            \node [style=site] (AAAB) at (8, 0) {$AAAB$};
            \node [style=transition, fill=green!20] (tau1) at (2, 0.8) {$\alpha$};
            \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
            \node [style=transition, fill=green!20] (tau3) at (6, 0) {$\gamma$};
            \node [style=transition] (tau4) at (10, 0) {$\delta$};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
            \draw [style=inarrow, bend right=15] (A) to (tau1);
            \draw [style=inarrow, bend left=15] (A) to (tau1);
            \draw [style=inarrow, bend right=15] (A) to (tau2);
            \draw [style=inarrow] (tau1) to (AA);
            \draw [style=inarrow] (B) to (tau2);
            \draw [style=inarrow] (tau2) to (AB);
            \draw [style=inarrow] (AA) to (tau3);
            \draw [style=inarrow] (AB) to (tau3);
            \draw [style=inarrow, bend left=30] (C) to (tau3);
            \draw [style=inarrow] (tau3) to (AAAB);
            \draw [style=inarrow, bend left=30] (tau3) to (C);
            \draw [style=inarrow] (AAAB) to (tau4);
            \draw [style=inarrow, bend right=30] (tau4) to (A);
            \draw [style=inarrow, bend right=30] (tau4) to (AA);
            \draw [style=inarrow, bend left=40] (tau4) to (B);
        \end{pgfonlayer}
    \end{tikzpicture}
}
\end{figure}

\begin{definition}\label{def:pathway-connected}
    Let $P$ be a Petri net and $x,y \in S(P)$.
    We say that $x$ is \textbf{pathway connected to} $y$ if and only if there exists a pathway $\gamma = t_n \ldots t_1$ such that $\sigma(t_1) = x + m$ and $\tau(t_n) = y + n$ for some $m, n \in \N[S(P)]$.
    The set of all pathways in $P$ from $x$ to $y$ is denoted $\Gamma_x^y$.
    We denote the set of all pathways in $P$ starting from $x$ as $\Gamma_x = \bigcup_{y \in S(P)} \Gamma_x^y$, and all pathways terminating at $y$ as $\Gamma^y = \bigcup_{x \in S(P)} \Gamma_x^y$.
\end{definition}

\begin{lemma}\label{lem:image-of-pathways}
    Let $f: P \rightarrow Q$ be a Petri net morphism and let $x, y \in S(P)$ be pathway connected in $P$.
    Then $f(x)$ and $f(y)$ are pathway connected in $f(P)$.
\end{lemma}
\begin{proof}
    Let $\gamma = t_n \ldots t_1$ be a pathway from $x$ to $y$.
    Given that $\sigma_P(t_i) \ne 0$ and $\tau_P(t_i) \ne 0$, we know that $\sigma_{f(P)} \ne 0$ and $\tau_{f(P)} \ne 0$.
    Since $\sigma_P(t_1) = x + m$, $\sigma_{f(P)}(f(x)) = f(x) + m'$ for some $m' \in \N[S(f(P))]$; similarly, $\tau_{f(P)}(f(y)) = f(y) + n'$ for some $n' \in \N[S(f(P))]$.

    Now, consider two transitions $t_i$ and $t_{i+1}$ in $\gamma$.
    We know then that there exist $m, n \in \N[S(P)]$ such that $m + \tau_P(t_i) = n + \sigma_P(t_{i+1})$ with $m \ne \sigma_P(t_{i+1})$ and $n \ne \tau_P(t_i)$.
    We can then apply $\N[S(f)]$ to each side to yield
    \begin{equation*}
        \N[S(f)](m) + \N[S(f)](\tau_P(t_i)) = \N[S(f)](n) + \N[S(f)](\sigma_P(t_{i+1})).
    \end{equation*}
    Per the commutativity relations imposed by the assembly map,
    \begin{equation*}
        \N[S(f)](\tau_P(t_i)) = \tau_{f(P)}(f(t_i)))
        \quad\textrm{and}\quad
        \N[S(f)](\sigma_P(t_{i+1})) = \sigma_{f(P)}(f(t_{i+1})).
    \end{equation*}
    So, there exist an $m', n' \in \N[S(f(P))]$ such that $m + \tau_{f(P)}(f(t_i)) = n + \sigma_{f(P)}(f(t_{i+1}))$, namely $m' = \N[S(f)](m)$ and $n' = \N[S(f)](n)$.
    Finally, we know that $m' \ne \sigma_{f(P)}(f(t_{i+1}))$ as otherwise $m = \sigma_P(t_{i+1})$, and similarly $n' \ne \tau_{f(P)}(f(t_i))$.

    This shows that a pathway exists from $f(x)$ to $f(y)$, so $f(x)$ and $f(y)$ are pathway connected.
\end{proof}

\begin{definition}\label{def:site-completion}
    Let $P$ be a petri net and let $X \subseteq T(P)$.
    The \textbf{site completion} of $X$ in $P$, denoted $X^*$ is the Petri net defined by $T(X^*) = X$, $S(X^*) = \pi(X)$, $\sigma_{X^*} = \sigma_P|_{X^*}$ and $\tau_{X^*} = \tau_P|_{X^*}$.
\end{definition}

\begin{definition}\label{def:upper-lower-subnet}
    Let $P$ be a Petri net and let $X \subseteq S(P)$.
    The \textbf{upper subnet} of $X$ in $P$, denoted $\upset{X}$, consists of transitions $T(\upset{X}) = \bigcup_{x \in X}\{t \in \gamma ~|~ \gamma \in \Gamma_x\}$, sites $S(\upset{X}) = X \cup S(T(\upset{X})^*)$, $\sigma_{X\uparrow} = \sigma_P|_{T(X\uparrow)^*}$ and $\tau_{X\uparrow} = \tau_P|_{T(X\uparrow)^*}$.
    Similarly, the \textbf{lower subnet} of $X$ in $P$, denoted $\downset{X}$, consists of transitions $T(\downset{X}) = \{t \in \gamma ~|~ \gamma \in \Gamma_X\}$, sites $S(\downset{X}) = X \cup S(T(\downset{X})^*)$, $\sigma' = \sigma|_{T(X\downarrow)^*}$ and $\tau = \tau|_{T(X\downarrow)^*}$.
    If $x$ is an element $x \in P$, we write $\upset{x} = \upset{\{x\}}$ and $\downset{x} = \downset{\{x\}}$.
\end{definition}

\begin{definition}\label{def:minimal}
    Let $P$ be a Petri net. A site $y$ is \textbf{minimal} in $P$ if $\Gamma_x^y = \emptyset$ for all sites $y \ne x$ in $P$.
    The set of all minimal sites of $P$ is denoted $\Min{P}$.
\end{definition}

\begin{definition}\label{def:basis}
    Let $P$ be a Petri net and let $\B$ be a non-empty subset of sites of $P$.
    We say that $\B$ is a \textbf{basis} of $P$ if $P = \upset{\B}$ such that if $U \subseteq \B$ with $P = \upset{U}$ then $U = \B$.
\end{definition}

\begin{lemma}
    Let $P$ be a Petri net. For any basis $\B$ of $P$, $\Min{P} \subseteq \B$.
    Furthermore, if $\Min{P}$ is a basis of $P$, then $\Min{P}$ is the unique basis of $P$.
\end{lemma}
\begin{proof}
    Let $x \in \Min{P}$ and $\B$ be a basis of $P$, then either there exists a $y \in \B$ such that $\Gamma_y^x$ is non-empty, or $x \in \B$.
    However, $\Gamma^x$ is empty by definition of $\Min{P}$, so we have that $x \in B$.
    Since the choice of $x$ was arbitrary, every element of $\Min{P}$ is in the basis $\B$ and thus $\min{P} \subseteq \B$.
    Furthermore, suppose that $P = \upset{\Min{P}}$.
    Then $\B = \Min{P}$, otherwise $\B$ would not be a basis, by definition.
    Since $\B$ was chosen arbitrarily, this holds for every choice of $\B$ and as such $\Min{P}$ is a unqiue basis for $P$.
\end{proof}

\begin{lemma}\label{lem:image-basis}
    Let $P$ be a Petri net with basis $\B$ and let $f : A \rightarrow B$ be a Petri net morphism.
    Then $f(\B)$ is a basis for $f(P)$.
\end{lemma}
\begin{proof}
    Certainly $f(\B)$ is nonempty as $\B$ is nonempty, and of course $f(P)$ must be in the upper set of $f(\B)$.
    This follows immediately from \cref{lem:image-of-pathways} since every site in $P$ is pathway connected to a site in $\B$.
    Now let $U \subset f(\B)$ such that $f(P) = \upset{U}$.
    \TODO: Show that $f(\B)$ is minimal.
\end{proof}

\section{Assembly Spaces, Subspaces and Maps}

\begin{definition}\label{def:assembly-space}
    An \textbf{assembly space} $(A, \B_A)$ is a sourceless and sinkless Petri net with basis $\B_A$.
    Were possible, we will simply write $A$ to denote an assembly space $(A, \B_A)$.
\end{definition}

\begin{definition}\label{def:assembly-subspace}
    Let $A$ and $A'$ be assembly spaces.
    $A'$ is an \textbf{assembly subspace} of $A$ if $A'$ is a Petri subnet of $A$.
    This relationship is denoted $A' \subseteq A$.
\end{definition}

\begin{definition}\label{def:rooted}
    Let $(A', \B_{A'})$ be an assembly subspace of $(A, \B_A)$.
    We say that $A'$ is rooted in $A$ if $\B_{A'} \subseteq \B_A$.
\end{definition}

\begin{lemma}\label{lem:lower-is-rooted}
    Let $A$ be an assembly space and let $x \in S(A)$.
    Then $\downset{x}$ with basis $\B_A \cap S(\downset{x})$ is a rooted assembly subspace of $A$.
\end{lemma}
\begin{proof}
    By construction, $\downset{x}$ is a Petri subnet of $A$.
    Since $A$ is an assembly space, it is sourceless and sinkless; and given that $\downset{x}$ is a site-completion, $\downset{x}$ is also sourceless and sinkless.
    This gives us that $\downset{x}$ is an assembly subspace of $A$.
    We need only show that $\B_{x\downarrow} = \B_A \cap S(\downset{x}) \subseteq \B_A$ is a basis of $\downset{x}$.
    First, $\B_{x\downarrow}$ is necessarily nonempty since $\B_A$ is a basis in $A$.
    Further, we know that every site in $\downset{x}$ is above $\B_A \cap S(\downset{x})$ since, again $\B_A$ is a basis in $A$.
    \TODO: Show that $\B_{x\downarrow}$ is minimal.
\end{proof}

\begin{definition}\label{def:assembly-map}
    Let $A$ and $B$ be assembly spaces.
    An \textbf{assembly map} is simply a Petri net map $f: A \rightarrow B$ between assembly spaces.
\end{definition}

\begin{theorem}\label{lem:assembly-image-is-subspace}
    If $f : A \rightarrow B$ is an assembly map between assembly spaces $A$ and $B$, then $f(A)$ is an assembly subspace of $B$.
\end{theorem}
\begin{proof}
    This follows directly from the fact that the image of a Petri net morphism is a Petri subnet, and that the image of a sourceless, sinkless Petri net is itself sourceless and sinkless.
\end{proof}

\begin{theorem}\label{thm:rooted-image}
    Let $A$ be an assembly space, $Z \subseteq A$ a rooted assembly subspace, and $f : A \rightarrow B$ an assembly map.
    Then $(f(Z), S(f)(\B_Z))$ is rooted in $(f(A), S(f)(\B_A)$.
\end{theorem}
\begin{proof}
    First, $f(Z)$ is certainly an assembly subspace of $f(A)$ as we can view $f|_Z$ as an assembly map, and thus \cref{lem:assembly-image-is-subspace} applies.
    To see that $f(Z)$ is rooted, we first note that $S(f)(\B_Z)$ and $S(f)(\B_A)$ are bases for $f(Z)$ and $f(A)$, respectively.
    Further, since $Z$ is rooted in $A$, then $\B_Z \subset \B_A$, so $f(\B_Z) \subseteq f(\B_A)$.
\end{proof}

\section{The Assembly Index}

\begin{definition}\label{def:size}
    Let $A$ be an assembly space.
    The \textbf{size} of $A$ is the cardinality of $T(A)$, denoted $|A|$.
\end{definition}

\begin{definition}\label{def:finiteness}
    Let $A$ be an assembly space and let $x$ be a site in $A$.
    We say that $x$ is \textbf{finite} in $A$ if $\downset{x}$ in $A$ has finite size.
\end{definition}

\begin{definition}\label{def:index}
    Let $A$ be an assembly space and let $x$ be a finite site in $A$.
    The \textbf{assembly index} of $x$ is the minimal size of all rooted assembly subspaces of $A$ containing $x$, and is denoted $c_A(x)$.
    This can be written $c(x)$ when the relevant assembly space is clear from context.
\end{definition}

\subsection{Bounds on the Assembly Index}

\begin{theorem}\label{cor:subspace-index-upper-bound}
    Let $(A, \B_A)$ be an assembly space and let $(B, \B_A)$ be a rooted assembly subspace of $A$.
    For every finite $b \in S(B)$, the assembly index of $b$ in $B$ is at least the assembly index of $b$ in $A$.
    That is, $c_B(b) \ge c_A(b)$ for all $b \in S(B)$
\end{theorem}
\begin{proof}
    We need only show that $c_A(b)$ cannot be greater than $c_B(b)$ for any $b \in S(B)$.
    To see this, let $Z \subseteq B$ be a rooted assembly subspace containing $b$ with $|Z| = c_B(b)$.
    Then $Z$ is also a rooted assembly subspace of $A$ containing $b$, and so $c_A(b)$ can be at most $|Z|$.
    That is, $c_A(b) \le |Z| = c_B(b)$.
\end{proof}

\begin{theorem}\label{thm:image-lower-bound}
    If $f: A \rightarrow B$ is an assembly map, then $c_{f(A)}(f(x)) \le c_A(x)$ for all finite $x \in S(A)$.
    Furthermore, if $f$ is an embedding, then $c_{f(A)}(f(x)) = c_A(x)$.
\end{theorem}
\begin{proof}
    Suppose $x \in S(A)$ is finite, and $Z \subseteq A$ is a rooted with $s \in S(Z)$ and $|Z| = c_A(x)$.
    Restricting $f$ to $Z$ provides an assembly map $f^* : Z \rightarrow B$ such that $f(Z)$ contains $f(x)$, and is rooted in $B$.
    As such, $c_{f(A)}(f(x))$ can be no larger than $|f(Z)|$, so $c_{f(A)}(f(x)) \le c_A(x)$.

    Furthermore, suppose that $f$ is an embedding, and consider any $Z' \subseteq f(A)$ rooted and containing $f(x)$.
    The preimage of $Z'$ under $f$ is then a rooted assembly subspace of $A$ containing $x$, so $c_A(x)$ can be no larger than $|f^{-1}(Z)|$.
    Together with the previous result, we then have $c_{f(A)}(f(x)) = c_A(x)$.
\end{proof}

\begin{corollary}\label{cor:lowerset-index}
    Let $A$ be an assembly space and $x \in S(A)$ be finite.
    Then $c_A(x) = c_{x\downarrow}(x)$.
\end{corollary}
\begin{proof}
    There is a natural embedding $i : \downset{x} \rightarrow A$, so $c_A(x) = c_{x\downarrow}(x)$ for all finite $x \in S(A)$, as per \cref{thm:image-lower-bound}.
\end{proof}

\subsection{Computability and Algorithms}

\begin{theorem}\label{thm:computable}
    If $A$ is an assembly space and $x \in S(A)$ is finite, then $c(x)$ is computable.
\end{theorem}
\begin{proof}
    Every rooted assembly subspace with minimal size and containing $x$ is a minimal, rooted assembly subspace of $\downset{x}$.
    Since $x$ is finite, $\downset{x}$ is finite; that is $\downset{x}$ has finitely many transitions.
    This, together with the fact that $\pi(\sigma(t))$ and $\pi(\tau(t))$ are finite for all $t \in T(A)$, ensures that there areonly finitely many assembly subspaces of $\downset{x}$.
    As such, the set of all rooted assembly subspaces is computable; simply enumerate them.
    The size of each subspace is, of course, computable as one need simply count the transitions in the subspace.
    Finally, finding the minimum value in a finite set of natural numbers is computable.
    Thus, $c(x)$ is computable.
\end{proof}

\TODO Typeset split-branch algorithm

\section{Assembly Examples}

\TODO Come up with a few fun examples.

\end{document}

### 2021-05-10 papers/assembly/I/main.tex
Add some subsection headers
Set off pain points in red

@@
 
-\newcommand{\TODO}{\noindent\textbf{TODO:}~}
+\newcommand{\red}[1]{{\color{red}#1}}
+\newcommand{\TODO}[1]{\noindent\red{\textbf{TODO:}~#1}}
 
@@
 \section{Petri Nets}
+
+\subsection{Free Commutative Monoids}
 
@@
 As a concrete example, you could imagine mapping each of the molecules $\ce{H_2}$, $\ce{O_2}$ and $\ce{H_2O}$ to the number of Hydrogen atoms they contain, i.e. $2$, $0$, and $2$.
-\textbf{I don't like that example very much, but it's good enough for the moment.}
+\red{I don't like that example very much, but it's good enough for the moment.}
 This mapping process can be ``lifted'' into a map on the linear combinations by distributing the map over addition, so that $\ce{H_2} + \ce{O_2}$ maps to $2 + 0 = 2$.
@@
 The value of doing this is that it will allow us to coherently define a map between assembly spaces, to be defined, which will then be useful for proving certain theorems regarding bounds on quantities of interest.
+
+\subsection{Petri Nets}
 
@@
     Now let $U \subset f(\B)$ such that $f(P) = \upset{U}$.
-    \TODO: Show that $f(\B)$ is minimal.
+    \TODO{Show that $f(\B)$ is minimal.}
 \end{proof}
@@
     Further, we know that every site in $\downset{x}$ is above $\B_A \cap S(\downset{x})$ since, again $\B_A$ is a basis in $A$.
-    \TODO: Show that $\B_{x\downarrow}$ is minimal.
+    \TODO{Show that $\B_{x\downarrow}$ is minimal.}
 \end{proof}
@@
 
-\TODO Typeset split-branch algorithm
+\TODO{Typeset split-branch algorithm}
 
@@
 
-\TODO Come up with a few fun examples.
+\TODO{Come up with a few fun examples.}
 

### 2021-05-11 papers/assembly/I/main.tex
[papers] Add to the Petri net subsection

@@
 \tikzstyle{simple}=[-,draw=black,line width=1.000]
-\tikzstyle{inarrow}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.000]
+\tikzstyle{arrow}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.000]
 \tikzstyle{tick}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\draw (0,-0.1) -- (0,0.1);}},line width=1.000]
@@
 
+We wish to represent the idea of assembling objects out of ``simpler'' objects, in some sense of the word.
+To formalize this idea, we will build off of the concept of a \textit{Petri net}.
+In simple terms, a Petri net is a set of sites which we think of as representing types of objects, e.g.
+molecules, building materials, characters, etc..., and a set of transitions representing the ways in which sites can be combined to yield other sites.
+For the sake of formalism, we somewhat elevate the transitions above the sites in that we mostly consider the ``inputs'' and ``outputs'' of transitions, rather the transitions that a given site participates in.
+With this in mind, we formally define a Petri net as follows.
+
 \begin{definition}\label{def:petri}
@@
 
-Consider, for example, the Petri $P$ net described by $S(P) = \{ A, B, C, AA, AB, AAAB \}$ and $T(P) = \{ \alpha, \beta, \gamma, \delta \}$ with source and target maps:
+The maps $\sigma$ and $\tau$ assign to each transition a formal linear combination of sites.
+Picking up our molecular example from the previous section, we can consider the Petri net with sites $S = \{\ce{H_2}, \ce{O_2}, \ce{H_2O}\}$, a single transition $T = \{\alpha\}$, and source and target maps
+\begin{equation*}
+    \begin{tikzcd}
+        \alpha \arrow[r, mapsto, "\sigma"] & 2\ce{H_2} + \ce{O_2}
+        \quad\textrm{and}\quad
+        \alpha \arrow[r, mapsto, "\tau"] & 2\ce{H_2O}
+    \end{tikzcd}
+\end{equation*}
+
+There is a natural way of graphically representing a Petri net as a bipartite multigraph:
+
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [style=site] (H2) at (0, 1) {$\ce{H_2}$};
+                \node [style=site] (O2) at (0, -1) {$\ce{O_2}$};
+                \node [style=site] (H2O) at (4, 0) {$\ce{H_2O}$};
+                \node [style=transition] (alpha) at (2, 0) {$\alpha$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend right=15] (H2) to (alpha);
+                \draw [style=arrow, bend left=15] (H2) to (alpha);
+                \draw [style=arrow] (O2) to (alpha);
+                \draw [style=arrow, bend right=15] (alpha) to (H2O);
+                \draw [style=arrow, bend left=15] (alpha) to (H2O);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+
+We read this as ``\textit{transition $\alpha$ can only proceed if at least two $\ce{H_2}$ and one $\ce{O_2}$ are present in the system, and will yield two $\ce{H_2O}$ when it does}''.
+In essence, this is a statement about was can possibly happen, not necessarily what will happen; that's more a question of dynamics.
+
+As a more elaborate example, one which we will repeatedly refer to as we expand on the formalism, we imagine a simple ligation type process where in the characters $A$ and $B$ can be combined into strings and $C$ acts something like a \red{``catalyst''} making some transitions possible if and only if $C$ exists.
+Consider the Petri $P$ net described by $S(P) = \{ A, B, C, AA, AB, AAAB \}$ and $T(P) = \{ \alpha, \beta, \gamma, \delta \}$ with source and target maps:
 
@@
     \sigma(\gamma) &= AA + AB + C  & \tau(\gamma) &= AAAB + C   \\
-    \sigma(\delta) &= AAAB         & \tau(\delta) &= A + AA + B.
+    \sigma(\delta) &= AAAB         & \tau(\delta) &= A + AA + B
 \end{align*}
 
-A natural way of graphically representing this $P$ is with a bipartite multigraph:
+which we graphically represent as
 
-\begin{figure}[!h]
+\begin{center}
     \scalebox{0.6}{
@@
             \begin{pgfonlayer}{edgelayer}
-            \draw [style=inarrow, bend right=15] (A) to (tau1);
-            \draw [style=inarrow, bend left=15] (A) to (tau1);
-            \draw [style=inarrow, bend right=15] (A) to (tau2);
-            \draw [style=inarrow] (tau1) to (AA);
-            \draw [style=inarrow] (B) to (tau2);
-            \draw [style=inarrow] (tau2) to (AB);
-            \draw [style=inarrow] (AA) to (tau3);
-            \draw [style=inarrow] (AB) to (tau3);
-            \draw [style=inarrow, bend left=30] (C) to (tau3);
-            \draw [style=inarrow] (tau3) to (AAAB);
-            \draw [style=inarrow, bend left=30] (tau3) to (C);
-            \draw [style=inarrow] (AAAB) to (tau4);
-            \draw [style=inarrow, bend right=30] (tau4) to (A);
-            \draw [style=inarrow, bend right=30] (tau4) to (AA);
-            \draw [style=inarrow, bend left=40] (tau4) to (B);
+                \draw [style=arrow, bend right=15] (A) to (tau1);
+                \draw [style=arrow, bend left=15] (A) to (tau1);
+                \draw [style=arrow, bend right=15] (A) to (tau2);
+                \draw [style=arrow] (tau1) to (AA);
+                \draw [style=arrow] (B) to (tau2);
+                \draw [style=arrow] (tau2) to (AB);
+                \draw [style=arrow] (AA) to (tau3);
+                \draw [style=arrow] (AB) to (tau3);
+                \draw [style=arrow, bend left=30] (C) to (tau3);
+                \draw [style=arrow] (tau3) to (AAAB);
+                \draw [style=arrow, bend left=30] (tau3) to (C);
+                \draw [style=arrow] (AAAB) to (tau4);
+                \draw [style=arrow, bend right=30] (tau4) to (A);
+                \draw [style=arrow, bend right=30] (tau4) to (AA);
+                \draw [style=arrow, bend left=40] (tau4) to (B);
             \end{pgfonlayer}
@@
     }
-\end{figure}
+\end{center}
+
+This particular example exhibits a number of interesting features.
+First, there are transitions wherein one of the input sites is also an output site, namely $\gamma$'s dependence on $C$.
+Drawing from chemical parlance, this represents a catalytic effect; the transition can only proceed when the site is present\footnote{The addition of another transitition next to $\gamma$ which does not depend on or yield $C$ can model processes that can proceed without $C$ but is accelerated by it.}.
+Second, transitions such as $\delta$ can be viewed as a degradation or disassembly process.
+This allows reactions to run in both directions.
+To elaborate on this point, we can return to the water example and introduce a second transition allowing for the degradation of water back into Hydrogen and Oxygen:
+
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [style=site] (H2) at (0, 1) {$\ce{H_2}$};
+                \node [style=site] (O2) at (0, -1) {$\ce{O_2}$};
+                \node [style=site] (H2O) at (4, 0) {$\ce{H_2O}$};
+                \node [style=transition] (alpha) at (2, 0) {$\alpha$};
+                \node [style=transition] (beta) at (6, 0) {$\beta$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend right=15] (H2) to (alpha);
+                \draw [style=arrow, bend left=15] (H2) to (alpha);
+                \draw [style=arrow] (O2) to (alpha);
+                \draw [style=arrow, bend right=15] (alpha) to (H2O);
+                \draw [style=arrow, bend left=15] (alpha) to (H2O);
+                \draw [style=arrow, bend right=15] (H2O) to (beta);
+                \draw [style=arrow, bend left=15] (H2O) to (beta);
+                \draw [style=arrow, bend right=25] (beta.north) to (H2);
+                \draw [style=arrow, bend right=15] (beta.north) to (H2);
+                \draw [style=arrow, bend left=15] (beta.south) to (O2);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
 
@@
 
-\begin{figure}[!h]
+\begin{center}
     \scalebox{0.6}{
@@
             \begin{pgfonlayer}{edgelayer}
-            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau1);
-            \draw [style=inarrow, draw=gray!80, bend left=15] (A) to (tau1);
-            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau2);
-            \draw [style=inarrow, draw=gray!80] (tau1) to (AA);
-            \draw [style=inarrow, draw=gray!80] (B) to (tau2);
-            \draw [style=inarrow, draw=gray!80] (tau2) to (AB);
-            \draw [style=inarrow, draw=gray!80] (AA) to (tau3);
-            \draw [style=inarrow, draw=gray!80] (AB) to (tau3);
-            \draw [style=inarrow, draw=gray!80, bend left=30] (C) to (tau3);
-            \draw [style=inarrow, draw=gray!80] (tau3) to (AAAB);
-            \draw [style=inarrow, draw=gray!80, bend left=30] (tau3) to (C);
-            \draw [style=inarrow, draw=gray!80] (AAAB) to (tau4);
-            \draw [style=inarrow, draw=gray!80, bend right=30] (tau4) to (A);
-            \draw [style=inarrow, draw=gray!80, bend right=30] (tau4) to (AA);
-            \draw [style=inarrow, draw=gray!80, bend left=40] (tau4) to (B);
+                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau1);
+                \draw [style=arrow, draw=gray!80, bend left=15] (A) to (tau1);
+                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau2);
+                \draw [style=arrow, draw=gray!80] (tau1) to (AA);
+                \draw [style=arrow, draw=gray!80] (B) to (tau2);
+                \draw [style=arrow, draw=gray!80] (tau2) to (AB);
+                \draw [style=arrow, draw=gray!80] (AA) to (tau3);
+                \draw [style=arrow, draw=gray!80] (AB) to (tau3);
+                \draw [style=arrow, draw=gray!80, bend left=30] (C) to (tau3);
+                \draw [style=arrow, draw=gray!80] (tau3) to (AAAB);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau3) to (C);
+                \draw [style=arrow, draw=gray!80] (AAAB) to (tau4);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (A);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (AA);
+                \draw [style=arrow, draw=gray!80, bend left=40] (tau4) to (B);
 
-            \draw [style=inarrow, draw=gray!80, bend left=15] (W) to (tau5);
-            \draw [style=inarrow, draw=gray!80, bend right=15] (W) to (tau5);
-            \draw [style=inarrow, draw=gray!80, bend left=15] (tau5) to (X);
-            \draw [style=inarrow, draw=gray!80, bend right=15] (tau5) to (X);
-            \draw [style=inarrow, draw=gray!80, bend left=15] (X) to (tau6);
-            \draw [style=inarrow, draw=gray!80, bend right=15] (X) to (tau6);
-            \draw [style=inarrow, draw=gray!80] (tau6) to (Y);
-            \draw [style=inarrow, draw=gray!80, bend left=20] (Y) to (tau7);
-            \draw [style=inarrow, draw=gray!80] (Y) to (tau7);
-            \draw [style=inarrow, draw=gray!80, bend right=20] (Y) to (tau7);
-            \draw [style=inarrow, draw=gray!80] (tau7) to (Z);
-            \draw [style=inarrow, draw=gray!80, bend left=50] (tau7.south) to (Y.south);
-            \draw [style=inarrow, draw=gray!80] (Z) to (tau8);
-            \draw [style=inarrow, draw=gray!80, bend left=30] (tau8) to (X);
-            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (X);
-            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (Y);
+                \draw [style=arrow, draw=gray!80, bend left=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend right=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend left=15] (tau5) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
+                \draw [style=arrow, draw=gray!80, bend left=15] (X) to (tau6);
+                \draw [style=arrow, draw=gray!80, bend right=15] (X) to (tau6);
+                \draw [style=arrow, draw=gray!80] (tau6) to (Y);
+                \draw [style=arrow, draw=gray!80, bend left=20] (Y) to (tau7);
+                \draw [style=arrow, draw=gray!80] (Y) to (tau7);
+                \draw [style=arrow, draw=gray!80, bend right=20] (Y) to (tau7);
+                \draw [style=arrow, draw=gray!80] (tau7) to (Z);
+                \draw [style=arrow, draw=gray!80, bend left=50] (tau7.south) to (Y.south);
+                \draw [style=arrow, draw=gray!80] (Z) to (tau8);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau8) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (Y);
 
@@
     }
-\end{figure}
+\end{center}
 
@@
             \begin{pgfonlayer}{edgelayer}
-            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau1);
-            \draw [style=inarrow, draw=gray!80, bend left=15] (A) to (tau1);
-            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau2);
-            \draw [style=inarrow, draw=gray!80] (tau1) to (AA);
-            \draw [style=inarrow, draw=gray!80] (B) to (tau2);
-            \draw [style=inarrow, draw=gray!80] (tau2) to (AB);
-            \draw [style=inarrow, draw=gray!80] (AA) to (tau3);
-            \draw [style=inarrow, draw=gray!80] (AB) to (tau3);
-            \draw [style=inarrow, draw=gray!80, bend left=30] (C) to (tau3);
-            \draw [style=inarrow, draw=gray!80] (tau3) to (AAAB);
-            \draw [style=inarrow, draw=gray!80, bend left=30] (tau3) to (C);
+                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau1);
+                \draw [style=arrow, draw=gray!80, bend left=15] (A) to (tau1);
+                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau2);
+                \draw [style=arrow, draw=gray!80] (tau1) to (AA);
+                \draw [style=arrow, draw=gray!80] (B) to (tau2);
+                \draw [style=arrow, draw=gray!80] (tau2) to (AB);
+                \draw [style=arrow, draw=gray!80] (AA) to (tau3);
+                \draw [style=arrow, draw=gray!80] (AB) to (tau3);
+                \draw [style=arrow, draw=gray!80, bend left=30] (C) to (tau3);
+                \draw [style=arrow, draw=gray!80] (tau3) to (AAAB);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau3) to (C);
 
-            \draw [style=inarrow, draw=gray!80, bend left=15] (W) to (tau5);
-            \draw [style=inarrow, draw=gray!80, bend right=15] (W) to (tau5);
-            \draw [style=inarrow, draw=gray!80, bend left=15] (tau5) to (X);
-            \draw [style=inarrow, draw=gray!80, bend right=15] (tau5) to (X);
-            \draw [style=inarrow, draw=red, bend left=15] (X) to (tau6);
-            \draw [style=inarrow, draw=red, bend right=15] (X) to (tau6);
-            \draw [style=inarrow, draw=red] (tau6) to (Y);
-            \draw [style=inarrow, draw=red, bend left=20] (Y) to (tau7);
-            \draw [style=inarrow, draw=red] (Y) to (tau7);
-            \draw [style=inarrow, draw=red, bend right=20] (Y) to (tau7);
-            \draw [style=inarrow, draw=red] (tau7) to (Z);
-            \draw [style=inarrow, draw=red, bend left=50] (tau7.south) to (Y.south);
-            \draw [style=inarrow, draw=gray!80] (Z) to (tau8);
-            \draw [style=inarrow, draw=gray!80, bend left=30] (tau8) to (X);
-            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (X);
-            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (Y);
+                \draw [style=arrow, draw=gray!80, bend left=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend right=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend left=15] (tau5) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
+                \draw [style=arrow, draw=red, bend left=15] (X) to (tau6);
+                \draw [style=arrow, draw=red, bend right=15] (X) to (tau6);
+                \draw [style=arrow, draw=red] (tau6) to (Y);
+                \draw [style=arrow, draw=red, bend left=20] (Y) to (tau7);
+                \draw [style=arrow, draw=red] (Y) to (tau7);
+                \draw [style=arrow, draw=red, bend right=20] (Y) to (tau7);
+                \draw [style=arrow, draw=red] (tau7) to (Z);
+                \draw [style=arrow, draw=red, bend left=50] (tau7.south) to (Y.south);
+                \draw [style=arrow, draw=gray!80] (Z) to (tau8);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau8) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (Y);
 
@@
             \begin{pgfonlayer}{edgelayer}
-            \draw [style=inarrow, bend left=15] (tau1) to (A);
-            \draw [style=inarrow, bend right=15] (tau1) to (B);
-            \draw [style=inarrow, bend left=15] (A) to (tau2);
-            \draw [style=inarrow, bend right=15] (B) to (tau2);
+                \draw [style=arrow, bend left=15] (tau1) to (A);
+                \draw [style=arrow, bend right=15] (tau1) to (B);
+                \draw [style=arrow, bend left=15] (A) to (tau2);
+                \draw [style=arrow, bend right=15] (B) to (tau2);
             \end{pgfonlayer}

### 2021-05-13 papers/assembly/I/main.tex
sara is testing if she can git cool like the rest of elife
[papers] Change "axioms" to "theorems"

@@
 With assembly spaces defined, we are then able to define an assembly index for each object in the space, relative to the chosen basis, which characterizes how directly that object can be assembled.
-Further, we prove several axioms relating to method of bounding the assembly index for a given object and algorithms for computing or approximating it.
+Further, we prove several theorems relating to method of bounding the assembly index for a given object and algorithms for computing or approximating it.
+
+[This is Sara testing if she can git cool like the rest of the peeps in elife, I will remove on my next commit]
 

### 2021-05-13 papers/assembly/I/main.tex
[papers] Fix a typo in the FCM section

@@
 we are expressing the idea that some chemical process (transition) consumes twice as much $\ce{H_2}$ as $\ce{O_2}$ and yields $\ce{H_2O}$.
-The apparent multiplication ($\ce{2H_2}$) and addition ($\ce{2H_2} + \ce{O_}$) are simply formal constructs use to encode the stoichiometry of the reaction.
+The apparent multiplication ($\ce{2H_2}$) and addition ($\ce{2H_2} + \ce{O_2}$) are simply formal constructs use to encode the stoichiometry of the reaction.
 The addition here is commutative; we could have written $\ce{O_2} + \ce{2H_2}$, and it would have meant precisely the same thing.

### 2021-05-13 papers/assembly/I/main.tex
Clarify a point about elements of N[X].

@@
 It is important to stress at this point that the linear combinations do not need to ``make sense'', at least not yet.
-Taking the molecular example, $\ce{H_2}$, $\ce{7H_2} + \ce{O_2}$ and $\ce{H_2} + \ce{H_2O} + \ce{O_2}$ are permissible linear combinations and so are elements of $\N[X]$.
+Taking the molecular example, $\ce{H_2}$, $\ce{7H_2} + \ce{O_2}$ and $\ce{H_2} + \ce{H_2O} + \ce{O_2}$ are permissible linear combinations and so they are elements of $\N[X]$.
 This does not mean that we will, in practice, consider all of them.

### 2021-05-13 papers/assembly/I/main.tex
Expand text through Petri subnets

@@
     We call $\sigma_P$ the source map and $\tau_Q$ the target map.
-    An element of $\N[S(P)]$ is called a \textbf{marking} of the Petri net.
     Where context is unambiguous we may simply write $\sigma$ and $\tau$, but will generally retain the $T(P)$ and $S(P)$ notation.
@@
 
+An element of $\N[S(P)]$ is called a \textbf{marking} of the Petri net.
+Markings play an important role in modeling dynamical systems with Petri nets, representing the state of the system at some time.
+For example, the linear combination $5\ce{H_2} + 2\ce{O_2}$ might be thought to represent a system with $5$ molecules of $\ce{H_2}$ and $2$ molecules of $\ce{O_2}$ and no $\ce{H_2O}$.
+From this element, we can see that, at least in principle, the transition $\alpha$ might carried out at most twice.
+The question of whether, under the action of some dynamical model, one marking can be transformed or processed into another is referred to as the reachability problem and is remarkably difficult.
+While we will not delve into dynamical aspects of Petri nets or the to-be-defined assembly spaces in this work, dynamics will likely be a key element of the formal theory going forward.
+
+It is natural, once a mathematical structure has been defined, to ask how two instantiations of that structure may be mapped to one another.
+There is, of course, a well defined notion of a map between Petri nets, termed here a \textit{Petri net morphism}, which maps sites and transitions of one Petri net into another in a way that is compatible and consistent with the source and target maps of both Petri nets.
+These Petri net morphisms will play a crucial roll in the establishment of lower bounds for the assembly index in \cref{sec:assembly-index}.
+
 \begin{definition}\label{def:petri-map}
@@
 
-\begin{align*}
-    f(\alpha) &= f(\beta) = \chi    & g&(A)    = g(B) = X \\
-    f(\gamma) &= \psi               & g&(AA)   = g(AB) = g(C) = Y \\
-    f(\delta) &= \omega             & g&(AAAB) = Z
-\end{align*}
+The commutative diagrams in this definition are what we mean by "compatible and consistent".
+They essentially encode the idea that asking for a transition's inputs/outputs and then mapping those inputs/outputs into the new Petri network will give you the same result as first mapping the transition and then asking for the inputs/outputs of the image.
+To clarify this point, consider the two Petri nets $P$ and $Q$
 
@@
             \begin{pgfonlayer}{nodelayer}
+                \node [scale=3] (P) at (12, 0) {$P$};
                 \node [style=site] (A) at (0, 0.8) {$A$};
@@
 
+                \node [scale=3] (Q) at (12, -6) {$Q$};
+                \node [style=site] (W) at (-4, -6) {$W$};
+                \node [style=site] (X) at (0, -6) {$X$};
+                \node [style=site] (Y) at (4, -6) {$Y$};
+                \node [style=site] (Z) at (8, -6) {$Z$};
+                \node [style=transition] (tau5) at (-2, -6) {$\phi$};
+                \node [style=transition] (tau6) at (2, -6) {$\chi$};
+                \node [style=transition] (tau7) at (6, -6) {$\psi$};
+                \node [style=transition] (tau8) at (10, -6) {$\omega$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend right=15] (A) to (tau1);
+                \draw [style=arrow, bend left=15] (A) to (tau1);
+                \draw [style=arrow, bend right=15] (A) to (tau2);
+                \draw [style=arrow] (tau1) to (AA);
+                \draw [style=arrow] (B) to (tau2);
+                \draw [style=arrow] (tau2) to (AB);
+                \draw [style=arrow] (AA) to (tau3);
+                \draw [style=arrow] (AB) to (tau3);
+                \draw [style=arrow, bend left=30] (C) to (tau3);
+                \draw [style=arrow] (tau3) to (AAAB);
+                \draw [style=arrow, bend left=30] (tau3) to (C);
+                \draw [style=arrow] (AAAB) to (tau4);
+                \draw [style=arrow, bend right=30] (tau4) to (A);
+                \draw [style=arrow, bend right=30] (tau4) to (AA);
+                \draw [style=arrow, bend left=40] (tau4) to (B);
+
+                \draw [style=arrow, bend left=15] (W) to (tau5);
+                \draw [style=arrow, bend right=15] (W) to (tau5);
+                \draw [style=arrow, bend left=15] (tau5) to (X);
+                \draw [style=arrow, bend right=15] (tau5) to (X);
+                \draw [style=arrow, bend left=15] (X) to (tau6);
+                \draw [style=arrow, bend right=15] (X) to (tau6);
+                \draw [style=arrow] (tau6) to (Y);
+                \draw [style=arrow, bend left=20] (Y) to (tau7);
+                \draw [style=arrow] (Y) to (tau7);
+                \draw [style=arrow, bend right=20] (Y) to (tau7);
+                \draw [style=arrow] (tau7) to (Z);
+                \draw [style=arrow, bend left=50] (tau7.south) to (Y.south);
+                \draw [style=arrow] (Z) to (tau8);
+                \draw [style=arrow, bend left=30] (tau8) to (X);
+                \draw [style=arrow, bend right=30] (tau8) to (X);
+                \draw [style=arrow, bend right=30] (tau8) to (Y);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+
+We can construct Petri net morphism $f: P \rightarrow Q$ such that
+\begin{align*}
+    S(f)(\alpha) &= S(f)(\beta) = \chi    & T(f)&(A)    = T(f)(B) = X \\
+    S(f)(\gamma) &= \psi                  & T(f)&(AA)   = T(f)(AB) = T(f)(C) = Y \\
+    S(f)(\delta) &= \omega                & T(f)&(AAAB) = Z.
+\end{align*}
+
+Graphically, this might be depicted as two sets of arrows $T(f)$ and $S(f)$ which map transitions to transitions and sites to sites, respectively colored blue and red.
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [scale=3] (P) at (12, 0) {$P$};
+                \node [style=site] (A) at (0, 0.8) {$A$};
+                \node [style=site] (B) at (0, -0.8) {$B$};
+                \node [style=site] (C) at (6, -1.6) {$C$};
+                \node [style=site] (AA) at (4, 0.8) {$AA$};
+                \node [style=site] (AB) at (4, -0.8) {$AB$};
+                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
+                \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
+                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
+                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
+                \node [style=transition] (tau4) at (10, 0) {$\delta$};
+
+                \node [scale=3] (Q) at (12, -6) {$Q$};
                 \node [style=site] (W) at (-4, -6) {$W$};
@@
 
-                \node [text=red, scale=2] (g) at (-1.5, -3) {$g$};
-                \node [text=blue, scale=2] (f) at (0.5, -3) {$f$};
+                \node [text=red, scale=2] (s) at (-2, -2.5) {$S(f)$};
+                \node [text=blue, scale=2] (t) at (0, -3.5) {$T(f)$};
             \end{pgfonlayer}
@@
 
+It is easy to see by inspection that $f$ makes the diagrams in \cref{def:petri-map} commute; for example,
+\begin{equation*}
+    \sigma_Q(T(f)(\alpha)) = 2X = \N[S(f)](\sigma_P(\alpha)).
+\end{equation*}
+
+With an understanding of how to map Petri nets to one another, we can now turn to structural properties and relationships, starting with the concept of a subnet.
+In essense, a Petri subnet is simply a Petri net whose sets of sites and transitions are subsets of another net and whose source and target maps are compatible.
+
 \begin{definition}\label{def:subnet}
-    % Let $P$ and $Q$ be Petri nets.
-    % We say that $P$ is a \textbf{Petri subnet} of $Q$ when $T(P) \subseteq T(Q)$, $S(P) \subseteq S(Q)$, $\sigma_P = \sigma_Q|_{T(P)}$ and $\tau_P = \tau_Q|_{T(P)}$.
     Let $Q$ be a Petri net. A \textbf{Petri subnet} $P$ of $Q$ consists of
@@
 \end{definition}
+
+For example, each of the following nets are Petri subnets of our ligation net:
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [style=site] (A1) at (0, 2) {$A$};
+                \node [style=site] (AA1) at (0, 6) {$AA$};
+                \node [style=transition] (tau11) at (0, 4) {$\alpha$};
+
+                \node [style=site] (A2) at (4, 2) {$A$};
+                \node [style=site] (B2) at (5.6, 2) {$B$};
+                \node [style=site] (AA2) at (4, 6) {$AA$};
+                \node [style=site] (AB2) at (5.6, 6) {$AB$};
+                \node [style=transition] (tau12) at (4, 4) {$\alpha$};
+                \node [style=transition] (tau22) at (5.6, 4) {$\beta$};
+
+                \node [style=site] (A3) at (9.6, 0) {$A$};
+                \node [style=site] (B3) at (11.2, 0) {$B$};
+                \node [style=site] (C3) at (12, 6) {$C$};
+                \node [style=site] (AA3) at (9.6, 4) {$AA$};
+                \node [style=site] (AB3) at (11.2, 4) {$AB$};
+                \node [style=site] (AAAB3) at (10.4, 8) {$AAAB$};
+                \node [style=transition] (tau13) at (9.6, 2) {$\alpha$};
+                \node [style=transition] (tau23) at (11.2, 2) {$\beta$};
+                \node [style=transition] (tau33) at (10.4, 6) {$\gamma$};
+
+                \node [style=site] (AAAB4) at (16.8, 0) {$AAAB$};
+                \node [style=site] (A4) at (16, 4) {$A$};
+                \node [style=site] (B4) at (17.6, 4) {$B$};
+                \node [style=site] (AA4) at (16, 8) {$AA$};
+                \node [style=site] (AB4) at (17.6, 8) {$AB$};
+                \node [style=transition] (tau44) at (16.8, 2) {$\delta$};
+                \node [style=transition] (tau14) at (16, 6) {$\alpha$};
+                \node [style=transition] (tau24) at (17.6, 6) {$\beta$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend right=15] (A1) to (tau11);
+                \draw [style=arrow, bend left=15] (A1) to (tau11);
+                \draw [style=arrow] (tau11) to (AA1);
+
+                \draw [style=arrow, bend right=15] (A2) to (tau12);
+                \draw [style=arrow, bend left=15] (A2) to (tau12);
+                \draw [style=arrow, bend right=15] (A2) to (tau22);
+                \draw [style=arrow] (B2) to (tau22);
+                \draw [style=arrow] (tau12) to (AA2);
+                \draw [style=arrow] (tau22) to (AB2);
+
+                \draw [style=arrow, bend right=15] (A3) to (tau13);
+                \draw [style=arrow, bend left=15] (A3) to (tau13);
+                \draw [style=arrow, bend right=15] (A3) to (tau23);
+                \draw [style=arrow] (tau13) to (AA3);
+                \draw [style=arrow] (B3) to (tau23);
+                \draw [style=arrow] (tau23) to (AB3);
+                \draw [style=arrow] (AA3) to (tau33);
+                \draw [style=arrow] (AB3) to (tau33);
+                \draw [style=arrow, bend left=30] (C3) to (tau33);
+                \draw [style=arrow] (tau33) to (AAAB3);
+                \draw [style=arrow, bend left=30] (tau33) to (C3);
+
+                \draw [style=arrow] (AAAB4) to (tau44);
+                \draw [style=arrow] (tau44) to (A4);
+                \draw [style=arrow, bend left=50] (tau44) to (AA4);
+                \draw [style=arrow] (tau44) to (B4);
+                \draw [style=arrow, bend left=15] (A4) to (tau14);
+                \draw [style=arrow, bend right=15] (A4) to (tau14);
+                \draw [style=arrow, bend right=15] (A4) to (tau24);
+                \draw [style=arrow] (B4) to (tau24);
+                \draw [style=arrow] (tau14) to (AA4);
+                \draw [style=arrow] (tau24) to (AB4);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
 
@@
 
-\section{Assembly Spaces, Subspaces and Maps}
+\section{Assembly Spaces, Subspaces and Maps}\label{sec:assembly-index}
 

### 2021-05-13 papers/assembly/I/main.tex
Fleshout text and diagrams through sources and sinks

@@
 
+Petri net morphisms and subnets interact well.
+In particular, for a Petri net morphism $f : P \rightarrow Q$, the image $f(P)$ in $Q$ is a Petri subnet with source and target maps $\sigma_{f(P)}$ and $\tau_{f(P)}$ defined by restriction of $\sigma_Q$ and $\tau_Q$, respectively.
+Similarly, the preimage of a Petri subnet of $Q$ is a Petri subnet of $P$ with source and target maps defined by restriction of $\sigma_P$ and $\tau_P$.
+Continuing the example map from our ligation model,
 \begin{center}
@@
                 \node [style=transition] (tau3) at (6, 0) {$\gamma$};
+                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
+                \node [style=transition] (tau4) at (10, 0) {$\delta$};
 
+                \node [scale=3] (Q) at (12, -6) {$Q$};
                 \node [style=site] (W) at (-4, -6) {$W$};
-                \node [style=site, fill=green!20] (X) at (0, -6) {$X$};
-                \node [style=site, fill=green!20] (Y) at (4, -6) {$Y$};
-                \node [style=site, fill=green!20] (Z) at (8, -6) {$Z$};
+                \node [style=site, fill=green!20, draw=red!50] (X) at (0, -6) {$X$};
+                \node [style=site, fill=green!20, draw=red!50] (Y) at (4, -6) {$Y$};
+                \node [style=site, fill=green!20, draw=red!50] (Z) at (8, -6) {$Z$};
                 \node [style=transition] (tau5) at (-2, -6) {$\phi$};
-                \node [style=transition, fill=yellow!20] (tau6) at (2, -6) {$\chi$};
-                \node [style=transition, fill=yellow!20] (tau7) at (6, -6) {$\psi$};
-                \node [style=transition] (tau8) at (10, -6) {$\omega$};
+                \node [style=transition, fill=yellow!20, draw=red!50] (tau6) at (2, -6) {$\chi$};
+                \node [style=transition, fill=yellow!20, draw=red!50] (tau7) at (6, -6) {$\psi$};
+                \node [style=transition, fill=yellow!20, draw=red!50] (tau8) at (10, -6) {$\omega$};
             \end{pgfonlayer}
@@
                 \draw [style=arrow, draw=gray!80, bend left=30] (tau3) to (C);
+                \draw [style=arrow, draw=gray!80] (AAAB) to (tau4);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (A);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (AA);
+                \draw [style=arrow, draw=gray!80, bend left=40] (tau4) to (B);
 
@@
                 \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
-                \draw [style=arrow, draw=red, bend left=15] (X) to (tau6);
-                \draw [style=arrow, draw=red, bend right=15] (X) to (tau6);
-                \draw [style=arrow, draw=red] (tau6) to (Y);
-                \draw [style=arrow, draw=red, bend left=20] (Y) to (tau7);
-                \draw [style=arrow, draw=red] (Y) to (tau7);
-                \draw [style=arrow, draw=red, bend right=20] (Y) to (tau7);
-                \draw [style=arrow, draw=red] (tau7) to (Z);
-                \draw [style=arrow, draw=red, bend left=50] (tau7.south) to (Y.south);
-                \draw [style=arrow, draw=gray!80] (Z) to (tau8);
-                \draw [style=arrow, draw=gray!80, bend left=30] (tau8) to (X);
-                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (X);
-                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (Y);
+                \draw [style=arrow, draw=red!50, bend left=15] (X) to (tau6);
+                \draw [style=arrow, draw=red!50, bend right=15] (X) to (tau6);
+                \draw [style=arrow, draw=red!50] (tau6) to (Y);
+                \draw [style=arrow, draw=red!50, bend left=20] (Y) to (tau7);
+                \draw [style=arrow, draw=red!50] (Y) to (tau7);
+                \draw [style=arrow, draw=red!50, bend right=20] (Y) to (tau7);
+                \draw [style=arrow, draw=red!50] (tau7) to (Z);
+                \draw [style=arrow, draw=red!50, bend left=50] (tau7.south) to (Y.south);
+                \draw [style=arrow, draw=red!50] (Z) to (tau8);
+                \draw [style=arrow, draw=red!50, bend left=30] (tau8) to (X);
+                \draw [style=arrow, draw=red!50, bend right=30] (tau8) to (X);
+                \draw [style=arrow, draw=red!50, bend right=30] (tau8) to (Y);
 
@@
                 \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau3) to (tau7);
+                \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau4) to (tau8);
             \end{pgfonlayer}
@@
 \end{center}
+the image, outlined in light red, is a subnet of $Q$.
 
-For a Petri net morphism $f : P \rightarrow Q$, the image $f(P)$ in $Q$ is a Petri subnet with source and target maps $\sigma_{f(P)}$ and $\tau_{f(P)}$ defined by restriction of $\sigma_Q$ and $\tau_Q$, respectively.
-Similarly, the preimage of a Petri subnet of $Q$ is a Petri subnet of $P$ with source and target maps defined by restriction of $\sigma_P$ and $\tau_P$.
-
+When it comes to describing systems like the construction of a string, or the building of a molecule, it is often classically unphysical for objects to be created from nothing or destroyed.
+For that reason, we need to be able to identify aspects of a Petri net that might represent exactly such a process: sources and sinks.
 \begin{definition}\label{def:source-sink}
@@
 
-It follows immediately from the definition of a Petri map that the image of a sourceless Petri net is sourceless, otherwise the $\sigma$-diagram would not commute.
-Similarly, the image of a sinkless Petri net is sinkless.
-
+Graphically, 
 \begin{center}
@@
             \begin{pgfonlayer}{nodelayer}
-                \node [style=site] (A) at (2, 0.8) {$A$};
-                \node [style=site] (B) at (2, -0.8) {$B$};
-                \node [style=transition] (tau1) at (0, 0) {$\alpha$};
-                \node [style=transition] (tau2) at (4, 0) {$\beta$};
+                \node [style=transition] (source) at (0, 0) {source};
+                \node (A) at (2, 1.6) {};
+                \node (B) at (2, 0.8) {};
+                \node (C) at (2, 0) {};
+                \node (D) at (2, -0.8) {};
+                \node (E) at (2, -1.6) {};
+
+                \node (F) at (3, 1.6) {};
+                \node (G) at (3, 0.8) {};
+                \node (H) at (3, 0) {};
+                \node (I) at (3, -0.8) {};
+                \node (J) at (3, -1.6) {};
+                \node [style=transition] (sink) at (5, 0) {sink};
             \end{pgfonlayer}
             \begin{pgfonlayer}{edgelayer}
-                \draw [style=arrow, bend left=15] (tau1) to (A);
-                \draw [style=arrow, bend right=15] (tau1) to (B);
-                \draw [style=arrow, bend left=15] (A) to (tau2);
-                \draw [style=arrow, bend right=15] (B) to (tau2);
+                \draw [style=arrow, bend left=15] (source) to (A);
+                \draw [style=arrow, bend left=15] (source) to (B);
+                \draw [style=arrow] (source) to (C);
+                \draw [style=arrow, bend right=15] (source) to (D);
+                \draw [style=arrow, bend right=15] (source) to (E);
+
+                \draw [style=arrow, bend left=15] (F) to (sink);
+                \draw [style=arrow, bend left=15] (G) to (sink);
+                \draw [style=arrow] (H) to (sink);
+                \draw [style=arrow, bend right=15] (I) to (sink);
+                \draw [style=arrow, bend right=15] (J) to (sink);
             \end{pgfonlayer}
@@
 \end{center}
+It follows immediately from the definition of a Petri map that the image of a sourceless Petri net is sourceless, otherwise the $\sigma$-diagram would not commute.
+Similarly, the image of a sinkless Petri net is sinkless.
 

### 2021-05-14 papers/assembly/I/main.tex
Expand text and examples through pathway connectedness

@@
 
-As a more elaborate example, one which we will repeatedly refer to as we expand on the formalism, we imagine a simple ligation type process where in the characters $A$ and $B$ can be combined into strings and $C$ acts something like a \red{``catalyst''} making some transitions possible if and only if $C$ exists.
+As a more elaborate example, one which we will repeatedly refer to as we expand on the formalism as it exhibits number of interesting features, we imagine a simple ligation type process where in the characters $A$ and $B$ can be combined into strings and $C$ acts something like a \red{``catalyst''} making some transitions possible if and only if $C$ exists.
 Consider the Petri $P$ net described by $S(P) = \{ A, B, C, AA, AB, AAAB \}$ and $T(P) = \{ \alpha, \beta, \gamma, \delta \}$ with source and target maps:
@@
 
+Up to this point, all of the defintions have been fairly standard, at least in terms of concepts.
+We now start constructing apparently new ideas that will allow us to formalize the concepts of an assembly space and the assembly index.
+The first of these is the idea of a pathway.
+Suppose you begin with a given object $x$ and wish to fleshout all of the ways in which a second object $y$ might be constructed.
+The simplest first step is to construct a sequence of transitions, the first of which takes $x$ as part of its input, the last yields $y$ as part of it its output, and every transition in between depends at least partially on the output of the previous.
+Such a sequence of transitions is what we refer to as a \textit{pathway}.
+
 \begin{definition}\label{def:pathway}
@@
 
+It is clear that a pathway is a directed concept in general.
+A pathway from $x$ to $y$ is not necessarily a pathway from $y$ to $x$, and the existence of a pathway from $x$ to $y$ does not imply a pathway from $y$ to $x$ exists.
+If there is a pathway from $x$ to $y$ we say \textit{$x$ pathway connected to $y$}.
+In general, if $x$ is pathway connected to $y$ there may be multiple pathways, and it will be useful to refer to that set of pathways.
+
+\begin{definition}\label{def:pathway-connected}
+    Let $P$ be a Petri net and $x,y \in S(P)$.
+    We say that $x$ is \textbf{pathway connected to} $y$ if and only if there exists a pathway $\gamma = t_n \ldots t_1$ such that $\sigma(t_1) = x + m$ and $\tau(t_n) = y + n$ for some $m, n \in \N[S(P)]$.
+    The set of all pathways in $P$ from $x$ to $y$ is denoted $\Gamma_x^y$.
+    We denote the set of all pathways in $P$ starting from $x$ as $\Gamma_x = \bigcup_{y \in S(P)} \Gamma_x^y$, and all pathways terminating at $y$ as $\Gamma^y = \bigcup_{x \in S(P)} \Gamma_x^y$.
+\end{definition}
+
+In our ligation example, you might suppose that you begin with $A$ and would like to ultimately yield $AAAB$.
+There are in fact two pathways which accomplish this, $\gamma\alpha$ and $\gamma\beta$, which we read as \textit{first fire $\alpha$ ($\beta$, respectively) and then fire $\gamma$}:
 \begin{center}
@@
                 \node [style=transition] (tau4) at (10, 0) {$\delta$};
+                \node [scale=3] at (5, -3.5) {$\gamma\alpha$};
+
+                \node [style=site] (A2) at (14, 0.8) {$A$};
+                \node [style=site] (B2) at (14, -0.8) {$B$};
+                \node [style=site] (C2) at (20, -1.6) {$C$};
+                \node [style=site] (AA2) at (18, 0.8) {$AA$};
+                \node [style=site] (AB2) at (18, -0.8) {$AB$};
+                \node [style=site] (AAAB2) at (22, 0) {$AAAB$};
+                \node [style=transition] (tau12) at (16, 0.8) {$\alpha$};
+                \node [style=transition, fill=green!20] (tau22) at (16, -0.8) {$\beta$};
+                \node [style=transition, fill=green!20] (tau32) at (20, 0) {$\gamma$};
+                \node [style=transition] (tau42) at (24, 0) {$\delta$};
+                \node [scale=3] at (19, -3.5) {$\gamma\beta$};
             \end{pgfonlayer}
@@
                 \draw [style=arrow, bend left=40] (tau4) to (B);
+
+                \draw [style=arrow, bend right=15] (A2) to (tau12);
+                \draw [style=arrow, bend left=15] (A2) to (tau12);
+                \draw [style=arrow, bend right=15] (A2) to (tau22);
+                \draw [style=arrow] (tau12) to (AA2);
+                \draw [style=arrow] (B2) to (tau22);
+                \draw [style=arrow] (tau22) to (AB2);
+                \draw [style=arrow] (AA2) to (tau32);
+                \draw [style=arrow] (AB2) to (tau32);
+                \draw [style=arrow, bend left=30] (C2) to (tau32);
+                \draw [style=arrow] (tau32) to (AAAB2);
+                \draw [style=arrow, bend left=30] (tau32) to (C2);
+                \draw [style=arrow] (AAAB2) to (tau42);
+                \draw [style=arrow, bend right=30] (tau42) to (A2);
+                \draw [style=arrow, bend right=30] (tau42) to (AA2);
+                \draw [style=arrow, bend left=40] (tau42) to (B2);
             \end{pgfonlayer}
@@
 \end{center}
+where the transitions involved in the pathway are colored green.
+The set of pathways from $A$ to $AAAB$ is then $\Gamma_{A}^{AAAB} = \{ \gamma\alpha, \gamma\beta \}$.
+In the case where there are loops in the Petri net, some or all of the sets of pathways will be countably infinite.
+While this seems undesirable, it does not present much of a problem for the problems under consideration in this work.
 
-\begin{definition}\label{def:pathway-connected}
-    Let $P$ be a Petri net and $x,y \in S(P)$.
-    We say that $x$ is \textbf{pathway connected to} $y$ if and only if there exists a pathway $\gamma = t_n \ldots t_1$ such that $\sigma(t_1) = x + m$ and $\tau(t_n) = y + n$ for some $m, n \in \N[S(P)]$.
-    The set of all pathways in $P$ from $x$ to $y$ is denoted $\Gamma_x^y$.
-    We denote the set of all pathways in $P$ starting from $x$ as $\Gamma_x = \bigcup_{y \in S(P)} \Gamma_x^y$, and all pathways terminating at $y$ as $\Gamma^y = \bigcup_{x \in S(P)} \Gamma_x^y$.
-\end{definition}
-
+As with subnets, pathways interact well with Petri net morphisms.
+This brings us to our first lemma:
 \begin{lemma}\label{lem:image-of-pathways}

### 2021-05-14 papers/assembly/I/main.tex
[papers] Fix a few typos
[papers] Fix a few typos and clarify a bit

@@
 This construction naturally has a monoidal structure, hence the name.
-You can add such linear combinations to gether, e.g.
+You can add such linear combinations together, e.g.
 $\ce{H_2} + (\ce{H_2} + \ce{O_2}) = \ce{2H_2} + \ce{O_2}$, and there exists an identity element $0$ such that $0 + a = a + 0 = a$ for all $a \in \N[X]$.
@@
 First, there are transitions wherein one of the input sites is also an output site, namely $\gamma$'s dependence on $C$.
-Drawing from chemical parlance, this represents a catalytic effect; the transition can only proceed when the site is present\footnote{The addition of another transitition next to $\gamma$ which does not depend on or yield $C$ can model processes that can proceed without $C$ but is accelerated by it.}.
+Drawing from chemical parlance, this represents a catalytic effect; the transition can only proceed when the site is present\footnote{The addition of another transitition next to $\gamma$ which does not depend on or yield $C$ can model a process that can proceed without $C$ but is accelerated by it's presence.}.
 Second, transitions such as $\delta$ can be viewed as a degradation or disassembly process.
 This allows reactions to run in both directions.
-To elaborate on this point, we can return to the water example and introduce a second transition allowing for the degradation of water back into Hydrogen and Oxygen:
+To elaborate on this point, we can return to the water example and introduce a second transition allowing for the degradation of water back into diatomic Hydrogen and diatomic Oxygen:
 
@@
 For example, the linear combination $5\ce{H_2} + 2\ce{O_2}$ might be thought to represent a system with $5$ molecules of $\ce{H_2}$ and $2$ molecules of $\ce{O_2}$ and no $\ce{H_2O}$.
-From this element, we can see that, at least in principle, the transition $\alpha$ might carried out at most twice.
+From this element, we can see that, at least in principle, the transition $\alpha$ might be carried out at most twice\footnote{This is assuming no water dissociates after formation}.
 The question of whether, under the action of some dynamical model, one marking can be transformed or processed into another is referred to as the reachability problem and is remarkably difficult.
@@
 
-The commutative diagrams in this definition are what we mean by "compatible and consistent".
+The commutative diagrams in this definition are what we mean by ``compatible and consistent".
 They essentially encode the idea that asking for a transition's inputs/outputs and then mapping those inputs/outputs into the new Petri network will give you the same result as first mapping the transition and then asking for the inputs/outputs of the image.

### 2021-05-14 papers/assembly/I/main.tex
[papers] Describe the concept of a site-completion

@@
 
-\subsection{Free Commutative Monoids}
+\subsection{Free Commutative Monoids}\label{subsec:fcm}
 
@@
 
+We can view a pathway in a given Petri net $P$ as, or rather use it to construct, a set of transitions.
+This set of transitions does not, in and of itself, give us a Petri subnet; however, we can imagine collecting all of the sites in $P$ which participate in those transitions.
+Recalling back to \cref{subsec:fcm}, we can use $\pi$ to determine the sites which participate in a given linear combination.
+We can extend this idea to transitions in a Petri net.
+\begin{definition}\label{def:participate}
+    Let $P$ be a Petri net and let $t \in T(P)$ be a transition.
+    The set of all sites which participate in $t$ is denoted $\rho(t) = \pi(\sigma(t)) \cup \pi(\tau(t))$.
+    Similarly, if $X \subseteq T(P)$, $\rho(X) = \bigcup_{t \in X}\rho(x)$.
+\end{definition}
+
+This allows us to then define the \textit{site completion} of a subset of transitions from some Petri net.
+
 \begin{definition}\label{def:site-completion}
     Let $P$ be a petri net and let $X \subseteq T(P)$.
-    The \textbf{site completion} of $X$ in $P$, denoted $X^*$ is the Petri net defined by $T(X^*) = X$, $S(X^*) = \pi(X)$, $\sigma_{X^*} = \sigma_P|_{X^*}$ and $\tau_{X^*} = \tau_P|_{X^*}$.
-\end{definition}
+    The \textbf{site completion} of $X$ in $P$, denoted $X^*$ is the Petri net defined by $T(X^*) = X$, $S(X^*) = \rho(X)$, $\sigma_{X^*} = \sigma_P|_{X^*}$ and $\tau_{X^*} = \tau_P|_{X^*}$.
+\end{definition}
+It is very clear from the definition that for any given set of transitions $X$, the site completion is a Petri subnet.
+The site completion presents a very natural method for constructing a Petri subnet from a set of pathways, and gives a clean way of thinking about all of the different ways in which an object might be assembled from some starting set of objects.
+Taking the paths $\gamma\alpha$, $\gamma\beta$ and the set $\Gamma_A^{AAAB}$ from the previous example, we can construct the following Petri subnets (highlighted in red):
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [style=site, draw=red] (A) at (0, 0.8) {$A$};
+                \node [style=site] (B) at (0, -0.8) {$B$};
+                \node [style=site, draw=red] (C) at (6, -1.6) {$C$};
+                \node [style=site, draw=red] (AA) at (4, 0.8) {$AA$};
+                \node [style=site, draw=red] (AB) at (4, -0.8) {$AB$};
+                \node [style=site, draw=red] (AAAB) at (8, 0) {$AAAB$};
+                \node [style=transition, fill=green!20, draw=red] (tau1) at (2, 0.8) {$\alpha$};
+                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
+                \node [style=transition, fill=green!20, draw=red] (tau3) at (6, 0) {$\gamma$};
+                \node [style=transition] (tau4) at (10, 0) {$\delta$};
+                \node [scale=3] at (5, -3.5) {$\rho(\gamma\alpha)^*$};
+
+                \node [style=site, draw=red] (A2) at (14, 0.8) {$A$};
+                \node [style=site, draw=red] (B2) at (14, -0.8) {$B$};
+                \node [style=site, draw=red] (C2) at (20, -1.6) {$C$};
+                \node [style=site, draw=red] (AA2) at (18, 0.8) {$AA$};
+                \node [style=site, draw=red] (AB2) at (18, -0.8) {$AB$};
+                \node [style=site, draw=red] (AAAB2) at (22, 0) {$AAAB$};
+                \node [style=transition] (tau12) at (16, 0.8) {$\alpha$};
+                \node [style=transition, fill=green!20, draw=red] (tau22) at (16, -0.8) {$\beta$};
+                \node [style=transition, fill=green!20, draw=red] (tau32) at (20, 0) {$\gamma$};
+                \node [style=transition] (tau42) at (24, 0) {$\delta$};
+                \node [scale=3] at (19, -3.5) {$\rho(\gamma\beta)^*$};
+
+                \node [style=site, draw=red] (A3) at (7, -5.2) {$A$};
+                \node [style=site, draw=red] (B3) at (7, -6.8) {$B$};
+                \node [style=site, draw=red] (C3) at (13, -7.6) {$C$};
+                \node [style=site, draw=red] (AA3) at (11, -5.2) {$AA$};
+                \node [style=site, draw=red] (AB3) at (11, -6.8) {$AB$};
+                \node [style=site, draw=red] (AAAB3) at (15, -6) {$AAAB$};
+                \node [style=transition, fill=green!20, draw=red] (tau13) at (9, -5.2) {$\alpha$};
+                \node [style=transition, fill=green!20, draw=red] (tau23) at (9, -6.8) {$\beta$};
+                \node [style=transition, fill=green!20, draw=red] (tau33) at (13, -6) {$\gamma$};
+                \node [style=transition] (tau43) at (17, -6) {$\delta$};
+                \node [scale=3] at (12, -9.5) {$\rho(\Gamma_A^{AAAB})^*$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend right=15, draw=red] (A) to (tau1);
+                \draw [style=arrow, bend left=15, draw=red] (A) to (tau1);
+                \draw [style=arrow, bend right=15] (A) to (tau2);
+                \draw [style=arrow, draw=red] (tau1) to (AA);
+                \draw [style=arrow] (B) to (tau2);
+                \draw [style=arrow] (tau2) to (AB);
+                \draw [style=arrow, draw=red] (AA) to (tau3);
+                \draw [style=arrow, draw=red] (AB) to (tau3);
+                \draw [style=arrow, bend left=30, draw=red] (C) to (tau3);
+                \draw [style=arrow, draw=red] (tau3) to (AAAB);
+                \draw [style=arrow, bend left=30, draw=red] (tau3) to (C);
+                \draw [style=arrow] (AAAB) to (tau4);
+                \draw [style=arrow, bend right=30] (tau4) to (A);
+                \draw [style=arrow, bend right=30] (tau4) to (AA);
+                \draw [style=arrow, bend left=40] (tau4) to (B);
+
+                \draw [style=arrow, bend right=15] (A2) to (tau12);
+                \draw [style=arrow, bend left=15] (A2) to (tau12);
+                \draw [style=arrow, bend right=15, draw=red] (A2) to (tau22);
+                \draw [style=arrow] (tau12) to (AA2);
+                \draw [style=arrow, draw=red] (B2) to (tau22);
+                \draw [style=arrow, draw=red] (tau22) to (AB2);
+                \draw [style=arrow, draw=red] (AA2) to (tau32);
+                \draw [style=arrow, draw=red] (AB2) to (tau32);
+                \draw [style=arrow, bend left=30, draw=red] (C2) to (tau32);
+                \draw [style=arrow, draw=red] (tau32) to (AAAB2);
+                \draw [style=arrow, bend left=30, draw=red] (tau32) to (C2);
+                \draw [style=arrow] (AAAB2) to (tau42);
+                \draw [style=arrow, bend right=30] (tau42) to (A2);
+                \draw [style=arrow, bend right=30] (tau42) to (AA2);
+                \draw [style=arrow, bend left=40] (tau42) to (B2);
+
+                \draw [style=arrow, bend right=15, draw=red] (A3) to (tau13);
+                \draw [style=arrow, bend left=15, draw=red] (A3) to (tau13);
+                \draw [style=arrow, bend right=15, draw=red] (A3) to (tau23);
+                \draw [style=arrow, draw=red] (tau13) to (AA3);
+                \draw [style=arrow, draw=red] (B3) to (tau23);
+                \draw [style=arrow, draw=red] (tau23) to (AB3);
+                \draw [style=arrow, draw=red] (AA3) to (tau33);
+                \draw [style=arrow, draw=red] (AB3) to (tau33);
+                \draw [style=arrow, bend left=30, draw=red] (C3) to (tau33);
+                \draw [style=arrow, draw=red] (tau33) to (AAAB3);
+                \draw [style=arrow, bend left=30, draw=red] (tau33) to (C3);
+                \draw [style=arrow] (AAAB3) to (tau43);
+                \draw [style=arrow, bend right=30] (tau43) to (A3);
+                \draw [style=arrow, bend right=30] (tau43) to (AA3);
+                \draw [style=arrow, bend left=40] (tau43) to (B3);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
 

### 2021-05-14 papers/assembly/I/main.tex
[paper] Highlight a major error in the formalism

@@
 
+{
+    \color{red}
+
+    {
+        \large
+        \noindent \textbf{MAJOR PROBLEM:} the following three definitions are flawed in that loops gum up the works.
+        The previous example is demonstrative.
+        Every site lies within the upper subset of every other site.
+        Pick any one and call the singleton set containing it $\B$; it is minimal.
+        These two facts combined means that $\B$ is a basis, but \textbf{we don't want that!}.
+        Ideally, the possible bases should be $\{A, B, C\}$, $\{AA, AB, C\}$ and $\{C, AAAB\}$.
+
+        I think we see the source of this problem in the example of minimal elements below.
+        $C$ should be minimal, but it is not because there are pathways that lead to it, e.g. $\gamma$ from $AA$.
+        The solution, in my mind, is to somehow merge the definition of a pathway and the site completion, and slightly modify the definition of a minimal element.
+    }
+
+    In some Petri nets, there exist sites to which no pathways lead.
+    Consider, for example, the subnet of our ligation network which leaves out the $\delta$ transition:
+
+    \begin{center}
+        \color{black}
+        \scalebox{0.6}{
+            \begin{tikzpicture}
+                \begin{pgfonlayer}{nodelayer}
+                    \node [style=site, draw=red] (A) at (0, 0.8) {$A$};
+                    \node [style=site] (B) at (0, -0.8) {$B$};
+                    \node [style=site, draw=red] (C) at (6, -1.6) {$C$};
+                    \node [style=site, draw=red] (AA) at (4, 0.8) {$AA$};
+                    \node [style=site, draw=red] (AB) at (4, -0.8) {$AB$};
+                    \node [style=site, draw=red] (AAAB) at (8, 0) {$AAAB$};
+                    \node [style=transition, fill=green!20, draw=red] (tau1) at (2, 0.8) {$\alpha$};
+                    \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
+                    \node [style=transition, fill=green!20, draw=red] (tau3) at (6, 0) {$\gamma$};
+                \end{pgfonlayer}
+                \begin{pgfonlayer}{edgelayer}
+                    \draw [style=arrow, bend right=15] (A) to (tau1);
+                    \draw [style=arrow, bend left=15] (A) to (tau1);
+                    \draw [style=arrow, bend right=15] (A) to (tau2);
+                    \draw [style=arrow] (tau1) to (AA);
+                    \draw [style=arrow] (B) to (tau2);
+                    \draw [style=arrow] (tau2) to (AB);
+                    \draw [style=arrow] (AA) to (tau3);
+                    \draw [style=arrow] (AB) to (tau3);
+                    \draw [style=arrow, bend left=30] (C) to (tau3);
+                    \draw [style=arrow] (tau3) to (AAAB);
+                    \draw [style=arrow, bend left=30] (tau3) to (C);
+                \end{pgfonlayer}
+            \end{tikzpicture}
+        }
+    \end{center}
+
+    \begin{definition}\label{def:minimal}
+        Let $P$ be a Petri net. A site $y$ is \textbf{minimal} in $P$ if $\Gamma_x^y = \emptyset$ for all sites $y \ne x$ in $P$.
+        The set of all minimal sites of $P$ is denoted $\Min{P}$.
+    \end{definition}
+
     \begin{definition}\label{def:upper-lower-subnet}
@@
 
-\begin{definition}\label{def:minimal}
-    Let $P$ be a Petri net. A site $y$ is \textbf{minimal} in $P$ if $\Gamma_x^y = \emptyset$ for all sites $y \ne x$ in $P$.
-    The set of all minimal sites of $P$ is denoted $\Min{P}$.
-\end{definition}
-
     \begin{definition}\label{def:basis}
@@
     \end{definition}
+}
 

### 2021-05-14 papers/assembly/I/main.tex
[papers] Tag necessary changes related to the definition of a pathway

@@
 The simplest first step is to construct a sequence of transitions, the first of which takes $x$ as part of its input, the last yields $y$ as part of it its output, and every transition in between depends at least partially on the output of the previous.
-Such a sequence of transitions is what we refer to as a \textit{pathway}.
-
+Such a sequence of transitions forms the core of what we refer to as a \textit{pathway}.
+
+{
+    \color{red}
     \begin{definition}\label{def:pathway}
@@
 \begin{definition}\label{def:pathway-connected}
+    \TODO{Update this to reflect changes in the definition of a pathway.}
     Let $P$ be a Petri net and $x,y \in S(P)$.
@@
 
+\TODO{Update this example to reflect changes in the definition of a pathway.}
 In our ligation example, you might suppose that you begin with $A$ and would like to ultimately yield $AAAB$.
@@
 \begin{lemma}\label{lem:image-of-pathways}
+    \TODO{Update this proof to reflect changes to the definition of a pathway.}
     Let $f: P \rightarrow Q$ be a Petri net morphism and let $x, y \in S(P)$ be pathway connected in $P$.

### 2021-05-19 papers/assembly/I/main.tex
Start fresh on the definition of a basis

--- 2021-05-14 papers/assembly/I/main.tex
@@
 
-\tikzstyle{simple}=[-,line width=2.000]
 \tikzstyle{arrow}=[-,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.100]
@@
 
-\tikzstyle{empty}=[circle,fill=none, draw=none]
-\tikzstyle{inputdot}=[circle,fill=black,draw=black, scale=.5]
-\tikzstyle{dot}=[circle,fill=black,draw=black]
-\tikzstyle{bounding}=[circle,dashed, fill=none,draw=black, scale=9.00]
-\tikzstyle{simple}=[-,draw=black,line width=1.000]
-\tikzstyle{arrow}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.000]
-\tikzstyle{tick}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\draw (0,-0.1) -- (0,0.1);}},line width=1.000]
-\tikzstyle{inputarrow}=[->,draw=black, shorten >=.05cm]
+\tikzstyle{empty}=[circle, fill=none, draw=none]
+\tikzstyle{inputdot}=[circle, fill=black, draw=black, scale=.5]
+\tikzstyle{dot}=[circle, fill=black, draw=black]
+\tikzstyle{bounding}=[circle, dashed, fill=none, draw=black, scale=9.00]
+\tikzstyle{simple}=[->, draw=black, line width=1]
+\tikzstyle{arrow}=[-, draw=black, postaction={decorate}, decoration={markings,mark=at position .5 with {\arrow{>}}}, line width=1.000]
+\tikzstyle{tick}=[-, draw=black, postaction={decorate}, decoration={markings,mark=at position .5 with {\draw (0,-0.1) -- (0,0.1);}}, line width=1.000]
+\tikzstyle{inputarrow}=[->, draw=black, shorten >=.05cm]
 \tikzstyle{sitemap}=[->, dashed, draw=red, ultra thick, shorten >=.05cm]
@@
 \newcommand{\Min}[1]{\min{(#1)}}
+\newcommand{\Max}[1]{\max{(#1)}}
+\newcommand{\Minim}{\mathcal{Min}}
+\newcommand{\Maxim}{\mathcal{Max}}
 \newcommand{\A}{\mathcal{A}}
 \newcommand{\powerset}{\mathcal{P}}
+\newcommand{\pathway}[1]{\langle~#1~\rangle}
 
 \newcommand{\red}[1]{{\color{red}#1}}
+\newcommand{\green}[1]{{\color{green}#1}}
+\newcommand{\blue}[1]{{\color{blue}#1}}
 \newcommand{\TODO}[1]{\noindent\red{\textbf{TODO:}~#1}}
@@
 To clarify this point, $\pi(\ce{2H2} + \ce{O_2}) = \{\ce{H_2}, \ce{O_2}\}$.
+
+\red{Describe the relationship between the $\pi$ notation and the addition operator since we use both in subsequent sections.}
 
@@
     such that $\sigma_P = \sigma_Q|_{T(P)}$ and $\tau_P = \tau_Q|_{T(P)}$.
+    We denote this relationship as $P \subseteq Q$.
 \end{definition}
@@
 \end{center}
+
+\begin{definition}
+    Let $P$ be a Petri net and let $Q \subseteq P$.
+    We say that $Q$ \textit{spans} $P$ if $S(Q) = S(P)$.
+    \TODO{New Definition. Integrate with surrounding text.}
+\end{definition}
 
@@
 The simplest first step is to construct a sequence of transitions, the first of which takes $x$ as part of its input, the last yields $y$ as part of it its output, and every transition in between depends at least partially on the output of the previous.
-Such a sequence of transitions is what we refer to as a \textit{pathway}.
+Such a sequence of transitions forms the core of what we refer to as a \textit{pathway}.
 
 \begin{definition}\label{def:pathway}
-    If $P$ is a Petri net, a \textbf{pathway} $\gamma = t_n \ldots t_1$ in $P$ of length $n \ge 1$ is a sequence of transitions $t_i \in T$ such that $\tau(t_i) \ne 0$, $\sigma(t_i) \ne 0$, $m_{i} + \tau(t_i) = n_{i+1} + \sigma(t_{i+1})$ with $\sigma(t_{i+1}) \ne m_{i}$ and $\tau(t_{i+1}) \ne n_{i+1}$.
-We write $t \in \gamma$ to denote that the transition $t$ appears in the pathway $\gamma$.
-\end{definition}
-
-It is clear that a pathway is a directed concept in general.
-A pathway from $x$ to $y$ is not necessarily a pathway from $y$ to $x$, and the existence of a pathway from $x$ to $y$ does not imply a pathway from $y$ to $x$ exists.
-If there is a pathway from $x$ to $y$ we say \textit{$x$ pathway connected to $y$}.
-In general, if $x$ is pathway connected to $y$ there may be multiple pathways, and it will be useful to refer to that set of pathways.
-
-\begin{definition}\label{def:pathway-connected}
-    Let $P$ be a Petri net and $x,y \in S(P)$.
-    We say that $x$ is \textbf{pathway connected to} $y$ if and only if there exists a pathway $\gamma = t_n \ldots t_1$ such that $\sigma(t_1) = x + m$ and $\tau(t_n) = y + n$ for some $m, n \in \N[S(P)]$.
-    The set of all pathways in $P$ from $x$ to $y$ is denoted $\Gamma_x^y$.
-    We denote the set of all pathways in $P$ starting from $x$ as $\Gamma_x = \bigcup_{y \in S(P)} \Gamma_x^y$, and all pathways terminating at $y$ as $\Gamma^y = \bigcup_{x \in S(P)} \Gamma_x^y$.
-\end{definition}
-
-In our ligation example, you might suppose that you begin with $A$ and would like to ultimately yield $AAAB$.
-There are in fact two pathways which accomplish this, $\gamma\alpha$ and $\gamma\beta$, which we read as \textit{first fire $\alpha$ ($\beta$, respectively) and then fire $\gamma$}:
-\begin{center}
-    \scalebox{0.6}{
-        \begin{tikzpicture}
-            \begin{pgfonlayer}{nodelayer}
-                \node [style=site] (A) at (0, 0.8) {$A$};
-                \node [style=site] (B) at (0, -0.8) {$B$};
-                \node [style=site] (C) at (6, -1.6) {$C$};
-                \node [style=site] (AA) at (4, 0.8) {$AA$};
-                \node [style=site] (AB) at (4, -0.8) {$AB$};
-                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
-                \node [style=transition, fill=green!20] (tau1) at (2, 0.8) {$\alpha$};
-                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
-                \node [style=transition, fill=green!20] (tau3) at (6, 0) {$\gamma$};
-                \node [style=transition] (tau4) at (10, 0) {$\delta$};
-                \node [scale=3] at (5, -3.5) {$\gamma\alpha$};
-
-                \node [style=site] (A2) at (14, 0.8) {$A$};
-                \node [style=site] (B2) at (14, -0.8) {$B$};
-                \node [style=site] (C2) at (20, -1.6) {$C$};
-                \node [style=site] (AA2) at (18, 0.8) {$AA$};
-                \node [style=site] (AB2) at (18, -0.8) {$AB$};
-                \node [style=site] (AAAB2) at (22, 0) {$AAAB$};
-                \node [style=transition] (tau12) at (16, 0.8) {$\alpha$};
-                \node [style=transition, fill=green!20] (tau22) at (16, -0.8) {$\beta$};
-                \node [style=transition, fill=green!20] (tau32) at (20, 0) {$\gamma$};
-                \node [style=transition] (tau42) at (24, 0) {$\delta$};
-                \node [scale=3] at (19, -3.5) {$\gamma\beta$};
-            \end{pgfonlayer}
-            \begin{pgfonlayer}{edgelayer}
-                \draw [style=arrow, bend right=15] (A) to (tau1);
-                \draw [style=arrow, bend left=15] (A) to (tau1);
-                \draw [style=arrow, bend right=15] (A) to (tau2);
-                \draw [style=arrow] (tau1) to (AA);
-                \draw [style=arrow] (B) to (tau2);
-                \draw [style=arrow] (tau2) to (AB);
-                \draw [style=arrow] (AA) to (tau3);
-                \draw [style=arrow] (AB) to (tau3);
-                \draw [style=arrow, bend left=30] (C) to (tau3);
-                \draw [style=arrow] (tau3) to (AAAB);
-                \draw [style=arrow, bend left=30] (tau3) to (C);
-                \draw [style=arrow] (AAAB) to (tau4);
-                \draw [style=arrow, bend right=30] (tau4) to (A);
-                \draw [style=arrow, bend right=30] (tau4) to (AA);
-                \draw [style=arrow, bend left=40] (tau4) to (B);
-
-                \draw [style=arrow, bend right=15] (A2) to (tau12);
-                \draw [style=arrow, bend left=15] (A2) to (tau12);
-                \draw [style=arrow, bend right=15] (A2) to (tau22);
-                \draw [style=arrow] (tau12) to (AA2);
-                \draw [style=arrow] (B2) to (tau22);
-                \draw [style=arrow] (tau22) to (AB2);
-                \draw [style=arrow] (AA2) to (tau32);
-                \draw [style=arrow] (AB2) to (tau32);
-                \draw [style=arrow, bend left=30] (C2) to (tau32);
-                \draw [style=arrow] (tau32) to (AAAB2);
-                \draw [style=arrow, bend left=30] (tau32) to (C2);
-                \draw [style=arrow] (AAAB2) to (tau42);
-                \draw [style=arrow, bend right=30] (tau42) to (A2);
-                \draw [style=arrow, bend right=30] (tau42) to (AA2);
-                \draw [style=arrow, bend left=40] (tau42) to (B2);
-            \end{pgfonlayer}
-        \end{tikzpicture}
-    }
-\end{center}
-where the transitions involved in the pathway are colored green.
-The set of pathways from $A$ to $AAAB$ is then $\Gamma_{A}^{AAAB} = \{ \gamma\alpha, \gamma\beta \}$.
-In the case where there are loops in the Petri net, some or all of the sets of pathways will be countably infinite.
-While this seems undesirable, it does not present much of a problem for the problems under consideration in this work.
-
-As with subnets, pathways interact well with Petri net morphisms.
-This brings us to our first lemma:
+    Let $P$ be a Petri net.
+    A \textbf{pathway} in $P$ is a sequence of transitions $\gamma = \pathway{t_n \ldots t_1}$ of length $n \ge 1$ such that for all $1 \le i \le n$
+    \begin{equation*}
+        \pi(\sigma(t_i)) \subseteq \bigcup_{j=1}^{i-1} \pi(\tau(t_j)).
+    \end{equation*}
+    We consider the empty sequence of transitions as a pathway and refer to it as the \textbf{zero pathway}.
+
+    \smallskip
+    Let $X$ be a subset of sites in $P$. We say that $\gamma$ is \textit{from $X$} if $\pi(\sigma(t_1)) \subseteq X$.
+
+    \smallskip
+    Let $y$ be site, and let $Y$ be a subset of sites.
+    We say $\gamma$ is a \textit{to $y$} if $y \in \pi(\tau(t_n))$, and \textit{to $Y$} if $Y \subseteq \pi(\tau(t_n))$.
+
+    \smallskip
+    We say that the zero pathway is a pathway from any set $X$ to itself and none other.
+
+    \smallskip
+    Let $X$ and $Y$ be sets of sites in $P$.
+    We say $X$ is \textbf{pathway connected} to $Y$ if there exists a pathway, possibly the zero pathway, from $X$ to $Y$.
+
+    \red{I'd rather express this idea using $\N$ directly instead of using $\pi$}
+
+    \TODO{Break this definition apart}
+\end{definition}
+
+\red{The definition above is very close to the definition of a firing sequence. The primary difference is that we have no number-preserving requirements.}
+
 \begin{lemma}\label{lem:image-of-pathways}
-    Let $f: P \rightarrow Q$ be a Petri net morphism and let $x, y \in S(P)$ be pathway connected in $P$.
-    Then $f(x)$ and $f(y)$ are pathway connected in $f(P)$.
+    Let $f: P \rightarrow Q$ be a Petri net morphism and let $X, Y \subseteq S(P)$ be pathway connected in $P$.
+    Then either $f(x)$ and $f(y)$ are pathway connected in $f(P)$.
 \end{lemma}
 \begin{proof}
-    Let $\gamma = t_n \ldots t_1$ be a pathway from $x$ to $y$.
-    Given that $\sigma_P(t_i) \ne 0$ and $\tau_P(t_i) \ne 0$, we know that $\sigma_{f(P)} \ne 0$ and $\tau_{f(P)} \ne 0$.
-    Since $\sigma_P(t_1) = x + m$, $\sigma_{f(P)}(f(x)) = f(x) + m'$ for some $m' \in \N[S(f(P))]$; similarly, $\tau_{f(P)}(f(y)) = f(y) + n'$ for some $n' \in \N[S(f(P))]$.
-
-    Now, consider two transitions $t_i$ and $t_{i+1}$ in $\gamma$.
-    We know then that there exist $m, n \in \N[S(P)]$ such that $m + \tau_P(t_i) = n + \sigma_P(t_{i+1})$ with $m \ne \sigma_P(t_{i+1})$ and $n \ne \tau_P(t_i)$.
-    We can then apply $\N[S(f)]$ to each side to yield
-    \begin{equation*}
-        \N[S(f)](m) + \N[S(f)](\tau_P(t_i)) = \N[S(f)](n) + \N[S(f)](\sigma_P(t_{i+1})).
-    \end{equation*}
-    Per the commutativity relations imposed by the assembly map,
-    \begin{equation*}
-        \N[S(f)](\tau_P(t_i)) = \tau_{f(P)}(f(t_i)))
-        \quad\textrm{and}\quad
-        \N[S(f)](\sigma_P(t_{i+1})) = \sigma_{f(P)}(f(t_{i+1})).
-    \end{equation*}
-    So, there exist an $m', n' \in \N[S(f(P))]$ such that $m + \tau_{f(P)}(f(t_i)) = n + \sigma_{f(P)}(f(t_{i+1}))$, namely $m' = \N[S(f)](m)$ and $n' = \N[S(f)](n)$.
-    Finally, we know that $m' \ne \sigma_{f(P)}(f(t_{i+1}))$ as otherwise $m = \sigma_P(t_{i+1})$, and similarly $n' \ne \tau_{f(P)}(f(t_i))$.
-
-    This shows that a pathway exists from $f(x)$ to $f(y)$, so $f(x)$ and $f(y)$ are pathway connected.
+    \TODO{Complete}
 \end{proof}
 
-We can view a pathway in a given Petri net $P$ as, or rather use it to construct, a set of transitions.
-This set of transitions does not, in and of itself, give us a Petri subnet; however, we can imagine collecting all of the sites in $P$ which participate in those transitions.
-Recalling back to \cref{subsec:fcm}, we can use $\pi$ to determine the sites which participate in a given linear combination.
-We can extend this idea to transitions in a Petri net.
-\begin{definition}\label{def:participate}
-    Let $P$ be a Petri net and let $t \in T(P)$ be a transition.
-    The set of all sites which participate in $t$ is denoted $\rho(t) = \pi(\sigma(t)) \cup \pi(\tau(t))$.
-    Similarly, if $X \subseteq T(P)$, $\rho(X) = \bigcup_{t \in X}\rho(x)$.
-\end{definition}
-
-This allows us to then define the \textit{site completion} of a subset of transitions from some Petri net.
-
 \begin{definition}\label{def:site-completion}
-    Let $P$ be a petri net and let $X \subseteq T(P)$.
-    The \textbf{site completion} of $X$ in $P$, denoted $X^*$ is the Petri net defined by $T(X^*) = X$, $S(X^*) = \rho(X)$, $\sigma_{X^*} = \sigma_P|_{X^*}$ and $\tau_{X^*} = \tau_P|_{X^*}$.
-\end{definition}
-It is very clear from the definition that for any given set of transitions $X$, the site completion is a Petri subnet.
-The site completion presents a very natural method for constructing a Petri subnet from a set of pathways, and gives a clean way of thinking about all of the different ways in which an object might be assembled from some starting set of objects.
-Taking the paths $\gamma\alpha$, $\gamma\beta$ and the set $\Gamma_A^{AAAB}$ from the previous example, we can construct the following Petri subnets (highlighted in red):
-\begin{center}
-    \scalebox{0.6}{
-        \begin{tikzpicture}
-            \begin{pgfonlayer}{nodelayer}
-                \node [style=site, draw=red] (A) at (0, 0.8) {$A$};
-                \node [style=site] (B) at (0, -0.8) {$B$};
-                \node [style=site, draw=red] (C) at (6, -1.6) {$C$};
-                \node [style=site, draw=red] (AA) at (4, 0.8) {$AA$};
-                \node [style=site, draw=red] (AB) at (4, -0.8) {$AB$};
-                \node [style=site, draw=red] (AAAB) at (8, 0) {$AAAB$};
-                \node [style=transition, fill=green!20, draw=red] (tau1) at (2, 0.8) {$\alpha$};
-                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
-                \node [style=transition, fill=green!20, draw=red] (tau3) at (6, 0) {$\gamma$};
-                \node [style=transition] (tau4) at (10, 0) {$\delta$};
-                \node [scale=3] at (5, -3.5) {$\rho(\gamma\alpha)^*$};
-
-                \node [style=site, draw=red] (A2) at (14, 0.8) {$A$};
-                \node [style=site, draw=red] (B2) at (14, -0.8) {$B$};
-                \node [style=site, draw=red] (C2) at (20, -1.6) {$C$};
-                \node [style=site, draw=red] (AA2) at (18, 0.8) {$AA$};
-                \node [style=site, draw=red] (AB2) at (18, -0.8) {$AB$};
-                \node [style=site, draw=red] (AAAB2) at (22, 0) {$AAAB$};
-                \node [style=transition] (tau12) at (16, 0.8) {$\alpha$};
-                \node [style=transition, fill=green!20, draw=red] (tau22) at (16, -0.8) {$\beta$};
-                \node [style=transition, fill=green!20, draw=red] (tau32) at (20, 0) {$\gamma$};
-                \node [style=transition] (tau42) at (24, 0) {$\delta$};
-                \node [scale=3] at (19, -3.5) {$\rho(\gamma\beta)^*$};
-
-                \node [style=site, draw=red] (A3) at (7, -5.2) {$A$};
-                \node [style=site, draw=red] (B3) at (7, -6.8) {$B$};
-                \node [style=site, draw=red] (C3) at (13, -7.6) {$C$};
-                \node [style=site, draw=red] (AA3) at (11, -5.2) {$AA$};
-                \node [style=site, draw=red] (AB3) at (11, -6.8) {$AB$};
-                \node [style=site, draw=red] (AAAB3) at (15, -6) {$AAAB$};
-                \node [style=transition, fill=green!20, draw=red] (tau13) at (9, -5.2) {$\alpha$};
-                \node [style=transition, fill=green!20, draw=red] (tau23) at (9, -6.8) {$\beta$};
-                \node [style=transition, fill=green!20, draw=red] (tau33) at (13, -6) {$\gamma$};
-                \node [style=transition] (tau43) at (17, -6) {$\delta$};
-                \node [scale=3] at (12, -9.5) {$\rho(\Gamma_A^{AAAB})^*$};
-            \end{pgfonlayer}
-            \begin{pgfonlayer}{edgelayer}
-                \draw [style=arrow, bend right=15, draw=red] (A) to (tau1);
-                \draw [style=arrow, bend left=15, draw=red] (A) to (tau1);
-                \draw [style=arrow, bend right=15] (A) to (tau2);
-                \draw [style=arrow, draw=red] (tau1) to (AA);
-                \draw [style=arrow] (B) to (tau2);
-                \draw [style=arrow] (tau2) to (AB);
-                \draw [style=arrow, draw=red] (AA) to (tau3);
-                \draw [style=arrow, draw=red] (AB) to (tau3);
-                \draw [style=arrow, bend left=30, draw=red] (C) to (tau3);
-                \draw [style=arrow, draw=red] (tau3) to (AAAB);
-                \draw [style=arrow, bend left=30, draw=red] (tau3) to (C);
-                \draw [style=arrow] (AAAB) to (tau4);
-                \draw [style=arrow, bend right=30] (tau4) to (A);
-                \draw [style=arrow, bend right=30] (tau4) to (AA);
-                \draw [style=arrow, bend left=40] (tau4) to (B);
-
-                \draw [style=arrow, bend right=15] (A2) to (tau12);
-                \draw [style=arrow, bend left=15] (A2) to (tau12);
-                \draw [style=arrow, bend right=15, draw=red] (A2) to (tau22);
-                \draw [style=arrow] (tau12) to (AA2);
-                \draw [style=arrow, draw=red] (B2) to (tau22);
-                \draw [style=arrow, draw=red] (tau22) to (AB2);
-                \draw [style=arrow, draw=red] (AA2) to (tau32);
-                \draw [style=arrow, draw=red] (AB2) to (tau32);
-                \draw [style=arrow, bend left=30, draw=red] (C2) to (tau32);
-                \draw [style=arrow, draw=red] (tau32) to (AAAB2);
-                \draw [style=arrow, bend left=30, draw=red] (tau32) to (C2);
-                \draw [style=arrow] (AAAB2) to (tau42);
-                \draw [style=arrow, bend right=30] (tau42) to (A2);
-                \draw [style=arrow, bend right=30] (tau42) to (AA2);
-                \draw [style=arrow, bend left=40] (tau42) to (B2);
-
-                \draw [style=arrow, bend right=15, draw=red] (A3) to (tau13);
-                \draw [style=arrow, bend left=15, draw=red] (A3) to (tau13);
-                \draw [style=arrow, bend right=15, draw=red] (A3) to (tau23);
-                \draw [style=arrow, draw=red] (tau13) to (AA3);
-                \draw [style=arrow, draw=red] (B3) to (tau23);
-                \draw [style=arrow, draw=red] (tau23) to (AB3);
-                \draw [style=arrow, draw=red] (AA3) to (tau33);
-                \draw [style=arrow, draw=red] (AB3) to (tau33);
-                \draw [style=arrow, bend left=30, draw=red] (C3) to (tau33);
-                \draw [style=arrow, draw=red] (tau33) to (AAAB3);
-                \draw [style=arrow, bend left=30, draw=red] (tau33) to (C3);
-                \draw [style=arrow] (AAAB3) to (tau43);
-                \draw [style=arrow, bend right=30] (tau43) to (A3);
-                \draw [style=arrow, bend right=30] (tau43) to (AA3);
-                \draw [style=arrow, bend left=40] (tau43) to (B3);
-            \end{pgfonlayer}
-        \end{tikzpicture}
-    }
-\end{center}
-
-\begin{definition}\label{def:upper-lower-subnet}
-    Let $P$ be a Petri net and let $X \subseteq S(P)$.
-    The \textbf{upper subnet} of $X$ in $P$, denoted $\upset{X}$, consists of transitions $T(\upset{X}) = \bigcup_{x \in X}\{t \in \gamma ~|~ \gamma \in \Gamma_x\}$, sites $S(\upset{X}) = X \cup S(T(\upset{X})^*)$, $\sigma_{X\uparrow} = \sigma_P|_{T(X\uparrow)^*}$ and $\tau_{X\uparrow} = \tau_P|_{T(X\uparrow)^*}$.
-    Similarly, the \textbf{lower subnet} of $X$ in $P$, denoted $\downset{X}$, consists of transitions $T(\downset{X}) = \{t \in \gamma ~|~ \gamma \in \Gamma_X\}$, sites $S(\downset{X}) = X \cup S(T(\downset{X})^*)$, $\sigma' = \sigma|_{T(X\downarrow)^*}$ and $\tau = \tau|_{T(X\downarrow)^*}$.
-    If $x$ is an element $x \in P$, we write $\upset{x} = \upset{\{x\}}$ and $\downset{x} = \downset{\{x\}}$.
-\end{definition}
-
-\begin{definition}\label{def:minimal}
-    Let $P$ be a Petri net. A site $y$ is \textbf{minimal} in $P$ if $\Gamma_x^y = \emptyset$ for all sites $y \ne x$ in $P$.
-    The set of all minimal sites of $P$ is denoted $\Min{P}$.
+    \TODO{Complete}
+\end{definition}
+
+\begin{definition}\label{def:generator}
+    \TODO{A set of sites from which there is a pathway to every other object}
 \end{definition}
@@
 \begin{definition}\label{def:basis}
-    Let $P$ be a Petri net and let $\B$ be a non-empty subset of sites of $P$.
-    We say that $\B$ is a \textbf{basis} of $P$ if $P = \upset{\B}$ such that if $U \subseteq \B$ with $P = \upset{U}$ then $U = \B$.
-\end{definition}
-
-\begin{lemma}
+    Let $P$ be a Petri net and $X \subseteq S(P)$.
+    We say that $X$ is a basis of $P$ if $\ldots$.
+    \TODO{Complete}
+\end{definition}
+
+\begin{lemma}\label{lem:minimal-are-basic}
     Let $P$ be a Petri net. For any basis $\B$ of $P$, $\Min{P} \subseteq \B$.
-    Furthermore, if $\Min{P}$ is a basis of $P$, then $\Min{P}$ is the unique basis of $P$.
 \end{lemma}
 \begin{proof}
-    Let $x \in \Min{P}$ and $\B$ be a basis of $P$, then either there exists a $y \in \B$ such that $\Gamma_y^x$ is non-empty, or $x \in \B$.
-    However, $\Gamma^x$ is empty by definition of $\Min{P}$, so we have that $x \in B$.
-    Since the choice of $x$ was arbitrary, every element of $\Min{P}$ is in the basis $\B$ and thus $\min{P} \subseteq \B$.
-    Furthermore, suppose that $P = \upset{\Min{P}}$.
-    Then $\B = \Min{P}$, otherwise $\B$ would not be a basis, by definition.
-    Since $\B$ was chosen arbitrarily, this holds for every choice of $\B$ and as such $\Min{P}$ is a unqiue basis for $P$.
+    \TODO{Complete}
 \end{proof}
@@
 \begin{proof}
-    Certainly $f(\B)$ is nonempty as $\B$ is nonempty, and of course $f(P)$ must be in the upper set of $f(\B)$.
-    This follows immediately from \cref{lem:image-of-pathways} since every site in $P$ is pathway connected to a site in $\B$.
-    Now let $U \subset f(\B)$ such that $f(P) = \upset{U}$.
-    \TODO{Show that $f(\B)$ is minimal.}
+    \TODO{Complete}
 \end{proof}
@@
 \begin{proof}
-    By construction, $\downset{x}$ is a Petri subnet of $A$.
-    Since $A$ is an assembly space, it is sourceless and sinkless; and given that $\downset{x}$ is a site-completion, $\downset{x}$ is also sourceless and sinkless.
-    This gives us that $\downset{x}$ is an assembly subspace of $A$.
-    We need only show that $\B_{x\downarrow} = \B_A \cap S(\downset{x}) \subseteq \B_A$ is a basis of $\downset{x}$.
-    First, $\B_{x\downarrow}$ is necessarily nonempty since $\B_A$ is a basis in $A$.
-    Further, we know that every site in $\downset{x}$ is above $\B_A \cap S(\downset{x})$ since, again $\B_A$ is a basis in $A$.
-    \TODO{Show that $\B_{x\downarrow}$ is minimal.}
+    \TODO{Complete}
 \end{proof}
@@
 \begin{proof}
-    This follows directly from the fact that the image of a Petri net morphism is a Petri subnet, and that the image of a sourceless, sinkless Petri net is itself sourceless and sinkless.
+    \TODO{Complete}
 \end{proof}
@@
 \begin{proof}
-    First, $f(Z)$ is certainly an assembly subspace of $f(A)$ as we can view $f|_Z$ as an assembly map, and thus \cref{lem:assembly-image-is-subspace} applies.
-    To see that $f(Z)$ is rooted, we first note that $S(f)(\B_Z)$ and $S(f)(\B_A)$ are bases for $f(Z)$ and $f(A)$, respectively.
-    Further, since $Z$ is rooted in $A$, then $\B_Z \subset \B_A$, so $f(\B_Z) \subseteq f(\B_A)$.
+    \TODO{Complete}
 \end{proof}
@@
 \begin{proof}
-    We need only show that $c_A(b)$ cannot be greater than $c_B(b)$ for any $b \in S(B)$.
-    To see this, let $Z \subseteq B$ be a rooted assembly subspace containing $b$ with $|Z| = c_B(b)$.
-    Then $Z$ is also a rooted assembly subspace of $A$ containing $b$, and so $c_A(b)$ can be at most $|Z|$.
-    That is, $c_A(b) \le |Z| = c_B(b)$.
+    \TODO{Complete}
+    % We need only show that $c_A(b)$ cannot be greater than $c_B(b)$ for any $b \in S(B)$.
+    % To see this, let $Z \subseteq B$ be a rooted assembly subspace containing $b$ with $|Z| = c_B(b)$.
+    % Then $Z$ is also a rooted assembly subspace of $A$ containing $b$, and so $c_A(b)$ can be at most $|Z|$.
+    % That is, $c_A(b) \le |Z| = c_B(b)$.
 \end{proof}
@@
 \begin{proof}
-    Suppose $x \in S(A)$ is finite, and $Z \subseteq A$ is a rooted with $s \in S(Z)$ and $|Z| = c_A(x)$.
-    Restricting $f$ to $Z$ provides an assembly map $f^* : Z \rightarrow B$ such that $f(Z)$ contains $f(x)$, and is rooted in $B$.
-    As such, $c_{f(A)}(f(x))$ can be no larger than $|f(Z)|$, so $c_{f(A)}(f(x)) \le c_A(x)$.
-
-    Furthermore, suppose that $f$ is an embedding, and consider any $Z' \subseteq f(A)$ rooted and containing $f(x)$.
-    The preimage of $Z'$ under $f$ is then a rooted assembly subspace of $A$ containing $x$, so $c_A(x)$ can be no larger than $|f^{-1}(Z)|$.
-    Together with the previous result, we then have $c_{f(A)}(f(x)) = c_A(x)$.
+    \TODO{Complete}
+    % Suppose $x \in S(A)$ is finite, and $Z \subseteq A$ is a rooted with $s \in S(Z)$ and $|Z| = c_A(x)$.
+    % Restricting $f$ to $Z$ provides an assembly map $f^* : Z \rightarrow B$ such that $f(Z)$ contains $f(x)$, and is rooted in $B$.
+    % As such, $c_{f(A)}(f(x))$ can be no larger than $|f(Z)|$, so $c_{f(A)}(f(x)) \le c_A(x)$.
+    %
+    % Furthermore, suppose that $f$ is an embedding, and consider any $Z' \subseteq f(A)$ rooted and containing $f(x)$.
+    % The preimage of $Z'$ under $f$ is then a rooted assembly subspace of $A$ containing $x$, so $c_A(x)$ can be no larger than $|f^{-1}(Z)|$.
+    % Together with the previous result, we then have $c_{f(A)}(f(x)) = c_A(x)$.
 \end{proof}
@@
 \begin{proof}
-    There is a natural embedding $i : \downset{x} \rightarrow A$, so $c_A(x) = c_{x\downarrow}(x)$ for all finite $x \in S(A)$, as per \cref{thm:image-lower-bound}.
+    \TODO{Complete}
+    % There is a natural embedding $i : \downset{x} \rightarrow A$, so $c_A(x) = c_{x\downarrow}(x)$ for all finite $x \in S(A)$, as per \cref{thm:image-lower-bound}.
 \end{proof}
@@
 \begin{proof}
-    Every rooted assembly subspace with minimal size and containing $x$ is a minimal, rooted assembly subspace of $\downset{x}$.
-    Since $x$ is finite, $\downset{x}$ is finite; that is $\downset{x}$ has finitely many transitions.
-    This, together with the fact that $\pi(\sigma(t))$ and $\pi(\tau(t))$ are finite for all $t \in T(A)$, ensures that there areonly finitely many assembly subspaces of $\downset{x}$.
-    As such, the set of all rooted assembly subspaces is computable; simply enumerate them.
-    The size of each subspace is, of course, computable as one need simply count the transitions in the subspace.
-    Finally, finding the minimum value in a finite set of natural numbers is computable.
-    Thus, $c(x)$ is computable.
+    \TODO{Complete}
+    % Every rooted assembly subspace with minimal size and containing $x$ is a minimal, rooted assembly subspace of $\downset{x}$.
+    % Since $x$ is finite, $\downset{x}$ is finite; that is $\downset{x}$ has finitely many transitions.
+    % This, together with the fact that $\pi(\sigma(t))$ and $\pi(\tau(t))$ are finite for all $t \in T(A)$, ensures that there areonly finitely many assembly subspaces of $\downset{x}$.
+    % As such, the set of all rooted assembly subspaces is computable; simply enumerate them.
+    % The size of each subspace is, of course, computable as one need simply count the transitions in the subspace.
+    % Finally, finding the minimum value in a finite set of natural numbers is computable.
+    % Thus, $c(x)$ is computable.
 \end{proof}

### 2021-05-19 papers/assembly/I/main.tex
Flesh out the definition of the basis

@@
 \newcommand{\powerset}{\mathcal{P}}
-\newcommand{\pathway}[1]{\langle~#1~\rangle}
+\newcommand{\pathway}[1]{\langle#1\rangle}
 
@@
     \smallskip
-    Let $X$ be a subset of sites in $P$. We say that $\gamma$ is \textit{from $X$} if $\pi(\sigma(t_1)) \subseteq X$.
+    Let $X$ be a subset of sites in $P$. We say that $\gamma$ is \textit{from $X$} if $\pi(\sigma(t_1)) \subseteq X$, an will sometimes say that $\gamma$ starts at $X$.
 
@@
     Let $y$ be site, and let $Y$ be a subset of sites.
-    We say $\gamma$ is a \textit{to $y$} if $y \in \pi(\tau(t_n))$, and \textit{to $Y$} if $Y \subseteq \pi(\tau(t_n))$.
+    We say $\gamma$ is a \textit{to $y$} if $y \in \pi(\tau(t_n))$, and \textit{to $Y$} if $Y \subseteq \pi(\tau(t_n))$, and will sometimes say that $\gamma$ terminates at $y$ or $Y$.
 
@@
     Let $f: P \rightarrow Q$ be a Petri net morphism and let $X, Y \subseteq S(P)$ be pathway connected in $P$.
-    Then either $f(x)$ and $f(y)$ are pathway connected in $f(P)$.
+    Then either $f(X)$ and $f(Y)$ are pathway connected in $f(P)$.
 \end{lemma}
@@
 
+\begin{definition}\label{def:minimal-maximal}
+    Let $P$ be a Petri net and let $x$ be a site in $P$.
+    We say that $x$ is minimal in $P$ if the only pathway terminating at $x$ is the zero pathway.
+    Similarly, $x$ is maximal in $P$ if the only pathway starting at $x$ is the zero pathway.
+    The set of all minimal sites in $P$ is denoted $\Min{P}$, and the set of all maximal sites is denoted $\Max{P}$.
+\end{definition}
+
 \begin{definition}\label{def:site-completion}
-    \TODO{Complete}
+    \TODO{Given a set of transitions, construct the set of all sites and add all the edges.}
 \end{definition}
@@
 \begin{definition}\label{def:generator}
-    \TODO{A set of sites from which there is a pathway to every other object}
+    Let $P$ be a Petri net and let $X$ be a subset of sites of $P$.
+    We say that $X$ is a \textbf{generating set} of $P$ if $X$ is pathway connected to every subset of sites $Y$ in $P$.
 \end{definition}
 
+\red{The set of all generating sets of a Petri net can be ordered by set inclusion}
+
 \begin{definition}\label{def:basis}
-    Let $P$ be a Petri net and $X \subseteq S(P)$.
-    We say that $X$ is a basis of $P$ if $\ldots$.
-    \TODO{Complete}
+    Let $P$ be a Petri net and let $X$ be a set of generators of $P$.
+    We say that $X$ is a \textbf{basis} of $P$ if it is minimal in the partially ordered set of generating sets.
+    That is, $X$ is a basis if for any other generating set $Y$ of $P$, if $Y \subseteq X$ then $X = Y$.
 \end{definition}

### 2021-05-20 papers/assembly/I/main.tex
Add a few lemmas worth including

@@
 \usepackage{amsthm}
-\usepackage[usenames,dvipsnames]{color}
+\usepackage[usenames,dvipsnames]{xcolor}
 \usepackage{graphicx}
@@
 \newcommand{\B}{\mathcal{B}}
+\newcommand{\G}{\mathcal{G}}
 \newcommand{\Min}[1]{\min{(#1)}}
@@
 \newcommand{\red}[1]{{\color{red}#1}}
-\newcommand{\green}[1]{{\color{green}#1}}
+\newcommand{\green}[1]{{\color{ForestGreen}#1}}
 \newcommand{\blue}[1]{{\color{blue}#1}}
@@
                 \node [style=transition] (tau3) at (6, 0) {$\gamma$};
-                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
                 \node [style=transition] (tau4) at (10, 0) {$\delta$};
@@
 The first of these is the idea of a pathway.
-Suppose you begin with a given object $x$ and wish to fleshout all of the ways in which a second object $y$ might be constructed.
-The simplest first step is to construct a sequence of transitions, the first of which takes $x$ as part of its input, the last yields $y$ as part of it its output, and every transition in between depends at least partially on the output of the previous.
-Such a sequence of transitions forms the core of what we refer to as a \textit{pathway}.
+Suppose you begin with a set of objects $X$ and wish to consider ways of building some other set of objects.
+The simplest approach is to construct a sequence of transitions such that each transition depends only on $X$ or something produced by an earlier transition.
+This is what we refer to as a \textit{pathway}.
 
@@
     \smallskip
-    Let $X$ be a subset of sites in $P$. We say that $\gamma$ is \textit{from $X$} if $\pi(\sigma(t_1)) \subseteq X$, an will sometimes say that $\gamma$ starts at $X$.
+    Let $X$ be a subset of sites in $P$. We say that $\gamma$ is \textit{from $X$} if $\pi(\sigma(t_1)) \subseteq X$, and will sometimes say that $\gamma$ starts at $X$.
 
@@
 
-\red{The definition above is very close to the definition of a firing sequence. The primary difference is that we have no number-preserving requirements.}
-
-\begin{lemma}\label{lem:image-of-pathways}
-    Let $f: P \rightarrow Q$ be a Petri net morphism and let $X, Y \subseteq S(P)$ be pathway connected in $P$.
-    Then either $f(X)$ and $f(Y)$ are pathway connected in $f(P)$.
+Returning to our ligation example, suppose we have the set $X = \{A, B\}$.
+There are, in fact, pathways from $X$, counting the zero pathway.
+The other three are $\pathway{\alpha}$, $\pathway{\beta}$ and $\pathway{\alpha\beta}$ and $\pathway{\beta\alpha}$.
+We depict these pathways below.
+The sites in $X$ are outlined in blue, the transitions are filled green, and relevant edges are red.
+
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [style=site, draw=blue] (A1) at (0, 0.8) {$A$};
+                \node [style=site, draw=blue] (B1) at (0, -0.8) {$B$};
+                \node [style=site] (C1) at (6, -1.6) {$C$};
+                \node [style=site] (AA1) at (4, 0.8) {$AA$};
+                \node [style=site] (AB1) at (4, -0.8) {$AB$};
+                \node [style=site] (AAAB1) at (8, 0) {$AAAB$};
+                \node [style=transition, fill=green!20] (tau11) at (2, 0.8) {$\alpha$};
+                \node [style=transition] (tau21) at (2, -0.8) {$\beta$};
+                \node [style=transition] (tau31) at (6, 0) {$\gamma$};
+                \node [style=transition] (tau41) at (10, 0) {$\delta$};
+                \node [scale=3] at (5, -3.6) {$\pathway{\alpha}$};
+
+                \node [style=site, draw=blue] (A2) at (14, 0.8) {$A$};
+                \node [style=site, draw=blue] (B2) at (14, -0.8) {$B$};
+                \node [style=site] (C2) at (20, -1.6) {$C$};
+                \node [style=site] (AA2) at (18, 0.8) {$AA$};
+                \node [style=site] (AB2) at (18, -0.8) {$AB$};
+                \node [style=site] (AAAB2) at (22, 0) {$AAAB$};
+                \node [style=transition] (tau12) at (16, 0.8) {$\alpha$};
+                \node [style=transition, fill=green!20] (tau22) at (16, -0.8) {$\beta$};
+                \node [style=transition] (tau32) at (20, 0) {$\gamma$};
+                \node [style=transition] (tau42) at (24, 0) {$\delta$};
+                \node [scale=3] at (19, -3.6) {$\pathway{\beta}$};
+
+                \node [style=site, draw=blue] (A3) at (7, -5.8) {$A$};
+                \node [style=site, draw=blue] (B3) at (7, -7.4) {$B$};
+                \node [style=site] (C3) at (13, -8.2) {$C$};
+                \node [style=site] (AA3) at (11, -5.8) {$AA$};
+                \node [style=site] (AB3) at (11, -7.4) {$AB$};
+                \node [style=site] (AAAB3) at (15, -6.6) {$AAAB$};
+                \node [style=transition, fill=green!20] (tau13) at (9, -5.8) {$\alpha$};
+                \node [style=transition, fill=green!20] (tau23) at (9, -7.4) {$\beta$};
+                \node [style=transition] (tau33) at (13, -6.6) {$\gamma$};
+                \node [style=transition] (tau43) at (17, -6.6) {$\delta$};
+                \node [scale=3] at (12, -10.2) {$\pathway{\alpha\beta}, \pathway{\beta\alpha}$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, draw=red, bend right=15] (A1) to (tau11);
+                \draw [style=arrow, draw=red, bend left=15] (A1) to (tau11);
+                \draw [style=arrow, draw=gray!80, bend right=15] (A1) to (tau21);
+                \draw [style=arrow, draw=red] (tau11) to (AA1);
+                \draw [style=arrow, draw=gray!80] (B1) to (tau21);
+                \draw [style=arrow, draw=gray!80] (tau21) to (AB1);
+                \draw [style=arrow, draw=gray!80] (AA1) to (tau31);
+                \draw [style=arrow, draw=gray!80] (AB1) to (tau31);
+                \draw [style=arrow, draw=gray!80, bend left=30] (C1) to (tau31);
+                \draw [style=arrow, draw=gray!80] (tau31) to (AAAB1);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau31) to (C1);
+                \draw [style=arrow, draw=gray!80] (AAAB1) to (tau41);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau41) to (A1);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau41) to (AA1);
+                \draw [style=arrow, draw=gray!80, bend left=40] (tau41) to (B1);
+
+                \draw [style=arrow, draw=gray!80, bend right=15] (A2) to (tau12);
+                \draw [style=arrow, draw=gray!80, bend left=15] (A2) to (tau12);
+                \draw [style=arrow, draw=red, bend right=15] (A2) to (tau22);
+                \draw [style=arrow, draw=gray!80] (tau12) to (AA2);
+                \draw [style=arrow, draw=red] (B2) to (tau22);
+                \draw [style=arrow, draw=red] (tau22) to (AB2);
+                \draw [style=arrow, draw=gray!80] (AA2) to (tau32);
+                \draw [style=arrow, draw=gray!80] (AB2) to (tau32);
+                \draw [style=arrow, draw=gray!80, bend left=30] (C2) to (tau32);
+                \draw [style=arrow, draw=gray!80] (tau32) to (AAAB2);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau32) to (C2);
+                \draw [style=arrow, draw=gray!80] (AAAB2) to (tau42);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau42) to (A2);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau42) to (AA2);
+                \draw [style=arrow, draw=gray!80, bend left=40] (tau42) to (B2);
+
+                \draw [style=arrow, draw=red, bend right=15] (A3) to (tau13);
+                \draw [style=arrow, draw=red, bend left=15] (A3) to (tau13);
+                \draw [style=arrow, draw=red, bend right=15] (A3) to (tau23);
+                \draw [style=arrow, draw=red] (tau13) to (AA3);
+                \draw [style=arrow, draw=red] (B3) to (tau23);
+                \draw [style=arrow, draw=red] (tau23) to (AB3);
+                \draw [style=arrow, draw=gray!80] (AA3) to (tau33);
+                \draw [style=arrow, draw=gray!80] (AB3) to (tau33);
+                \draw [style=arrow, draw=gray!80, bend left=30] (C3) to (tau33);
+                \draw [style=arrow, draw=gray!80] (tau33) to (AAAB3);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau33) to (C3);
+                \draw [style=arrow, draw=gray!80] (AAAB3) to (tau43);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau43) to (A3);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau43) to (AA3);
+                \draw [style=arrow, draw=gray!80, bend left=40] (tau43) to (B3);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+
+There are a number of points to make with this example.
+First, because we did not include $C$ in our starting set, the pathways cannot include $\gamma$ or consequently $\delta$.
+Had $X$ included $C$, there would have been at least one pathway from $X$ to any subset of sites.
+This is an important point which we will return to shortly.
+Second, the graphical representations of both $\pathway{\alpha\beta}$ and $\pathway{\beta\alpha}$ are identical.
+This tells us that the order in which $\alpha$ and $\beta$ fire is unimportant as the result is the same.
+Finally, in each case the highlighted sites and transitions form a Petri subnet of the larger net.
+In fact, given any set of transitions, we can construct a Petri subnet.
+
+\begin{definition}\label{def:site-completion}
+    Let $P$ be a Petri net and let $X$ be a set of transitions in $P$.
+    The \textbf{site completion} of $X$, denoted $X^*$ is the Petri subnet of $P$ formed such that
+    \begin{itemize}
+        \item $T(X^*) = X$
+        \item $\displaystyle S(X^*) = \bigcup_{t \in X} \pi(\sigma(t) + \tau(t))$
+        \item $\sigma_{X^*} = \sigma_P|_X$ and $\tau_{X^*} = \tau_P|_X$.
+    \end{itemize}
+\end{definition}
+
+That this the site completion is, in fact, a subnet follows immediately from the definition of a subnet.
+Furthermore, since we can view a pathway as an ordered set of transitions, we can simply site complete that set to construct a Petri subnet.
+There are several questions we could continue with here, such whether every Petri subnet gives rise to a pathway which uses every transition in the subnet.
+However, since questions such as this are immaterial to the problem at hand, we will postpone addressing them to subsequent works.
+
+The value of pathways is that they allow us to consider or construct sets of sites which are sufficient to construct every other object in the space.
+We refer to such a subset of objects as a \textit{generating set}.
+
+\begin{definition}\label{def:generating-set}
+    Let $P$ be a Petri net and let $X$ be a subset of sites of $P$.
+    We say that $X$ is a \textbf{generating set} of $P$ if $X$ is pathway connected to every subset of sites $Y$ in $P$.
+    The set of all generating sets of $P$ is denoted $\G_P$.
+\end{definition}
+
+It is trivially true that $\G_P \ne \emptyset$ since the set of all sites in $P$ is a generating set.
+The set of all generating sets of a Petri net is naturally a subset of the powerset of the sites of $P$.
+That is, $\G_P \subseteq \powerset(S(P))$.
+As such, $\G_P$ inherits a partial order from $\powerset(S(P))$ with which we can seek ``smaller" generating sets.
+
+\begin{definition}\label{def:basis}
+    Let $P$ be a Petri net and let $X$ be a set of generators of $P$, $X \in \G_P$.
+    We say that $X$ is a \textbf{basis} if it is minimal with respect to the set inclusion order on $\G_P$.
+\end{definition}
+
+\begin{lemma}\label{lem:bases-exist}
+    Every Petri net admits at least one basis.
 \end{lemma}
 \begin{proof}
-    \TODO{Complete}
+    \TODO{Complete (likely to use Zorn's lemma)}
 \end{proof}
@@
 
-\begin{definition}\label{def:site-completion}
-    \TODO{Given a set of transitions, construct the set of all sites and add all the edges.}
-\end{definition}
-
-\begin{definition}\label{def:generator}
-    Let $P$ be a Petri net and let $X$ be a subset of sites of $P$.
-    We say that $X$ is a \textbf{generating set} of $P$ if $X$ is pathway connected to every subset of sites $Y$ in $P$.
-\end{definition}
-
-\red{The set of all generating sets of a Petri net can be ordered by set inclusion}
-
-\begin{definition}\label{def:basis}
-    Let $P$ be a Petri net and let $X$ be a set of generators of $P$.
-    We say that $X$ is a \textbf{basis} of $P$ if it is minimal in the partially ordered set of generating sets.
-    That is, $X$ is a basis if for any other generating set $Y$ of $P$, if $Y \subseteq X$ then $X = Y$.
-\end{definition}
-
 \begin{lemma}\label{lem:minimal-are-basic}
-    Let $P$ be a Petri net. For any basis $\B$ of $P$, $\Min{P} \subseteq \B$.
+    Let $P$ be a Petri net.
+    For any basis $\B$ of $P$, $\Min{P} \subseteq \B$.
+    Furthermore, if $\Min{P}$ is a basis, then it is a unique basis for $P$.
+
+    \red{I'm not $100\%$ sure of the last point, but I think it's true. We'll find out when we start writing the proof.}
+
+    \green{This is important for internal use.
+In all of the cases we have dealt with in practice, e.g.
+molecular assembly as applied, the minimal elements form a basis and there is no ambiguity in the Nat.
+Comm.
+paper recently published.}
+\end{lemma}
+\begin{proof}
+    \TODO{Complete}
+\end{proof}
+
+\begin{lemma}\label{lem:image-of-pathways}
+    Let $f: P \rightarrow Q$ be a Petri net morphism and let $X, Y \subseteq S(P)$ be pathway connected in $P$.
+    Then either $f(X)$ and $f(Y)$ are pathway connected in $f(P)$.
 \end{lemma}

### 2021-05-20 papers/assembly/I/main.tex
Finish draft of the Petri net section

@@
 \newcommand{\G}{\mathcal{G}}
-\newcommand{\Min}[1]{\min{(#1)}}
-\newcommand{\Max}[1]{\max{(#1)}}
-\newcommand{\Minim}{\mathcal{Min}}
-\newcommand{\Maxim}{\mathcal{Max}}
+\newcommand{\Ini}[1]{\textrm{Ini}(#1)}
+\newcommand{\Term}[1]{\textrm{Term}(#1)}
 \newcommand{\A}{\mathcal{A}}
@@
 \newcommand{\pathway}[1]{\langle#1\rangle}
+\newcommand{\R}{\mathbb{R}}
 
@@
 There is, of course, a well defined notion of a map between Petri nets, termed here a \textit{Petri net morphism}, which maps sites and transitions of one Petri net into another in a way that is compatible and consistent with the source and target maps of both Petri nets.
-These Petri net morphisms will play a crucial roll in the establishment of lower bounds for the assembly index in \cref{sec:assembly-index}.
+These Petri net morphisms will play a crucial roll in the establishment of bounds for the assembly index in \Cref{sec:assembly-index-bounds}.
 
@@
         \item $T(X^*) = X$
-        \item $\displaystyle S(X^*) = \bigcup_{t \in X} \pi(\sigma(t) + \tau(t))$
+        \item $\displaystyle S(X^*) = \bigcup_{t \in X} \pi(\sigma_P(t) + \tau_P(t))$
         \item $\sigma_{X^*} = \sigma_P|_X$ and $\tau_{X^*} = \tau_P|_X$.
@@
 
-That this the site completion is, in fact, a subnet follows immediately from the definition of a subnet.
+That the site completion is, in fact, a subnet follows immediately from the definition of a subnet.
 Furthermore, since we can view a pathway as an ordered set of transitions, we can simply site complete that set to construct a Petri subnet.
@@
 
-It is trivially true that $\G_P \ne \emptyset$ since the set of all sites in $P$ is a generating set.
-The set of all generating sets of a Petri net is naturally a subset of the powerset of the sites of $P$.
-That is, $\G_P \subseteq \powerset(S(P))$.
-As such, $\G_P$ inherits a partial order from $\powerset(S(P))$ with which we can seek ``smaller" generating sets.
+To clarify this idea, let us consider a few sets of sites from the ligation example.
+The first, and least interesting example, is the set of all sites $\{A, B, AA, AB, C, AAAB\}$.
+Clearly every site in the space can be created, or at least provided, from this set.
+In fact it is trivially true that for any Petri net $P$, the set of all sites in the net is a generating set, i.e. $\G_P \ne \emptyset$.
+Furthermore, the empty set of sites is not generating in this case, though it may be in Petri nets with sources (\Cref{def:source-sink}).
+The set $\{A,B\}$ is also not a generating set; what sequence of transitions could yield $C$ or $AAAB$?
+It is reassuring to know that not all subsets sites are generating, in this case at least.
+However, the set $\{A,B,C\}$ is generating, and we can add any other site to this set and the result will be a generating set, e.g. $\{A,B,C,AAAB\}$.
+The sets $\{A, AA, AB, C\}$ and $\{AB, AAAB, C\}$ are generating, but upon close inspection we can see that some of the sites within them are not required, e.g.
+$A$ or $AA$ in the former, and $AB$ in the latter.
+This alludes to the idea of a \textit{minimal} generating set; one from which we can remove no sites and the result still be a generating set.
+We can formalize this idea by noting that the set of all generating sets of a Petri net is naturally a subset of the powerset of the sites of the net, $\G_P \subseteq \powerset(S(P))$.
+As such, $\G_P$ inherits a partial order from $\powerset(S(P))$ (subset inclusion) within which we can determine if a generating set is minimal.
+We refer to a minimal generating set with respect to this partial order as a \textit{basis}.
 
 \begin{definition}\label{def:basis}
-    Let $P$ be a Petri net and let $X$ be a set of generators of $P$, $X \in \G_P$.
+    Let $P$ be a Petri net and let $X$ be a generating set of $P$, $X \in \G_P$.
     We say that $X$ is a \textbf{basis} if it is minimal with respect to the set inclusion order on $\G_P$.
@@
 
+The ligation example admits a choice of basis: $\{A,B,C\}$, $\{A,AB,C\}$, $\{AA,AB,C\}$, or $\{C,AAAB\}$.
+While it may seem undesirable, on its face, for a Petri net to admit more than one basis, there is little difference between this and being able to choose the basis of a vector space such as $\R^2$.
+We can view each choice of basis as representing a minimal set of starting components from which everything of interest can be constructed; similar to deciding which raw materials to use to build a house, or which chemical reagents to use to synthesis a given set of molecules.
+Depending on the context, there may be \textit{a priori} reasons to prefer one basis over another.
+For example, in the ligation example, the $\{A,B,C\}$ basis seems somehow preferable as it is composed of monomers while all other bases consist of higher-order components.
+To make such a distinction, however, requires additional structure, such as a grading\footnote{Here we use the term \textit{grading} loosely.
+It could, for example, simply mean a map $g : S(P) \rightarrow \N$ for some Petri net $P$ which is consistent in some way with the graph structure of $P$.} on the sites with which to formally distinguish between bases.
+The choice of basis will become important in \Cref{sec:assembly-spaces,sec:assembly-index}, but for now we are only interested in the existence and uniqueness of bases and their preservation under Petri net morphisms.
+For this reason, we will leave the question of mechanisms for preferentially choosing a basis for a future work.
+
+Whether or not a Petri net admits a basis at all and whether that basis is unique, are both fundamentally important questions.
+The establishment of something like the assembly index of an object relies on the specification of a basis.
+Fortuitously, every Petri net admits at least one basis, and in certain cases this basis will be unique.
 \begin{lemma}\label{lem:bases-exist}
@@
 
-\begin{definition}\label{def:minimal-maximal}
+If we recall, a generating set (and consequently a basis) is a set of sites from which all others can be reached via a pathway.
+However, some objects are priviledged in that there are not pathways which terminate at them.
+Consider $C$ in the ligation example:
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node (a) at (-4, 0.8) {};
+                \node (b) at (-4, -0.8) {};
+                \node (c) at (4, 0) {};
+                \node [style=site] (C) at (0, -1.6) {$C$};
+                \node [style=site] (AA) at (-2, 0.8) {$AA$};
+                \node [style=site] (AB) at (-2, -0.8) {$AB$};
+                \node [style=site] (AAAB) at (2, 0) {$AAAB$};
+                \node [style=transition] (gamma) at (0, 0) {$\gamma$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend left=30] (C) to (gamma);
+                \draw [style=arrow, bend left=30] (gamma) to (C);
+                \draw [style=arrow] (AA) to (gamma);
+                \draw [style=arrow] (AB) to (gamma);
+                \draw [style=arrow] (gamma) to (AAAB);
+                \draw [style=arrow] (a) to (AA);
+                \draw [style=arrow] (b) to (AB);
+                \draw [style=arrow] (AAAB) to (c);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+There is no transition that yields $C$ without depending upon it, so $C$ must be included in any generating set or basis.
+This is also true of any site that has no incoming edges, for example.
+We refer to such a site as these as \textit{initial}, with the concept of \textit{terminal} defined similarly\footnote{We've chosen this terminology to allude to a possible category-theoretic formulation wherein a Petri net is a category with sets of sites as objects and pathways are morphisms.
+In that context, sets of sites which are initial/terminal this text's formalism are initial/terminal objects in the category.}
+\begin{definition}\label{def:initial-final}
     Let $P$ be a Petri net and let $x$ be a site in $P$.
-    We say that $x$ is minimal in $P$ if the only pathway terminating at $x$ is the zero pathway.
-    Similarly, $x$ is maximal in $P$ if the only pathway starting at $x$ is the zero pathway.
-    The set of all minimal sites in $P$ is denoted $\Min{P}$, and the set of all maximal sites is denoted $\Max{P}$.
-\end{definition}
-
-\begin{lemma}\label{lem:minimal-are-basic}
+    We say that $x$ is initial in $P$ if the only pathway terminating at $x$ is the zero pathway.
+    Similarly, $x$ is final in $P$ if the only pathway starting at $x$ is the zero pathway.
+    The set of all initial sites in $P$ is denoted $\Ini{P}$, and the set of all final sites is denoted $\Term{P}$.
+\end{definition}
+In the ligation example, the only inital site is $C$ and there are no terminal sites.
+However, if we were to remove the $\delta$ transition, for example,
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [style=site] (A) at (0, 0.8) {$A$};
+                \node [style=site] (B) at (0, -0.8) {$B$};
+                \node [style=site] (C) at (6, -1.6) {$C$};
+                \node [style=site] (AA) at (4, 0.8) {$AA$};
+                \node [style=site] (AB) at (4, -0.8) {$AB$};
+                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
+                \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
+                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
+                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend right=15] (A) to (tau1);
+                \draw [style=arrow, bend left=15] (A) to (tau1);
+                \draw [style=arrow, bend right=15] (A) to (tau2);
+                \draw [style=arrow] (tau1) to (AA);
+                \draw [style=arrow] (B) to (tau2);
+                \draw [style=arrow] (tau2) to (AB);
+                \draw [style=arrow] (AA) to (tau3);
+                \draw [style=arrow] (AB) to (tau3);
+                \draw [style=arrow, bend left=30] (C) to (tau3);
+                \draw [style=arrow] (tau3) to (AAAB);
+                \draw [style=arrow, bend left=30] (tau3) to (C);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+then the site $AAAB$ will be terminal and both the initial sites will be $A$, $B$ and $C$.
+Sourceless, acyclic Petri nets (nets without loops) will necessarily contain initial sites, and similarly sinkless, acyclic Petri nets will contain terminal sites.
+
+The value of identifying initial sites is that they are necessarily elements of every basis, and if the set of initial sites is a basis in its own right, then it is the only basis.
+\begin{lemma}\label{lem:initial-are-basic}
     Let $P$ be a Petri net.
-    For any basis $\B$ of $P$, $\Min{P} \subseteq \B$.
-    Furthermore, if $\Min{P}$ is a basis, then it is a unique basis for $P$.
+    For any basis $\B$ of $P$, $\Ini{P} \subseteq \B$.
+    Furthermore, if $\Ini{P}$ is a basis, then it is a unique basis for $P$.
 
@@
 In all of the cases we have dealt with in practice, e.g.
-molecular assembly as applied, the minimal elements form a basis and there is no ambiguity in the Nat.
+molecular assembly as applied, the inital sites form a basis and so there is no ambiguity in the Nat.
 Comm.
@@
 
+Our final concern regaring Petri nets is whether or not bases are are preserved under Petri net morphisms.
+To establish that this is the case, we must first show that if two sets of sites are pathway connected, then they will be pathway connected in the image of a Petri net morphism.
 \begin{lemma}\label{lem:image-of-pathways}
@@
 
-\begin{lemma}\label{lem:image-basis}
-    Let $P$ be a Petri net with basis $\B$ and let $f : A \rightarrow B$ be a Petri net morphism.
-    Then $f(\B)$ is a basis for $f(P)$.
+\TODO{Example}
+
+The fact that generating sets are preserved, follows from the preservation of pathways.
+\begin{lemma}\label{lem:image-of-generating-sets}
+    Let $f: P \rightarrow Q$ be a Petri net morphism and let $X$ be a generating set of $P$.
+    Then $f(X)$ is a generating set of $f(P)$.
 \end{lemma}
@@
 
-\section{Assembly Spaces, Subspaces and Maps}\label{sec:assembly-index}
+\TODO{Example Figure}
+
+This is not to say that the only generating sets in the image of a Petri net will be the image of a generating set.
+The codomain of the Petri net morphism may in fact have additional generating sets.
+
+\TODO{Example Figure}
+
+Still, the fact that generating sets are preserved yields nicely our final result: bases are preserved under Petri net morphisms
+\begin{corollary}\label{lem:image-basis}
+    Let $P$ be a Petri net with basis $\B$ and let $f : A \rightarrow B$ be a Petri net morphism.
+    Then $f(\B)$ is a basis for $f(P)$.
+\end{corollary}
+\begin{proof}
+    \TODO{Complete}
+\end{proof}
+The property that Petri net morphisms preserve bases is fundamentally important for establishing relationships between basis-dependent quantities computed in one Petri net with those in another.
+
+The Petri net formalism, and the extensions presented in this section, can now be leveraged to define the structure of primary interest in this work: assembly spaces.
+These spaces can be seen as a subclass of Petri nets which admit specific features useful for describing the fewest number of steps required to construct a given object, the assembly index.
+The concepts of subnets and bases will be a key component in the definition of the assembly index, and Petri net morphisms will be indispensible for establishing bounding the value of the assembly index where explict calculation may be infeasible.
+
+\section{Assembly Spaces, Subspaces and Maps}\label{sec:assembly-spaces}
 
@@
 
-\section{The Assembly Index}
+\section{The Assembly Index}\label{sec:assembly-index}
 
@@
 
-\subsection{Bounds on the Assembly Index}
+\subsection{Bounds on the Assembly Index}\label{subsec:assembly-index-bounds}
 

### 2021-05-21 papers/assembly/I/main.tex
Flesh out text for the Assembly Space section

@@
 \newcommand{\B}{\mathcal{B}}
+\newcommand{\C}{\mathcal{C}}
 \newcommand{\G}{\mathcal{G}}
@@
 
-\section{Petri Nets}
+\section{Petri Nets}\label{sec:petri-nets}
 
@@
 There is, of course, a well defined notion of a map between Petri nets, termed here a \textit{Petri net morphism}, which maps sites and transitions of one Petri net into another in a way that is compatible and consistent with the source and target maps of both Petri nets.
-These Petri net morphisms will play a crucial roll in the establishment of bounds for the assembly index in \Cref{sec:assembly-index-bounds}.
+These Petri net morphisms will play a crucial roll in the establishment of bounds for the assembly index in \Cref{subsec:assembly-index-bounds}.
 
@@
 
+This this work, we are specifically interested in determing if it is possible, given some set of starting objects, to assembly a desired product through some sequence of joining (or disjoining) operations.
+If so, how can we assess the minimum number of steps required in the assembly process?
+We will refer to the resulting value as the \textit{assembly index} of the object, and ascribe it to the a combination of the structure of the underlying space of assembly processes (\textit{assembly space}), the chosen set of starting objects (\textit{basis}) and the desired product itself.
+
+We draw on the Petri net formalism described and extended in \Cref{sec:petri-nets} to formally define an \textit{assembly space} as a particular variety of Petri net.
+
 \begin{definition}\label{def:assembly-space}
-    An \textbf{assembly space} $(A, \B_A)$ is a sourceless and sinkless Petri net with basis $\B_A$.
-    Were possible, we will simply write $A$ to denote an assembly space $(A, \B_A)$.
-\end{definition}
-
+    An \textbf{assembly space} $(A, \B_A)$ is a sourceless and sinkless Petri net with a chosen basis $\B_A$.
+    Where possible, we will simply write $A$ to denote an assembly space $(A, \B_A)$.
+\end{definition}
+
+The ligation example, reproduced below and used throughout \Cref{sec:petri-nets}, is in fact an assembly space, provided we endow it with a basis.
+
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [style=site] (A) at (0, 0.8) {$A$};
+                \node [style=site] (B) at (0, -0.8) {$B$};
+                \node [style=site] (C) at (6, -1.6) {$C$};
+                \node [style=site] (AA) at (4, 0.8) {$AA$};
+                \node [style=site] (AB) at (4, -0.8) {$AB$};
+                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
+                \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
+                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
+                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
+                \node [style=transition] (tau4) at (10, 0) {$\delta$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend right=15] (A) to (tau1);
+                \draw [style=arrow, bend left=15] (A) to (tau1);
+                \draw [style=arrow, bend right=15] (A) to (tau2);
+                \draw [style=arrow] (tau1) to (AA);
+                \draw [style=arrow] (B) to (tau2);
+                \draw [style=arrow] (tau2) to (AB);
+                \draw [style=arrow] (AA) to (tau3);
+                \draw [style=arrow] (AB) to (tau3);
+                \draw [style=arrow, bend left=30] (C) to (tau3);
+                \draw [style=arrow] (tau3) to (AAAB);
+                \draw [style=arrow, bend left=30] (tau3) to (C);
+                \draw [style=arrow] (AAAB) to (tau4);
+                \draw [style=arrow, bend right=30] (tau4) to (A);
+                \draw [style=arrow, bend right=30] (tau4) to (AA);
+                \draw [style=arrow, bend left=40] (tau4) to (B);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+As previously discussed, this net admits four possible bases: $\{A,B,C\}$, $\{A,AB,C\}$, $\{AA,AB,C\}$, or $\{C,AAAB\}$.
+In the all of the examples in this sections, we use $\B = \{A,B,C\}$ as the particular basis unless and refer to this this Petri net with $\B$ as the assembly space $\A$.
+
+Assembly spaces, as with Petri nets in general, admit a subnet structure.
+In general, a Petri subnet need now have a specified basis; however, we will require this of subnets of assembly spaces.
+To distinguish the two concepts, we will refer exclusively to \textit{assembly subspaces} which are little more than Petri subnets with a specified basis.
 \begin{definition}\label{def:assembly-subspace}
@@
 
+\TODO{Example Figure}
+
+Assembly subspaces whose basis is a subset of the larger space, such as \red{subexample} from the previous example, will be referred to as \textit{rooted}.
 \begin{definition}\label{def:rooted}
@@
 \end{definition}
-
-\begin{lemma}\label{lem:lower-is-rooted}
-    Let $A$ be an assembly space and let $x \in S(A)$.
-    Then $\downset{x}$ with basis $\B_A \cap S(\downset{x})$ is a rooted assembly subspace of $A$.
-\end{lemma}
-\begin{proof}
-    \TODO{Complete}
-\end{proof}
-
+By restricting ourselves to rooted assembly subspaces we tie the particular processes which they represent to the basis of the larger space.
+We are particularly interested in constructing assembly subspaces which may produce some specific object.
+The subspace relation on the set of all assembly subspaces allows us to partially order the subspaces.
+Our ultimate objective is to then constrain the full set of assembly subspaces by requiring they they contain some desired object and determine which subspaces are minimal.
+However, if we are do not further restrict this subset of subspace to rooted subspaces, we will inevitably yield highly trivial minimal subspaces.
+To elucidate this point, consider the minimal subspaces of $\A$ containing $AB$ with and without the rooting constraint:
+
+\TODO{Example Figure}
+
+Without requiring that the subspaces be rooted, we find that the unenlightening subspace containing only $AB$ as a site and no transitions.
+However, given the rooted constraint, we find only one minimal, rooted assembly subspace.
+The uniqueness of this minimal rooted subspace is possibly misleading; in general, the minimal subpsaces will not be unique.
+This point will be addressed in \Cref{sec:assembly-index}.
+
+As with Petri nets in general, assembly spaces admit structure preserving maps.
+In fact, \textit{assembly maps} are just Petri net morphisms between assembly spaces.
 \begin{definition}\label{def:assembly-map}
     Let $A$ and $B$ be assembly spaces.
-    An \textbf{assembly map} is simply a Petri net map $f: A \rightarrow B$ between assembly spaces.
-\end{definition}
-
+    An \textbf{assembly map} is a Petri net morphism $f: A \rightarrow B$ between assembly spaces.
+\end{definition}
+
+As a simple example of this, consider $\A$ and a map to a second space, here referred to as $\C$.
+
+\TODO{Example Figure}
+
+Of particular note here is that $\A$ is certainly a subspace of $\C$, though it is decidedly not rooted in $\C$.
+In fact, it will always be the case that the image of an assembly space will be a subspace of the codomain.
 \begin{theorem}\label{lem:assembly-image-is-subspace}
@@
 
+Exploring the previous example a bit more, by highlighting a rooted subspace of $\A$ we see that the image of that subspace is rooted in the image of $\A$ in $\C$.
+
+\TODO{Example Figure}
+
+This too will alway be the case: the image of a rooted subspace will always be rooted in the image.
 \begin{theorem}\label{thm:rooted-image}
@@
 
+The interaction of assembly maps and rooted subspaces will allow us to establish bounds on the assembly index, defined in the next section, by considering the image of the space under some map.
+These bounds will be useful in situations where determining the assembly index of some object is computationally infeasible.
+
 \section{The Assembly Index}\label{sec:assembly-index}
@@
     The \textbf{size} of $A$ is the cardinality of $T(A)$, denoted $|A|$.
+\end{definition}
+
+\begin{definition}\label{def:downset}
+    Let $(A, \B_A)$ be an assembly space and let $x$ be a site in $A$.
+    The \textbf{down set} of $x$, denoted $\downset{x}$ in $A$ is the site completion of all pathways from $\B_A$ terminating at $x$.
 \end{definition}
@@
 \end{definition}
+
+\begin{theorem}\label{def:index-existence-uniqueness}
+    Let $A$ be an assembly space and let $x$ be a finite site in $A$.
+    Then the assembly index $c_A(x)$ is exists and is unique.
+\end{theorem}
+\begin{proof}
+    \TODO{Complete: likely requires Zorn's lemma, but maybe not...}
+\end{proof}
 
@@
     \TODO{Complete}
-    % We need only show that $c_A(b)$ cannot be greater than $c_B(b)$ for any $b \in S(B)$.
-    % To see this, let $Z \subseteq B$ be a rooted assembly subspace containing $b$ with $|Z| = c_B(b)$.
-    % Then $Z$ is also a rooted assembly subspace of $A$ containing $b$, and so $c_A(b)$ can be at most $|Z|$.
-    % That is, $c_A(b) \le |Z| = c_B(b)$.
 \end{proof}

### 2021-05-21 papers/assembly/I/main.tex
Flesh out text for the assembly index section

@@
 \newcommand{\G}{\mathcal{G}}
+\newcommand{\SB}{\mathcal{S}}
 \newcommand{\Ini}[1]{\textrm{Ini}(#1)}
@@
 
+With the core formalism established, we can now present the concept of the \textit{assembly index}.
+As we have seen, within the context of an assembly space, the rooted assembly spaces are partially ordered.
+This allows us to inquire about the minimal, rooted assembly subspaces which contain some desirable site.
+Each of these subspaces will consist of some, possibly infinite, number of transitions.
+We refer to the number of transitions in an assembly space as the \textit{size}.
 \begin{definition}\label{def:size}
@@
 \end{definition}
-
-\begin{definition}\label{def:downset}
-    Let $(A, \B_A)$ be an assembly space and let $x$ be a site in $A$.
-    The \textbf{down set} of $x$, denoted $\downset{x}$ in $A$ is the site completion of all pathways from $\B_A$ terminating at $x$.
-\end{definition}
-
+In the running ligation model, $\A$, the size of the entire space is $|\A| = 4$ as there are four transitions.
+Similarly, the minimal, rooted subspace of $\A$ containing $AA$ has size $1$; it contains only one transition, $\alpha$.
+
+We can think of the size of a minimal, rooted subspace containing a given site as counting the number of steps required to assemble that site in a particular way.
+However, it is entirely possible that there is no finite way assembly an site.
+For example, consider a polymer model which consists of combining monomers $A$ and $B$ into polymers of arbitrary length via pairwise joining operations.
+The space of all polymers naturally extends to infinite-length polymers such as $ABABA\ldots$ which require an infinite number of steps to assemble.
+While the abstract assembly space may well contain such sites, we wish to restrict ourselves to sites which can be assembled in finitely many steps.
+We say that such a site if $\textit{finite}$.
 \begin{definition}\label{def:finiteness}
     Let $A$ be an assembly space and let $x$ be a site in $A$.
-    We say that $x$ is \textbf{finite} in $A$ if $\downset{x}$ in $A$ has finite size.
-\end{definition}
-
+    We say that $x$ is \textbf{finite} in $A$ there exists a rooted assembly subspace of $A$ which contains $x$ as a site.
+\end{definition}
+Every site in our running example space, $\A$ is finite.
+In the polymer model, only sites representing polymers with finitely many monomers are finite.
+If we are presented with such a finite site, we can count the size of every rooted assembly subspaces containing that site.
+The least size of these subspaces is the \textit{assembly index} of the site.
 \begin{definition}\label{def:index}
     Let $A$ be an assembly space and let $x$ be a finite site in $A$.
-    The \textbf{assembly index} of $x$ is the minimal size of all rooted assembly subspaces of $A$ containing $x$, and is denoted $c_A(x)$.
+    The \textbf{assembly index} of $x$ is the minimum size of all rooted assembly subspaces of $A$ containing $x$, and is denoted $c_A(x)$.
     This can be written $c(x)$ when the relevant assembly space is clear from context.
 \end{definition}
-
+In this definition, we do not restrict ourselves specifically to minimal subspaces containing the site $x$.
+However, in effect we are.
+If we were to consider the size of a non-minimal, rooted subspace some site $x$, we'd always be able to find some minimal, rooted subspace which contains $x$ and has at most the same size.
+Since we are looking specifically for the \textit{minimum} size of the subspaces, we need to confirm that such a value even exists.
+It does and is in fact unique.
 \begin{theorem}\label{def:index-existence-uniqueness}
@@
 
-\subsection{Bounds on the Assembly Index}\label{subsec:assembly-index-bounds}
-
+To conclude this section, we present the assembly index of every site of in our ligation model $\A$ together with a minimal, rooted assembly subspace containing that site.
+
+\TODO{Complete Figure}
+
+In the next section, we will consider methods for bounding the assembly index of a site.
+
+\subsection{Computability of and Bounds on the Assembly Index}\label{subsec:assembly-index-bounds}
+
+The first task, when presented with an assembly space, is to determine the assembly index of the sites in the space.
+In practical terms, this requires an algorithm for computing the assembly index relative to some space.
+In this work, we do not present a general algorithm to do so, though a simple depth-first search of the space may suffice in some cases.
+Rather, we first show that the assembly index is in fact computable.
+\begin{theorem}\label{thm:computable}
+    If $A$ is an assembly space and $x \in S(A)$ is finite, then $c(x)$ is computable.
+\end{theorem}
+\begin{proof}
+    \TODO{Complete}
+\end{proof}
+Of course, just because the value is computable does not mean that it can be computed in reasonable time.
+In fact, the general problem is likely to be \texttt{NP}-hard.
+In situtations where direct computation is infeasible, we can resort to bounding the value of the assembly index by computing the index in an analogous space.
+The first of the bounds we present is an upper bound determined by computing the assembly index in a subspace containing the site.
 \begin{theorem}\label{cor:subspace-index-upper-bound}
@@
 
+\TODO{Example and Figure}
+
+The second bound we establish is a lower bound determined by mapping the space in question into a space within which computing the assembly index may be simpler.
 \begin{theorem}\label{thm:image-lower-bound}
@@
     \TODO{Complete}
-    % Suppose $x \in S(A)$ is finite, and $Z \subseteq A$ is a rooted with $s \in S(Z)$ and $|Z| = c_A(x)$.
-    % Restricting $f$ to $Z$ provides an assembly map $f^* : Z \rightarrow B$ such that $f(Z)$ contains $f(x)$, and is rooted in $B$.
-    % As such, $c_{f(A)}(f(x))$ can be no larger than $|f(Z)|$, so $c_{f(A)}(f(x)) \le c_A(x)$.
-    %
-    % Furthermore, suppose that $f$ is an embedding, and consider any $Z' \subseteq f(A)$ rooted and containing $f(x)$.
-    % The preimage of $Z'$ under $f$ is then a rooted assembly subspace of $A$ containing $x$, so $c_A(x)$ can be no larger than $|f^{-1}(Z)|$.
-    % Together with the previous result, we then have $c_{f(A)}(f(x)) = c_A(x)$.
 \end{proof}
 
-\begin{corollary}\label{cor:lowerset-index}
-    Let $A$ be an assembly space and $x \in S(A)$ be finite.
-    Then $c_A(x) = c_{x\downarrow}(x)$.
+\TODO{Example and Figure}
+
+Our final bound is a special case of the lower bound derived from an assembly map; however, it represents an upper bound.
+Given an assembly space with no directed loops, which we refer to as \textbf{acyclic}, we can form an analogous assembly space which has a tree-like structure by duplicating sites that participate in more than one transition.
+We refer to such a space as the \textit{split-branch} representation of the space.
+\begin{definition}\label{def:split-branch}
+    Let $A$ be an acyclic assembly space.
+    The \textbf{split-branch} representation of $A$ is $\ldots$.
+
+    \TODO{Doug is leaving this for Stu since it's his jam.}
+\end{definition}
+
+There is a natural assembly map from the split-branch representation of a space to the space itself.
+As such, \Cref{thm:image-lower-bound} applies, and we can produce an upper bound on the assembly index of sites in the original space.
+\begin{corollary}\label{cor:split-branch}
+    Let $A$ be a \red{adjectives} assembly space and let $\SB(A)$ be the split-branch representation of $A$, and let $f : \SB(A)$ such that $\ldots$.
+    For any site $x$ in $A$, the assembly index $c_A(x) \le \min_{x' \in S(f)^{-1}(x)}c_{\SB(A)}(x')$.
 \end{corollary}
 \begin{proof}
-    \TODO{Complete}
-    % There is a natural embedding $i : \downset{x} \rightarrow A$, so $c_A(x) = c_{x\downarrow}(x)$ for all finite $x \in S(A)$, as per \cref{thm:image-lower-bound}.
+    \TODO{Stu to complete? Or Doug can with a workable \Cref{def:split-branch}.}
 \end{proof}
 
-\subsection{Computability and Algorithms}
-
-\begin{theorem}\label{thm:computable}
-    If $A$ is an assembly space and $x \in S(A)$ is finite, then $c(x)$ is computable.
-\end{theorem}
-\begin{proof}
-    \TODO{Complete}
-    % Every rooted assembly subspace with minimal size and containing $x$ is a minimal, rooted assembly subspace of $\downset{x}$.
-    % Since $x$ is finite, $\downset{x}$ is finite; that is $\downset{x}$ has finitely many transitions.
-    % This, together with the fact that $\pi(\sigma(t))$ and $\pi(\tau(t))$ are finite for all $t \in T(A)$, ensures that there areonly finitely many assembly subspaces of $\downset{x}$.
-    % As such, the set of all rooted assembly subspaces is computable; simply enumerate them.
-    % The size of each subspace is, of course, computable as one need simply count the transitions in the subspace.
-    % Finally, finding the minimum value in a finite set of natural numbers is computable.
-    % Thus, $c(x)$ is computable.
-\end{proof}
-
-\TODO{Typeset split-branch algorithm}
-
-\section{Assembly Examples}
-
-\TODO{Come up with a few fun examples.}
+\TODO{Typeset algorithm}
+\red{I need a PDF version of the previous version of the supplement. The formatted algorithm not rendering correctly for me in Word.}
 

### 2021-05-21 papers/assembly/I/main.tex
Remove the definition of a span
Add examples of pathways and generating sets under maps

@@
     \scalebox{0.6}{
-        \begin{tikzpicture}
+        \begin{tikzpicture}\label{ex:map}
             \begin{pgfonlayer}{nodelayer}
@@
 \end{center}
-
-\begin{definition}
-    Let $P$ be a Petri net and let $Q \subseteq P$.
-    We say that $Q$ \textit{spans} $P$ if $S(Q) = S(P)$.
-    \TODO{New Definition. Integrate with surrounding text.}
-\end{definition}
 
@@
     Let $f: P \rightarrow Q$ be a Petri net morphism and let $X, Y \subseteq S(P)$ be pathway connected in $P$.
-    Then either $f(X)$ and $f(Y)$ are pathway connected in $f(P)$.
+    The images $f(X)$ and $f(Y)$ are pathway connected in $f(P)$.
 \end{lemma}
@@
 
-\TODO{Example}
-
-The fact that generating sets are preserved, follows from the preservation of pathways.
+As a specific example, we can consider the pathway $\pathway{\alpha\beta}$ in our ligation model, which starts at $\{A, B\}$ and terminates at $\{AA, AB\}$, under the map describe previously.
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [scale=3] (P) at (12, 0) {$P$};
+                \node [style=site, fill=blue!20] (A) at (0, 0.8) {$A$};
+                \node [style=site, fill=blue!20] (B) at (0, -0.8) {$B$};
+                \node [style=site] (C) at (6, -1.6) {$C$};
+                \node [style=site, fill=red!20] (AA) at (4, 0.8) {$AA$};
+                \node [style=site, fill=red!20] (AB) at (4, -0.8) {$AB$};
+                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
+                \node [style=transition, fill=green!20] (tau1) at (2, 0.8) {$\alpha$};
+                \node [style=transition, fill=green!20] (tau2) at (2, -0.8) {$\beta$};
+                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
+                \node [style=transition] (tau4) at (10, 0) {$\delta$};
+
+                \node [scale=3] (Q) at (12, -6) {$Q$};
+                \node [style=site] (W) at (-4, -6) {$W$};
+                \node [style=site, fill=blue!20] (X) at (0, -6) {$X$};
+                \node [style=site, fill=red!20] (Y) at (4, -6) {$Y$};
+                \node [style=site] (Z) at (8, -6) {$Z$};
+                \node [style=transition] (tau5) at (-2, -6) {$\phi$};
+                \node [style=transition, fill=green!20] (tau6) at (2, -6) {$\chi$};
+                \node [style=transition] (tau7) at (6, -6) {$\psi$};
+                \node [style=transition] (tau8) at (10, -6) {$\omega$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, line width=1.5, draw=red, bend right=15] (A) to (tau1);
+                \draw [style=arrow, line width=1.5, draw=red, bend left=15] (A) to (tau1);
+                \draw [style=arrow, line width=1.5, draw=red, bend right=15] (A) to (tau2);
+                \draw [style=arrow, line width=1.5, draw=red] (tau1) to (AA);
+                \draw [style=arrow, line width=1.5, draw=red] (B) to (tau2);
+                \draw [style=arrow, line width=1.5, draw=red] (tau2) to (AB);
+                \draw [style=arrow, draw=gray!80] (AA) to (tau3);
+                \draw [style=arrow, draw=gray!80] (AB) to (tau3);
+                \draw [style=arrow, draw=gray!80, bend left=30] (C) to (tau3);
+                \draw [style=arrow, draw=gray!80] (tau3) to (AAAB);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau3) to (C);
+                \draw [style=arrow, draw=gray!80] (AAAB) to (tau4);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (A);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (AA);
+                \draw [style=arrow, draw=gray!80, bend left=40] (tau4) to (B);
+
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (A) to (X);
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (B) to (X);
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (AA) to (Y);
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (AB) to (Y);
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (C) to (Y);
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (AAAB) to (Z);
+                \draw [style=transitionmap, opacity=0.5, bend right=30, shorten >=2mm] (tau1) to (tau6);
+                \draw [style=transitionmap, opacity=0.5, bend right=30, shorten >=2mm] (tau2) to (tau6);
+                \draw [style=transitionmap, opacity=0.5, bend right=30, shorten >=2mm] (tau3) to (tau7);
+                \draw [style=transitionmap, opacity=0.5, bend right=30, shorten >=2mm] (tau4) to (tau8);
+
+                \draw [style=arrow, draw=gray!80, bend left=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend right=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend left=15] (tau5) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
+                \draw [style=arrow, line width=1.5, draw=red, bend left=15] (X) to (tau6);
+                \draw [style=arrow, line width=1.5, draw=red, bend right=15] (X) to (tau6);
+                \draw [style=arrow, line width=1.5, draw=red] (tau6) to (Y);
+                \draw [style=arrow, draw=gray!80, bend left=20] (Y) to (tau7);
+                \draw [style=arrow, draw=gray!80] (Y) to (tau7);
+                \draw [style=arrow, draw=gray!80, bend right=20] (Y) to (tau7);
+                \draw [style=arrow, draw=gray!80] (tau7) to (Z);
+                \draw [style=arrow, draw=gray!80, bend left=50] (tau7.south) to (Y.south);
+                \draw [style=arrow, draw=gray!80] (Z) to (tau8);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau8) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (Y);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+Here the starting set of sites is highlight in blue, the terminal sites in red, the transitions in green and relevant edges are emboldened red.
+The images of $\{A,B\}$ and $\{AA,AB\}$ are $\{X\}$ and $\{Y\}$ respectively, and the pathway $\pathway{\alpha\beta}$ is mapped to $\pathway{\chi}$.
+As we've proven, any pathway we choose will map to a pathway.
+From this fact, it follows that generating sets are preserved.
 \begin{lemma}\label{lem:image-of-generating-sets}
@@
 \end{proof}
-
-\TODO{Example Figure}
-
-This is not to say that the only generating sets in the image of a Petri net will be the image of a generating set.
-The codomain of the Petri net morphism may in fact have additional generating sets.
-
-\TODO{Example Figure}
+Identifying a generating set of the ligation model, say $\{A, AB, C\}$, and mapping it forward we see that the result is a generating set of \textit{within the image}:
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [scale=3] (P) at (12, 0) {$P$};
+                \node [style=site, fill=blue!20] (A) at (0, 0.8) {$A$};
+                \node [style=site] (B) at (0, -0.8) {$B$};
+                \node [style=site, fill=blue!20] (C) at (6, -1.6) {$C$};
+                \node [style=site] (AA) at (4, 0.8) {$AA$};
+                \node [style=site, fill=blue!20] (AB) at (4, -0.8) {$AB$};
+                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
+                \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
+                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
+                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
+                \node [style=transition] (tau4) at (10, 0) {$\delta$};
+
+                \node [scale=3] (Q) at (12, -6) {$Q$};
+                \node [style=site] (W) at (-4, -6) {$W$};
+                \node [style=site, fill=blue!20] (X) at (0, -6) {$X$};
+                \node [style=site, fill=blue!20] (Y) at (4, -6) {$Y$};
+                \node [style=site] (Z) at (8, -6) {$Z$};
+                \node [style=transition] (tau5) at (-2, -6) {$\phi$};
+                \node [style=transition] (tau6) at (2, -6) {$\chi$};
+                \node [style=transition] (tau7) at (6, -6) {$\psi$};
+                \node [style=transition] (tau8) at (10, -6) {$\omega$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau1);
+                \draw [style=arrow, draw=gray!80, bend left=15] (A) to (tau1);
+                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau2);
+                \draw [style=arrow, draw=gray!80] (tau1) to (AA);
+                \draw [style=arrow, draw=gray!80] (B) to (tau2);
+                \draw [style=arrow, draw=gray!80] (tau2) to (AB);
+                \draw [style=arrow, draw=gray!80] (AA) to (tau3);
+                \draw [style=arrow, draw=gray!80] (AB) to (tau3);
+                \draw [style=arrow, draw=gray!80, bend left=30] (C) to (tau3);
+                \draw [style=arrow, draw=gray!80] (tau3) to (AAAB);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau3) to (C);
+                \draw [style=arrow, draw=gray!80] (AAAB) to (tau4);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (A);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (AA);
+                \draw [style=arrow, draw=gray!80, bend left=40] (tau4) to (B);
+
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (A) to (X);
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (B) to (X);
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (AA) to (Y);
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (AB) to (Y);
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (C) to (Y);
+                \draw [style=sitemap, opacity=0.5, bend right=30, shorten >=2mm] (AAAB) to (Z);
+                \draw [style=transitionmap, opacity=0.5, bend right=30, shorten >=2mm] (tau1) to (tau6);
+                \draw [style=transitionmap, opacity=0.5, bend right=30, shorten >=2mm] (tau2) to (tau6);
+                \draw [style=transitionmap, opacity=0.5, bend right=30, shorten >=2mm] (tau3) to (tau7);
+                \draw [style=transitionmap, opacity=0.5, bend right=30, shorten >=2mm] (tau4) to (tau8);
+
+                \draw [style=arrow, draw=gray!80, bend left=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend right=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend left=15] (tau5) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
+                \draw [style=arrow, draw=red!50, bend left=15] (X) to (tau6);
+                \draw [style=arrow, draw=red!50, bend right=15] (X) to (tau6);
+                \draw [style=arrow, draw=red!50] (tau6) to (Y);
+                \draw [style=arrow, draw=red!50, bend left=20] (Y) to (tau7);
+                \draw [style=arrow, draw=red!50] (Y) to (tau7);
+                \draw [style=arrow, draw=red!50, bend right=20] (Y) to (tau7);
+                \draw [style=arrow, draw=red!50] (tau7) to (Z);
+                \draw [style=arrow, draw=red!50, bend left=50] (tau7.south) to (Y.south);
+                \draw [style=arrow, draw=red!50] (Z) to (tau8);
+                \draw [style=arrow, draw=red!50, bend left=30] (tau8) to (X);
+                \draw [style=arrow, draw=red!50, bend right=30] (tau8) to (X);
+                \draw [style=arrow, draw=red!50, bend right=30] (tau8) to (Y);
+
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+where the generating set $\{A, AB, C\}$ is mapped into the set $\{X, Y\}$, both blue.
+The set $\{X, Y\}$ generates the entire image of $P$, whose edges are red.
+This is not to say that the only generating sets in the image of a Petri net will be the image of a generating set, for example $\{X\}$ is generating in the image $f(P)$ but its preimage $\{A,B\}$ is not.
 

### 2021-05-21 papers/assembly/I/main.tex
Annotate some painpoints regarding bases.
Petri net morphisms do not, in general, preserve bases. Given that's
case, we may have to losen our definition of an Assembly space to "a
special Petri net with chosen generating set".

@@
 This is not to say that the only generating sets in the image of a Petri net will be the image of a generating set, for example $\{X\}$ is generating in the image $f(P)$ but its preimage $\{A,B\}$ is not.
-
-Still, the fact that generating sets are preserved yields nicely our final result: bases are preserved under Petri net morphisms
-\begin{corollary}\label{lem:image-basis}
-    Let $P$ be a Petri net with basis $\B$ and let $f : A \rightarrow B$ be a Petri net morphism.
-    Then $f(\B)$ is a basis for $f(P)$.
-\end{corollary}
-\begin{proof}
-    \TODO{Complete}
-\end{proof}
-The property that Petri net morphisms preserve bases is fundamentally important for establishing relationships between basis-dependent quantities computed in one Petri net with those in another.
+The property that Petri net morphisms preserve generating sets is fundamentally important for establishing relationships between generator-dependent quantities computed in one Petri net with those in another.
 
@@
 
-This too will alway be the case: the image of a rooted subspace will always be rooted in the image.
+This too will always be the case: the image of a rooted subspace will always be rooted in the image.
 \begin{theorem}\label{thm:rooted-image}
@@
     Then $(f(Z), S(f)(\B_Z))$ is rooted in $(f(A), S(f)(\B_A)$.
+
+    \TODO{This almost certainly isn't true as defined at present.
+Assembly maps do not, in general, preserve the basis, $S(f)(\B_A)$ and $S(f)(\B_Z)$ are probably not bases.
+That said, we might not actually need this.
+It'll depend on how the proof of \Cref{thm:image-lower-bound} go.}
 \end{theorem}
@@
 The first of the bounds we present is an upper bound determined by computing the assembly index in a subspace containing the site.
-\begin{theorem}\label{cor:subspace-index-upper-bound}
+\begin{theorem}\label{thm:subspace-index-upper-bound}
     Let $(A, \B_A)$ be an assembly space and let $(B, \B_A)$ be a rooted assembly subspace of $A$.
@@
     \TODO{Complete}
+
+    \red{This may suffer from the fact that assembly maps do not preserve bases. If that's the case, we should rip all mention of bases out for a future work.}
 \end{proof}

### 2021-05-21 papers/assembly/I/main.tex
Flesh out examples throught Thm 1

@@
             \begin{pgfonlayer}{nodelayer}
-                \node [style=site] (A) at (0, 0.8) {$A$};
-                \node [style=site] (B) at (0, -0.8) {$B$};
-                \node [style=site] (C) at (6, -1.6) {$C$};
+                \node [style=site, fill=blue!20] (A) at (0, 0.8) {$A$};
+                \node [style=site, fill=blue!20] (B) at (0, -0.8) {$B$};
+                \node [style=site, fill=blue!20] (C) at (6, -1.6) {$C$};
                 \node [style=site] (AA) at (4, 0.8) {$AA$};
@@
 As previously discussed, this net admits four possible bases: $\{A,B,C\}$, $\{A,AB,C\}$, $\{AA,AB,C\}$, or $\{C,AAAB\}$.
-In the all of the examples in this sections, we use $\B = \{A,B,C\}$ as the particular basis unless and refer to this this Petri net with $\B$ as the assembly space $\A$.
+In the all of the examples in this sections, we use $\B = \{A,B,C\}$ (highlighted in blue) as the particular basis unless and refer to this this Petri net with $\B$ as the assembly space $\A$.
 
@@
 \end{definition}
-
-\TODO{Example Figure}
-
-Assembly subspaces whose basis is a subset of the larger space, such as \red{subexample} from the previous example, will be referred to as \textit{rooted}.
+The example space $\A$ admits a number of subspaces, a few of which are depicted below.
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [style=site, fill=blue!20] (A) at (0,  1.6) {$A$};
+                \node [style=site, fill=blue!20] (B) at (0,  0.0) {$B$};
+                \node [style=site, fill=blue!20] (C) at (0, -1.6) {$C$};
+                \node [scale=2] at (0, -3.6) {a.};
+
+                \node [style=site, fill=blue!20] (A1) at (4,  0.8) {$A$};
+                \node [style=site, fill=blue!20] (B1) at (4, -0.8) {$B$};
+                \node [style=transition] (alpha) at (6, 0.8) {$\alpha$};
+                \node [style=transition] (beta) at (6, -0.8) {$\beta$};
+                \node [style=site] (AA1) at (8, 0.8) {$AA$};
+                \node [style=site] (AB1) at (8, -0.8) {$AB$};
+                \node [scale=2] at (6, -3.6) {b.};
+
+                \node [style=site, fill=blue!20] (AA2) at (12, 0.8) {$AA$};
+                \node [style=site, fill=blue!20] (AB2) at (12, -0.8) {$AB$};
+                \node [style=site, fill=blue!20] (C2) at (14, -1.6) {$C$};
+                \node [style=transition] (gamma) at (14, 0) {$\gamma$};
+                \node [style=site] (AAAB) at (16, 0) {$AAAB$};
+                \node [scale=2] at (14, -3.6) {c.};
+
+                \node [style=site, fill=blue!20] (A3) at (20,  0.8) {$A$};
+                \node [style=site, fill=blue!20] (B3) at (20, -0.8) {$B$};
+                \node [style=transition] (alpha3) at (22, 0.8) {$\alpha$};
+                \node [style=transition] (beta3) at (22, -0.8) {$\beta$};
+                \node [style=site] (AA3) at (24, 0.8) {$AA$};
+                \node [style=site] (AB3) at (24, -0.8) {$AB$};
+                \node [style=site, fill=blue!20] (C3) at (26, -1.6) {$C$};
+                \node [style=transition] (gamma3) at (26, 0) {$\gamma$};
+                \node [style=site] (AAAB3) at (28, 0) {$AAAB$};
+                \node [scale=2] at (24, -3.6) {d.};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend right=15] (A1) to (alpha);
+                \draw [style=arrow, bend left=15] (A1) to (alpha);
+                \draw [style=arrow, bend right=15] (A1) to (beta);
+                \draw [style=arrow] (alpha) to (AA1);
+                \draw [style=arrow] (B1) to (beta);
+                \draw [style=arrow] (beta) to (AB1);
+
+                \draw [style=arrow] (AA2) to (gamma);
+                \draw [style=arrow] (AB2) to (gamma);
+                \draw [style=arrow, bend left=30] (C2) to (gamma);
+                \draw [style=arrow, bend left=30] (gamma) to (C2);
+                \draw [style=arrow] (gamma) to (AAAB);
+
+                \draw [style=arrow, bend right=15] (A3) to (alpha3);
+                \draw [style=arrow, bend left=15] (A3) to (alpha3);
+                \draw [style=arrow, bend right=15] (A3) to (beta3);
+                \draw [style=arrow] (alpha3) to (AA3);
+                \draw [style=arrow] (B3) to (beta3);
+                \draw [style=arrow] (beta3) to (AB3);
+                \draw [style=arrow] (AA3) to (gamma3);
+                \draw [style=arrow] (AB3) to (gamma3);
+                \draw [style=arrow, bend left=30] (C3) to (gamma3);
+                \draw [style=arrow, bend left=30] (gamma3) to (C3);
+                \draw [style=arrow] (gamma3) to (AAAB3);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+In all of these cases, we've highlighted the chosen (and in fact only) basis for the subspace.
+Some of these subspaces are quite trivial, such as \textbf{a.}, while the others capture some information about the way in which some objects be be assembled.
+In subspace \textbf{c.} we can see that the basis has sites which are not in the basis of $\A$, while the other spaces $\textbf{a.}$, $\textbf{b.}$ and $\textbf{d.}$ do not.
+Consequently, \textbf{c.} does not tie the assembly of $AAAB$ to the chosen basis of the $\A$.
+Assembly subspaces whose basis is a subset of the larger space will be referred to as \textit{rooted}.
 \begin{definition}\label{def:rooted}
@@
 To elucidate this point, consider the minimal subspaces of $\A$ containing $AB$ with and without the rooting constraint:
-
-\TODO{Example Figure}
-
-Without requiring that the subspaces be rooted, we find that the unenlightening subspace containing only $AB$ as a site and no transitions.
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [style=site, fill=blue!20] (AB) at (0, 0) {$AB$};
+                \node [scale=2] at (0, -2.8) {a. Not Rooted in $\A$};
+
+                \node [style=site, fill=blue!20] (A1) at (6,  0.8) {$A$};
+                \node [style=site, fill=blue!20] (B1) at (6, -0.8) {$B$};
+                \node [style=transition] (beta1) at (8, 0) {$\beta$};
+                \node [style=site] (AB1) at (10, 0) {$AB$};
+                \node [scale=2] at (8, -2.8) {b. Rooted in $\A$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow] (A1) to (beta1);
+                \draw [style=arrow] (B1) to (beta1);
+                \draw [style=arrow] (beta1) to (AB1);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+Without requiring that the subspaces be rooted, we find the unenlightening subspace containing only $AB$ as a site and no transitions.
 However, given the rooted constraint, we find only one minimal, rooted assembly subspace.
-The uniqueness of this minimal rooted subspace is possibly misleading; in general, the minimal subpsaces will not be unique.
-This point will be addressed in \Cref{sec:assembly-index}.
+The uniqueness of this minimal, rooted subspace is possibly misleading; in general, the minimal subpsaces will not be unique.
+This point will be further addressed in \Cref{sec:assembly-index}.
 
@@
 
-As a simple example of this, consider $\A$ and a map to a second space, here referred to as $\C$.
-
-\TODO{Example Figure}
-
+As an example of an assembly map, we can use the example map from the Petri net section:
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}\label{ex:map}
+            \begin{pgfonlayer}{nodelayer}
+                \node [scale=3] (P) at (12, 0) {$\A$};
+                \node [style=site, fill=blue!20] (A) at (0, 0.8) {$A$};
+                \node [style=site, fill=blue!20] (B) at (0, -0.8) {$B$};
+                \node [style=site, fill=blue!20] (C) at (6, -1.6) {$C$};
+                \node [style=site] (AA) at (4, 0.8) {$AA$};
+                \node [style=site] (AB) at (4, -0.8) {$AB$};
+                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
+                \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
+                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
+                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
+                \node [style=transition] (tau4) at (10, 0) {$\delta$};
+
+                \node [scale=3] (Q) at (12, -6) {$\C$};
+                \node [style=site, fill=blue!20] (W) at (-4, -6) {$W$};
+                \node [style=site] (X) at (0, -6) {$X$};
+                \node [style=site] (Y) at (4, -6) {$Y$};
+                \node [style=site] (Z) at (8, -6) {$Z$};
+                \node [style=transition] (tau5) at (-2, -6) {$\phi$};
+                \node [style=transition] (tau6) at (2, -6) {$\chi$};
+                \node [style=transition] (tau7) at (6, -6) {$\psi$};
+                \node [style=transition] (tau8) at (10, -6) {$\omega$};
+
+                \node [text=red, scale=2] (s) at (-2, -2.5) {$S(f)$};
+                \node [text=blue, scale=2] (t) at (0, -3.5) {$T(f)$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau1);
+                \draw [style=arrow, draw=gray!80, bend left=15] (A) to (tau1);
+                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau2);
+                \draw [style=arrow, draw=gray!80] (tau1) to (AA);
+                \draw [style=arrow, draw=gray!80] (B) to (tau2);
+                \draw [style=arrow, draw=gray!80] (tau2) to (AB);
+                \draw [style=arrow, draw=gray!80] (AA) to (tau3);
+                \draw [style=arrow, draw=gray!80] (AB) to (tau3);
+                \draw [style=arrow, draw=gray!80, bend left=30] (C) to (tau3);
+                \draw [style=arrow, draw=gray!80] (tau3) to (AAAB);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau3) to (C);
+                \draw [style=arrow, draw=gray!80] (AAAB) to (tau4);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (A);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (AA);
+                \draw [style=arrow, draw=gray!80, bend left=40] (tau4) to (B);
+
+                \draw [style=arrow, draw=gray!80, bend left=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend right=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend left=15] (tau5) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
+                \draw [style=arrow, draw=gray!80, bend left=15] (X) to (tau6);
+                \draw [style=arrow, draw=gray!80, bend right=15] (X) to (tau6);
+                \draw [style=arrow, draw=gray!80] (tau6) to (Y);
+                \draw [style=arrow, draw=gray!80, bend left=20] (Y) to (tau7);
+                \draw [style=arrow, draw=gray!80] (Y) to (tau7);
+                \draw [style=arrow, draw=gray!80, bend right=20] (Y) to (tau7);
+                \draw [style=arrow, draw=gray!80] (tau7) to (Z);
+                \draw [style=arrow, draw=gray!80, bend left=50] (tau7.south) to (Y.south);
+                \draw [style=arrow, draw=gray!80] (Z) to (tau8);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau8) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (Y);
+
+                \draw [style=sitemap, bend right=30] (A) to (X);
+                \draw [style=sitemap, bend right=30] (B) to (X);
+                \draw [style=sitemap, bend right=30] (AA) to (Y);
+                \draw [style=sitemap, bend right=30] (AB) to (Y);
+                \draw [style=sitemap, bend right=30] (C) to (Y);
+                \draw [style=sitemap, bend right=30] (AAAB) to (Z);
+                \draw [style=transitionmap, bend right=30] (tau1) to (tau6);
+                \draw [style=transitionmap, bend right=30] (tau2) to (tau6);
+                \draw [style=transitionmap, bend right=30] (tau3) to (tau7);
+                \draw [style=transitionmap, bend right=30] (tau4) to (tau8);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+were we've chosen $\{A,B,C\}$ and $\{W\}$ as the bases for $\A$ and $\C$, respectively.  
 Of particular note here is that $\A$ is certainly a subspace of $\C$, though it is decidedly not rooted in $\C$.

### 2021-05-21 papers/assembly/I/main.tex
Religate the concept of a basis to a tangent

@@
 \newcommand{\N}{\mathbb{N}}
-\newcommand{\B}{\mathcal{B}}
+% \newcommand{\B}{\mathcal{B}}
 \newcommand{\C}{\mathcal{C}}
@@
 We quickly come to the conclusion that a Petri network is appropriate when we consider this kind of process in general, though with specific modifications to allow the types of questions in which we are interested to be well defined.
-As such, the fundamental mathematical structure we define and explore herein, referred to as an assembly space, can be described as a sourceless, sinkless Petri net with a chosen basis.
+As such, the fundamental mathematical structure we define and explore herein, referred to as an assembly space, can be described as a sourceless, sinkless Petri net with a chosen generating set.
 The details of this description will, of course, be made precise below.
-With assembly spaces defined, we are then able to define an assembly index for each object in the space, relative to the chosen basis, which characterizes how directly that object can be assembled.
+With assembly spaces defined, we are then able to define an assembly index for each object in the space, relative to the chosen generating set, which characterizes how directly that object can be assembled.
 Further, we prove several theorems relating to method of bounding the assembly index for a given object and algorithms for computing or approximating it.
@@
 
+{
+\color{red}
+\TODO{Rework this text}
 The ligation example admits a choice of basis: $\{A,B,C\}$, $\{A,AB,C\}$, $\{AA,AB,C\}$, or $\{C,AAAB\}$.
@@
 \end{proof}
+}
 
@@
 
-The value of identifying initial sites is that they are necessarily elements of every basis, and if the set of initial sites is a basis in its own right, then it is the only basis.
+The value of identifying initial sites is that they are necessarily elements of every generating set, and if the set of initial sites is a generating set in its own right, then it is the only basis.
 \begin{lemma}\label{lem:initial-are-basic}
     Let $P$ be a Petri net.
-    For any basis $\B$ of $P$, $\Ini{P} \subseteq \B$.
+    For any generating set $G$ of $P$, $\Ini{P} \subseteq G$.
     Furthermore, if $\Ini{P}$ is a basis, then it is a unique basis for $P$.
@@
 
-Our final concern regaring Petri nets is whether or not bases are are preserved under Petri net morphisms.
-To establish that this is the case, we must first show that if two sets of sites are pathway connected, then they will be pathway connected in the image of a Petri net morphism.
+Our final concern regaring Petri nets is whether or not generating sets and bases are preserved under Petri net morphisms.
+To establish that this is the case for generating sets, we must first show that if two sets of sites are pathway connected, then they will be pathway connected in the image of a Petri net morphism.
 \begin{lemma}\label{lem:image-of-pathways}
@@
 This is not to say that the only generating sets in the image of a Petri net will be the image of a generating set, for example $\{X\}$ is generating in the image $f(P)$ but its preimage $\{A,B\}$ is not.
+Additionally, this examples provides a counter example for the assertion that bases are preserved under Petri net morphisms since $\{A, AB, C\}$ is a basis for $P$, but $\{X, Y\}$ is not a basis for $f(P)$ -- both $\{X\}$ and $\{Y\}$ are generating sets for $f(P)$ and subsets of $\{X, Y\}$.
+This religates the concept of a basis to simply a special class of generating set that might be preferable in some ways, namely minimality, to a generic generating set.
 The property that Petri net morphisms preserve generating sets is fundamentally important for establishing relationships between generator-dependent quantities computed in one Petri net with those in another.
@@
 These spaces can be seen as a subclass of Petri nets which admit specific features useful for describing the fewest number of steps required to construct a given object, the assembly index.
-The concepts of subnets and bases will be a key component in the definition of the assembly index, and Petri net morphisms will be indispensible for establishing bounding the value of the assembly index where explict calculation may be infeasible.
+The concepts of subnets and generating sets will be a key component in the definition of the assembly index, and Petri net morphisms will be indispensible for establishing bounding the value of the assembly index where explict calculation may be infeasible.
 
@@
 If so, how can we assess the minimum number of steps required in the assembly process?
-We will refer to the resulting value as the \textit{assembly index} of the object, and ascribe it to the a combination of the structure of the underlying space of assembly processes (\textit{assembly space}), the chosen set of starting objects (\textit{basis}) and the desired product itself.
+We will refer to the resulting value as the \textit{assembly index} of the object, and ascribe it to the a combination of the structure of the underlying space of assembly processes (\textit{assembly space}), the chosen set of starting objects (\textit{generating set}) and the desired product itself.
 
@@
 \begin{definition}\label{def:assembly-space}
-    An \textbf{assembly space} $(A, \B_A)$ is a sourceless and sinkless Petri net with a chosen basis $\B_A$.
-    Where possible, we will simply write $A$ to denote an assembly space $(A, \B_A)$.
-\end{definition}
-
-The ligation example, reproduced below and used throughout \Cref{sec:petri-nets}, is in fact an assembly space, provided we endow it with a basis.
-
+    An \textbf{assembly space} $(A, G_A)$ is a sourceless and sinkless Petri net with a chosen generating set $G_A$ of $A$.
+    Where possible, we will simply write $A$ to denote an assembly space $(A, G_A)$.
+\end{definition}
+
+The ligation example, used throughout \Cref{sec:petri-nets} and reproduced below, is in fact an assembly space, provided we choose a generating set.
 \begin{center}
@@
 \end{center}
-As previously discussed, this net admits four possible bases: $\{A,B,C\}$, $\{A,AB,C\}$, $\{AA,AB,C\}$, or $\{C,AAAB\}$.
-In the all of the examples in this sections, we use $\B = \{A,B,C\}$ (highlighted in blue) as the particular basis unless and refer to this this Petri net with $\B$ as the assembly space $\A$.
+As previously discussed, this net admits four possible bases ($\{A,B,C\}$, $\{A,AB,C\}$, $\{AA,AB,C\}$, or $\{C,AAAB\}$) and numerous, non-minimal generating sets.
+In the all of the examples in this sections, we use $G = \{A,B,C\}$ (highlighted in blue) as the particular generating set unless and refer to this this Petri net with $G$ as the assembly space $\A$.
 
 Assembly spaces, as with Petri nets in general, admit a subnet structure.
-In general, a Petri subnet need now have a specified basis; however, we will require this of subnets of assembly spaces.
-To distinguish the two concepts, we will refer exclusively to \textit{assembly subspaces} which are little more than Petri subnets with a specified basis.
+In general, a Petri subnet need now have a specified generating set; however, we will require this of subnets of assembly spaces.
+To distinguish the two concepts, we will refer exclusively to \textit{assembly subspaces} which are little more than Petri subnets with a chosen generating set.
 \begin{definition}\label{def:assembly-subspace}
@@
 \end{center}
-In all of these cases, we've highlighted the chosen (and in fact only) basis for the subspace.
+In all of these cases, we've highlighted the chosen generating set for the subspace which is in fact the only basis for each.
 Some of these subspaces are quite trivial, such as \textbf{a.}, while the others capture some information about the way in which some objects be be assembled.
-In subspace \textbf{c.} we can see that the basis has sites which are not in the basis of $\A$, while the other spaces $\textbf{a.}$, $\textbf{b.}$ and $\textbf{d.}$ do not.
-Consequently, \textbf{c.} does not tie the assembly of $AAAB$ to the chosen basis of the $\A$.
-Assembly subspaces whose basis is a subset of the larger space will be referred to as \textit{rooted}.
+In subspace \textbf{c.} we can see that the generating set has sites which are not in the generating set of $\A$, while the other spaces $\textbf{a.}$, $\textbf{b.}$ and $\textbf{d.}$ do not.
+Consequently, \textbf{c.} does not tie the assembly of $AAAB$ to the chosen generating set of the $\A$.
+Assembly subspaces whose generating set is a subset of the larger space will be referred to as \textit{rooted}.
 \begin{definition}\label{def:rooted}
-    Let $(A', \B_{A'})$ be an assembly subspace of $(A, \B_A)$.
-    We say that $A'$ is rooted in $A$ if $\B_{A'} \subseteq \B_A$.
-\end{definition}
-By restricting ourselves to rooted assembly subspaces we tie the particular processes which they represent to the basis of the larger space.
+    Let $(A', G_{A'})$ be an assembly subspace of $(A, G_A)$.
+    We say that $A'$ is rooted in $A$ if $G_{A'} \subseteq G_A$.
+\end{definition}
+By restricting ourselves to rooted assembly subspaces we tie the particular processes which they represent to the generating set of the larger space.
 We are particularly interested in constructing assembly subspaces which may produce some specific object.
@@
 \end{center}
-were we've chosen $\{A,B,C\}$ and $\{W\}$ as the bases for $\A$ and $\C$, respectively.  
+were we've chosen $\{A,B,C\}$ and $\{W\}$ as the generating sets (in fact, bases) for $\A$ and $\C$, respectively.  
 Of particular note here is that $\A$ is certainly a subspace of $\C$, though it is decidedly not rooted in $\C$.
@@
     Let $A$ be an assembly space, $Z \subseteq A$ a rooted assembly subspace, and $f : A \rightarrow B$ an assembly map.
-    Then $(f(Z), S(f)(\B_Z))$ is rooted in $(f(A), S(f)(\B_A)$.
-
-    \TODO{This almost certainly isn't true as defined at present.
-Assembly maps do not, in general, preserve the basis, $S(f)(\B_A)$ and $S(f)(\B_Z)$ are probably not bases.
-That said, we might not actually need this.
-It'll depend on how the proof of \Cref{thm:image-lower-bound} go.}
+    Then $(f(Z), S(f)(G_Z))$ is rooted in $(f(A), S(f)(G_A)$.
 \end{theorem}
@@
 \end{proof}
-
 The interaction of assembly maps and rooted subspaces will allow us to establish bounds on the assembly index, defined in the next section, by considering the image of the space under some map.
@@
 \begin{theorem}\label{thm:subspace-index-upper-bound}
-    Let $(A, \B_A)$ be an assembly space and let $(B, \B_A)$ be a rooted assembly subspace of $A$.
+    Let $(A, G_A)$ be an assembly space and let $(B, G_A)$ be a rooted assembly subspace of $A$.
     For every finite $b \in S(B)$, the assembly index of $b$ in $B$ is at least the assembly index of $b$ in $A$.
@@
     \TODO{Complete}
-
-    \red{This may suffer from the fact that assembly maps do not preserve bases. If that's the case, we should rip all mention of bases out for a future work.}
 \end{proof}

### 2021-05-22 papers/assembly/I/main.tex
Finish the last of the examples

@@
 There is, of course, a well defined notion of a map between Petri nets, termed here a \textit{Petri net morphism}, which maps sites and transitions of one Petri net into another in a way that is compatible and consistent with the source and target maps of both Petri nets.
-These Petri net morphisms will play a crucial roll in the establishment of bounds for the assembly index in \Cref{subsec:assembly-index-bounds}.
+These Petri net morphisms will play a crucial roll in the establishment of bounds for the assembly index in \Cref{sec:assembly-index}.
 
@@
 
-{
-\color{red}
-\TODO{Rework this text}
 The ligation example admits a choice of basis: $\{A,B,C\}$, $\{A,AB,C\}$, $\{AA,AB,C\}$, or $\{C,AAAB\}$.
@@
 \end{proof}
-}
 
@@
     \scalebox{0.6}{
-        \begin{tikzpicture}\label{ex:map}
+        \begin{tikzpicture}
             \begin{pgfonlayer}{nodelayer}
@@
                 \node [style=site, fill=blue!20] (W) at (-4, -6) {$W$};
-                \node [style=site] (X) at (0, -6) {$X$};
-                \node [style=site] (Y) at (4, -6) {$Y$};
-                \node [style=site] (Z) at (8, -6) {$Z$};
+                \node [style=site, draw=ForestGreen] (X) at (0, -6) {$X$};
+                \node [style=site, draw=ForestGreen] (Y) at (4, -6) {$Y$};
+                \node [style=site, draw=ForestGreen] (Z) at (8, -6) {$Z$};
                 \node [style=transition] (tau5) at (-2, -6) {$\phi$};
-                \node [style=transition] (tau6) at (2, -6) {$\chi$};
-                \node [style=transition] (tau7) at (6, -6) {$\psi$};
-                \node [style=transition] (tau8) at (10, -6) {$\omega$};
+                \node [style=transition, draw=ForestGreen] (tau6) at (2, -6) {$\chi$};
+                \node [style=transition, draw=ForestGreen] (tau7) at (6, -6) {$\psi$};
+                \node [style=transition, draw=ForestGreen] (tau8) at (10, -6) {$\omega$};
 
@@
                 \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
-                \draw [style=arrow, draw=gray!80, bend left=15] (X) to (tau6);
-                \draw [style=arrow, draw=gray!80, bend right=15] (X) to (tau6);
-                \draw [style=arrow, draw=gray!80] (tau6) to (Y);
-                \draw [style=arrow, draw=gray!80, bend left=20] (Y) to (tau7);
-                \draw [style=arrow, draw=gray!80] (Y) to (tau7);
-                \draw [style=arrow, draw=gray!80, bend right=20] (Y) to (tau7);
-                \draw [style=arrow, draw=gray!80] (tau7) to (Z);
-                \draw [style=arrow, draw=gray!80, bend left=50] (tau7.south) to (Y.south);
-                \draw [style=arrow, draw=gray!80] (Z) to (tau8);
-                \draw [style=arrow, draw=gray!80, bend left=30] (tau8) to (X);
-                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (X);
-                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (Y);
+                \draw [style=arrow, draw=ForestGreen, bend left=15] (X) to (tau6);
+                \draw [style=arrow, draw=ForestGreen, bend right=15] (X) to (tau6);
+                \draw [style=arrow, draw=ForestGreen] (tau6) to (Y);
+                \draw [style=arrow, draw=ForestGreen, bend left=20] (Y) to (tau7);
+                \draw [style=arrow, draw=ForestGreen] (Y) to (tau7);
+                \draw [style=arrow, draw=ForestGreen, bend right=20] (Y) to (tau7);
+                \draw [style=arrow, draw=ForestGreen] (tau7) to (Z);
+                \draw [style=arrow, draw=ForestGreen, bend left=50] (tau7.south) to (Y.south);
+                \draw [style=arrow, draw=ForestGreen] (Z) to (tau8);
+                \draw [style=arrow, draw=ForestGreen, bend left=30] (tau8) to (X);
+                \draw [style=arrow, draw=ForestGreen, bend right=30] (tau8) to (X);
+                \draw [style=arrow, draw=ForestGreen, bend right=30] (tau8) to (Y);
 
@@
 were we've chosen $\{A,B,C\}$ and $\{W\}$ as the generating sets (in fact, bases) for $\A$ and $\C$, respectively.
-Of particular note here is that $\A$ is certainly a subspace of $\C$, though it is decidedly not rooted in $\C$.
-In fact, it will always be the case that the image of an assembly space will be a subspace of the codomain.
+Of particular note here is that $f(\A)$ (outlined in red) is a subspace of $\C$.
+It will always be the case that the image of an assembly space will be a subspace of the codomain.
 \begin{theorem}\label{lem:assembly-image-is-subspace}
@@
 \end{proof}
-
-Exploring the previous example a bit more, by highlighting a rooted subspace of $\A$ we see that the image of that subspace is rooted in the image of $\A$ in $\C$.
-
-\TODO{Example Figure}
-
+While $f(\A)$ is a subspace of $\C$, it is decidedly not rooted in $\C$.
+However, by highlighting a rooted subspace of $\A$ we see that the image of that subspace is rooted in $f(\A)$.
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [scale=3] (P) at (12, 0) {$\A$};
+                \node [style=site, fill=blue!20, draw=red, line width=1.5] (A) at (0, 0.8) {$A$};
+                \node [style=site, fill=blue!20, draw=red, line width=1.5] (B) at (0, -0.8) {$B$};
+                \node [style=site] (C) at (6, -1.6) {$C$};
+                \node [style=site, draw=red, line width=1.5] (AA) at (4, 0.8) {$AA$};
+                \node [style=site, draw=red, line width=1.5] (AB) at (4, -0.8) {$AB$};
+                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
+                \node [style=transition, draw=red, line width=1.5] (tau1) at (2, 0.8) {$\alpha$};
+                \node [style=transition, draw=red, line width=1.5] (tau2) at (2, -0.8) {$\beta$};
+                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
+                \node [style=transition] (tau4) at (10, 0) {$\delta$};
+
+                \node [scale=3] (Q) at (12, -6) {$\C$};
+                \node [style=site, fill=blue!20] (W) at (-4, -6) {$W$};
+                \node [style=site, draw=red, line width=1.5] (X) at (0, -6) {$X$};
+                \node [style=site, draw=red, line width=1.5] (Y) at (4, -6) {$Y$};
+                \node [style=site, draw=ForestGreen] (Z) at (8, -6) {$Z$};
+                \node [style=transition] (tau5) at (-2, -6) {$\phi$};
+                \node [style=transition, draw=red, line width=1.5] (tau6) at (2, -6) {$\chi$};
+                \node [style=transition, draw=ForestGreen] (tau7) at (6, -6) {$\psi$};
+                \node [style=transition, draw=ForestGreen] (tau8) at (10, -6) {$\omega$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, draw=red, line width=1.5, bend right=15] (A) to (tau1);
+                \draw [style=arrow, draw=red, line width=1.5, bend left=15] (A) to (tau1);
+                \draw [style=arrow, draw=red, line width=1.5, bend right=15] (A) to (tau2);
+                \draw [style=arrow, draw=red, line width=1.5] (tau1) to (AA);
+                \draw [style=arrow, draw=red, line width=1.5] (B) to (tau2);
+                \draw [style=arrow, draw=red, line width=1.5] (tau2) to (AB);
+                \draw [style=arrow, draw=gray!80] (AA) to (tau3);
+                \draw [style=arrow, draw=gray!80] (AB) to (tau3);
+                \draw [style=arrow, draw=gray!80, bend left=30] (C) to (tau3);
+                \draw [style=arrow, draw=gray!80] (tau3) to (AAAB);
+                \draw [style=arrow, draw=gray!80, bend left=30] (tau3) to (C);
+                \draw [style=arrow, draw=gray!80] (AAAB) to (tau4);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (A);
+                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (AA);
+                \draw [style=arrow, draw=gray!80, bend left=40] (tau4) to (B);
+
+                \draw [style=arrow, draw=gray!80, bend left=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend right=15] (W) to (tau5);
+                \draw [style=arrow, draw=gray!80, bend left=15] (tau5) to (X);
+                \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
+                \draw [style=arrow, draw=red, line width=1.5, bend left=15] (X) to (tau6);
+                \draw [style=arrow, draw=red, line width=1.5, bend right=15] (X) to (tau6);
+                \draw [style=arrow, draw=red, line width=1.5] (tau6) to (Y);
+                \draw [style=arrow, draw=ForestGreen, bend left=20] (Y) to (tau7);
+                \draw [style=arrow, draw=ForestGreen] (Y) to (tau7);
+                \draw [style=arrow, draw=ForestGreen, bend right=20] (Y) to (tau7);
+                \draw [style=arrow, draw=ForestGreen] (tau7) to (Z);
+                \draw [style=arrow, draw=ForestGreen, bend left=50] (tau7.south) to (Y.south);
+                \draw [style=arrow, draw=ForestGreen] (Z) to (tau8);
+                \draw [style=arrow, draw=ForestGreen, bend left=30] (tau8) to (X);
+                \draw [style=arrow, draw=ForestGreen, bend right=30] (tau8) to (X);
+                \draw [style=arrow, draw=ForestGreen, bend right=30] (tau8) to (Y);
+
+                \draw [style=sitemap, opacity=0.5,  bend right=30] (A) to (X);
+                \draw [style=sitemap, opacity=0.5,  bend right=30] (B) to (X);
+                \draw [style=sitemap, opacity=0.5,  bend right=30] (AA) to (Y);
+                \draw [style=sitemap, opacity=0.5,  bend right=30] (AB) to (Y);
+                \draw [style=sitemap, opacity=0.5,  bend right=30] (C) to (Y);
+                \draw [style=sitemap, opacity=0.5,  bend right=30] (AAAB) to (Z);
+                \draw [style=transitionmap, opacity=0.5,  bend right=30] (tau1) to (tau6);
+                \draw [style=transitionmap, opacity=0.5,  bend right=30] (tau2) to (tau6);
+                \draw [style=transitionmap, opacity=0.5,  bend right=30] (tau3) to (tau7);
+                \draw [style=transitionmap, opacity=0.5,  bend right=30] (tau4) to (tau8);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
 This too will always be the case: the image of a rooted subspace will always be rooted in the image.
@@
 
-To conclude this section, we present the assembly index of every site of in our ligation model $\A$ together with a minimal, rooted assembly subspace containing that site.
-
-\TODO{Complete Figure}
-
-In the next section, we will consider methods for bounding the assembly index of a site.
-
-\subsection{Computability of and Bounds on the Assembly Index}\label{subsec:assembly-index-bounds}
-
-The first task, when presented with an assembly space, is to determine the assembly index of the sites in the space.
+The assembly index, as we have defined it, is dependent on the choice of generating set.
+To make this point clear, we will first consider the example assembly space $\A$ and present the assembly index and a representative minimal assembly subspace for each site.
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [scale=3] (P) at (1, 9) {$\A$};
+                \node [style=site, fill=blue!20] (A) at (0, 7.4) {$A$};
+                \node [style=site, fill=blue!20] (B) at (0, 5.8) {$B$};
+                \node [style=site, fill=blue!20] (C) at (6, 5) {$C$};
+                \node [style=site] (AA) at (4, 7.4) {$AA$};
+                \node [style=site] (AB) at (4, 5.8) {$AB$};
+                \node [style=site] (AAAB) at (8, 6.6) {$AAAB$};
+                \node [style=transition] (alpha) at (2, 7.4) {$\alpha$};
+                \node [style=transition] (beta) at (2, 5.8) {$\beta$};
+                \node [style=transition] (gamma) at (6, 6.6) {$\gamma$};
+                \node [style=transition] (delta) at (10, 6.6) {$\delta$};
+
+                \node [style=site, fill=blue!20] (A0) at (0, 0) {$A$};
+                \node [scale=2] at (0, -2) {$c_\A(A) = 0$};
+
+                \node [style=site, fill=blue!20] (B1) at (4, 0) {$B$};
+                \node [scale=2] at (4, -2) {$c_\A(B) = 0$};
+
+                \node [style=site, fill=blue!20] (C2) at (8, 0) {$C$};
+                \node [scale=2] at (8, -2) {$c_\A(C) = 0$};
+
+                \node [style=site, fill=blue!20] (A3) at (12, 0) {$A$};
+                \node [style=transition] (alpha3) at (12, 2) {$\alpha$};
+                \node [style=site] (AA3) at (12, 4) {$AA$};
+                \node [scale=2] at (12, -2) {$c_\A(AA) = 1$};
+
+                \node [style=site, fill=blue!20] (A4) at (16, 0) {$A$};
+                \node [style=site, fill=blue!20] (B4) at (17.6, 0) {$B$};
+                \node [style=transition] (beta4) at (16.8, 2) {$\beta$};
+                \node [style=site] (AB4) at (16.8, 4) {$AB$};
+                \node [scale=2] at (16.8, -2) {$c_\A(AB) = 1$};
+
+                \node [style=site, fill=blue!20] (A5) at (21.6, 0) {$A$};
+                \node [style=site, fill=blue!20] (B5) at (23.2, 0) {$B$};
+                \node [style=transition] (alpha5) at (21.6, 2) {$\alpha$};
+                \node [style=transition] (beta5) at (23.2, 2) {$\beta$};
+                \node [style=site] (AA5) at (21.6, 4) {$AA$};
+                \node [style=site] (AB5) at (23.2, 4) {$AB$};
+                \node [style=site, fill=blue!20] (C5) at (24, 6) {$C$};
+                \node [style=transition] (gamma5) at (22.4, 6) {$\gamma$};
+                \node [style=site] (AAAB5) at (22.4, 8) {$AAAB$};
+                \node [scale=2] at (22.4, -2) {$c_\A(AAAB) = 3$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend right=15] (A) to (alpha);
+                \draw [style=arrow, bend left=15] (A) to (alpha);
+                \draw [style=arrow] (alpha) to (AA);
+                \draw [style=arrow, bend right=15] (A) to (beta);
+                \draw [style=arrow] (B) to (beta);
+                \draw [style=arrow] (beta) to (AB);
+                \draw [style=arrow] (AA) to (gamma);
+                \draw [style=arrow] (AB) to (gamma);
+                \draw [style=arrow, bend left=30] (C) to (gamma);
+                \draw [style=arrow, bend left=30] (gamma) to (C);
+                \draw [style=arrow] (gamma) to (AAAB);
+                \draw [style=arrow] (AAAB) to (delta);
+                \draw [style=arrow, bend right=30] (delta) to (A);
+                \draw [style=arrow, bend right=30] (delta) to (AA);
+                \draw [style=arrow, bend left=40] (delta) to (B);
+
+                \draw [style=arrow, bend left=15] (A3) to (alpha3);
+                \draw [style=arrow, bend right=15] (A3) to (alpha3);
+                \draw [style=arrow] (alpha3) to (AA3);
+
+                \draw [style=arrow] (A4) to (beta4);
+                \draw [style=arrow] (B4) to (beta4);
+                \draw [style=arrow] (beta4) to (AB4);
+
+                \draw [style=arrow, bend left=15] (A5) to (alpha5);
+                \draw [style=arrow, bend right=15] (A5) to (alpha5);
+                \draw [style=arrow] (alpha5) to (AA5);
+                \draw [style=arrow, bend right=15] (A5) to (beta5);
+                \draw [style=arrow] (B5) to (beta5);
+                \draw [style=arrow] (beta5) to (AB5);
+                \draw [style=arrow] (AA5) to (gamma5);
+                \draw [style=arrow] (AB5) to (gamma5);
+                \draw [style=arrow, bend left=30] (C5) to (gamma5);
+                \draw [style=arrow, bend left=30] (gamma5) to (C5);
+                \draw [style=arrow] (gamma5) to (AAAB5);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+However, if we were to have chosen a different generating set, say $\{C, AAAB\}$, while retaining the same underlying Petri net the results would have been quite different.
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [scale=3] (P) at (1, 10.2) {$\A'$};
+                \node [style=site, fill=blue!20] (AAAB) at (0, 7.8) {$AAAB$};
+                \node [style=transition] (delta) at (2, 7.8) {$\delta$};
+                \node [style=site] (A) at (4, 8.6) {$A$};
+                \node [style=site] (B) at (4, 7.0) {$B$};
+                \node [style=transition] (alpha) at (6, 8.6) {$\alpha$};
+                \node [style=transition] (beta) at (6, 7.0) {$\beta$};
+                \node [style=site] (AA) at (8, 8.6) {$AA$};
+                \node [style=site] (AB) at (8, 7.0) {$AB$};
+                \node [style=site, fill=blue!20] (C) at (10, 9.4) {$C$};
+                \node [style=transition] (gamma) at (10, 7.8) {$\gamma$};
+
+                \node [style=site, fill=blue!20] (AAAB0) at (0, 0) {$AAAB$};
+                \node [scale=2] at (0, -2) {$c_{\A'}(AAAB) = 0$};
+
+                \node [style=site, fill=blue!20] (C1) at (6, 0) {$C$};
+                \node [scale=2] at (6, -2) {$c_{\A'}(C) = 0$};
+
+                \node [style=site, fill=blue!20] (AAAB2) at (13.6, 0) {$AAAB$};
+                \node [style=transition] (delta2) at (13.6, 2) {$\delta$};
+                \node [style=site] (A2) at (12, 4) {$A$};
+                \node [style=site] (B2) at (13.6, 4) {$B$};
+                \node [style=site] (AA2) at (15.2, 4) {$AA$};
+                \node [scale=2] at (13.6, -2) {$c_{\A'}(A) = c_{\A'}(B) = c_{\A'}(AA) = 1$};
+
+                \node [style=site, fill=blue!20] (AAAB3) at (22, 0) {$AAAB$};
+                \node [style=transition] (delta3) at (22, 2) {$\delta$};
+                \node [style=site] (A3) at (21.2, 4) {$A$};
+                \node [style=site] (B3) at (22.8, 4) {$B$};
+                \node [style=site] (AA3) at (23.6, 2) {$AA$};
+                \node [style=transition] (beta3) at (22, 6) {$\beta$};
+                \node [style=site] (AB3) at (22, 8) {$AB$};
+                \node [scale=2] at (22, -2) {$c_{\A'}(AB) = 2$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow] (AAAB) to (delta);
+                \draw [style=arrow] (delta) to (A);
+                \draw [style=arrow, bend left=40] (delta.north) to (AA);
+                \draw [style=arrow] (delta) to (B);
+                \draw [style=arrow, bend right=15] (A) to (alpha);
+                \draw [style=arrow, bend left=15] (A) to (alpha);
+                \draw [style=arrow] (alpha) to (AA);
+                \draw [style=arrow, bend right=15] (A) to (beta);
+                \draw [style=arrow] (B) to (beta);
+                \draw [style=arrow] (beta) to (AB);
+                \draw [style=arrow] (AA) to (gamma);
+                \draw [style=arrow] (AB) to (gamma);
+                \draw [style=arrow, bend right=30] (C) to (gamma);
+                \draw [style=arrow, bend right=30] (gamma) to (C);
+                \draw [style=arrow, bend left=40] (gamma.south) to (AAAB);
+
+                \draw [style=arrow] (AAAB2) to (delta2);
+                \draw [style=arrow] (delta2) to (AA2);
+                \draw [style=arrow] (delta2) to (A2);
+                \draw [style=arrow] (delta2) to (B2);
+
+                \draw [style=arrow] (AAAB3) to (delta3);
+                \draw [style=arrow] (delta3) to (A3);
+                \draw [style=arrow] (delta3) to (B3);
+                \draw [style=arrow] (delta3) to (AA3);
+                \draw [style=arrow] (A3) to (beta3);
+                \draw [style=arrow] (B3) to (beta3);
+                \draw [style=arrow] (beta3) to (AB3);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+While this may seem, at first glance, to be undesirable it captures a very important point about the assembly process: the materials that you start with greatly influence how difficult, complex or costly assembling a given object may be.
+The cases of interest in this work presume that we being with only ``simple" objects from which we aim to build more ``complex" objects.
+However, the formalism, in and of itself, it far more general than this.
+
+We now turn our attention to the task of determining the assembly index of an object.
 In practical terms, this requires an algorithm for computing the assembly index relative to some space.
 In this work, we do not present a general algorithm to do so, though a simple depth-first search of the space may suffice in some cases.
-Rather, we first show that the assembly index is in fact computable.
+Rather, we first show that the assembly index is in fact computable, and subsequently establish methods of bounding the assembly index in cases where direct calculation is infeasible.
 \begin{theorem}\label{thm:computable}
@@
 
-\TODO{Example and Figure}
+The the remaining examples, we will depart from using $\A$ since large enough to demonstrate the desired points.
+Consider the assembly space and subspace depicted below:
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [style=site, fill=blue!20] (A) at (0, 0) {$A$};
+                \node [style=site] (B) at (4, 0) {$B$};
+                \node [style=site] (C) at (8, 0) {$C$};
+                \node [style=site] (D) at (12, 0) {$D$};
+                \node [style=site] (E) at (16, 0) {$E$};
+                \node [style=site] (F) at (20, 0) {$F$};
+                \node [style=transition] (a) at (2, 0) {$\alpha$};
+                \node [style=transition] (b) at (6, 0) {$\beta$};
+                \node [style=transition] (c) at (10, 0) {$\gamma$};
+                \node [style=transition] (d) at (14, 0) {$\delta$};
+                \node [style=transition] (e) at (18, 0) {$\epsilon$};
+                \node [style=transition] (f) at (8, 2) {$\zeta$};
+                \node [style=transition] (g) at (12, -4) {$\eta$};
+                \node [style=transition] (h) at (16, -3) {$\theta$};
+                \node [style=transition] (i) at (14, 3) {$\iota$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=arrow, bend left=25, draw=gray!70] (B) to (f);
+                \draw [style=arrow, bend left=10, draw=gray!70] (B) to (f);
+                \draw [style=arrow, bend left=25, draw=gray!70] (f) to (D);
+
+                \draw [style=arrow, bend right=10, draw=gray!80] (B) to (g);
+                \draw [style=arrow, bend right=10, draw=gray!80] (C) to (g);
+                \draw [style=arrow, bend right=10, draw=gray!80] (g) to (E);
+
+                \draw [style=arrow, bend right=10, draw=gray!90] (B) to (h);
+                \draw [style=arrow, bend right=10, draw=gray!90] (D) to (h);
+                \draw [style=arrow, bend right=10, draw=gray!90] (h) to (F);
+
+                \draw [style=arrow, bend left=25, draw=gray!80] (C) to (i);
+                \draw [style=arrow, bend left=10, draw=gray!80] (C) to (i);
+                \draw [style=arrow, bend left=25, draw=gray!80] (i) to (F);
+
+                \draw [style=arrow, draw=red, bend left=15] (A) to (a);
+                \draw [style=arrow, draw=red, bend right=15] (A) to (a);
+                \draw [style=arrow, draw=red, bend right=30] (A) to (b);
+                \draw [style=arrow, draw=red, bend right=30] (A) to (c);
+                \draw [style=arrow, draw=red, bend right=30] (A) to (d);
+                \draw [style=arrow, draw=red, bend right=30] (A) to (e);
+                \draw [style=arrow, draw=red] (a) to (B);
+                \draw [style=arrow, draw=red] (B) to (b);
+                \draw [style=arrow, draw=red] (b) to (C);
+                \draw [style=arrow, draw=red] (C) to (c);
+                \draw [style=arrow, draw=red] (c) to (D);
+                \draw [style=arrow, draw=red] (D) to (d);
+                \draw [style=arrow, draw=red] (d) to (E);
+                \draw [style=arrow, draw=red] (E) to (e);
+                \draw [style=arrow, draw=red] (e) to (F);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+The edges associated with an assembly subspace are highlighed in red.
+If we consider the site $F$ in the context of the space, as a whole, the assembly index is $c(F) = 3$.
+There are two minimal, rooted assembly subspaces with that size which contain either $\alpha$, $\zeta$ and $\eta$; or $\alpha$, $\beta$ and $\theta$; as transitions.
+However, if we've restricted ourselves only the the subspace, then $\zeta$, $\eta$ and $\theta$ are inadmissible.
+As such, the assembly index in the subspace is $5$.
 
@@
 
-\TODO{Example and Figure}
+For this final example, we will consider a binary string formation process wherein any two strings can be concatentated to form another, and we choose $\{0, 1\}$ as the generating set (in fact the only choice).
+This will be referred to as space $\mathcal{B}$.
+We will also consider a secondary space consisting of the natural numbers wherein any two integers can be added together to for another, and we choose $\{1\}$ as the generating set (again, the only choice).
+This space will be referred to as $\mathcal{N}$.
+There is a canonical map $f : \mathcal{B} \rightarrow \mathcal{N}$ such that $S(f)(x) = \textrm{length}(x)$, and the transition map follows naturally.
+In this example, we are particularly interested in the assembly index of $1100$ in $\mathcal{B}$.
+The site $1100$ maps under $f$ to $4$ in $\mathcal{N}$.
+Depicted below a restricted view of $\mathcal{B}$, $\mathcal{N}$ and $f$ wherein we only consider sites which might be used to produced $1100$.
+\begin{center}
+    \scalebox{0.6}{
+        \begin{tikzpicture}
+            \begin{pgfonlayer}{nodelayer}
+                \node [scale=3] at (15, 12) {$\mathcal{N}$};
+                \node [style=site, fill=blue!20] (A) at (13, 0) {$1$};
+                \node [style=site] (B) at (13, 4) {$2$};
+                \node [style=site] (C) at (13, 8) {$3$};
+                \node [style=site] (D) at (13, 12) {$4$};
+                \node [style=transition, scale=0.5] (a) at (13, 2) {};
+                \node [style=transition, scale=0.5] (b) at (13, 6) {};
+                \node [style=transition, scale=0.5] (c) at (13, 10) {};
+                \node [style=transition, scale=0.5] (d) at (11, 8) {};
+
+                \node [scale=3] at (-2, 14) {$\mathcal{B}$};
+                \node [style=site, fill=blue!20] (0) at (-2, 0) {$0$};
+                \node [style=site, fill=blue!20] (1) at ( 2, 0) {$1$};
+                \node [style=transition, scale=0.5] (a00) at (-3, 2) {};
+                \node [style=transition, scale=0.5] (a10) at ( 0, 2) {};
+                \node [style=transition, scale=0.5] (a11) at ( 3, 2) {};
+                \node [style=site] (00) at (-4, 4) {$00$};
+                \node [style=site] (10) at ( 0, 4) {$10$};
+                \node [style=site] (11) at ( 4, 4) {$11$};
+                \node [style=transition, scale=0.5] (a100a) at (-3, 6) {};
+                \node [style=transition, scale=0.5] (a100b) at (-1, 6) {};
+                \node [style=transition, scale=0.5] (a110a) at ( 1, 6) {};
+                \node [style=transition, scale=0.5] (a110b) at ( 3, 6) {};
+                \node [style=site] (100) at (-2, 8) {$100$};
+                \node [style=site] (110) at ( 2, 8) {$110$};
+                \node [style=transition, scale=0.5] (a1100a) at (-1, 10) {};
+                \node [style=transition, scale=0.5] (a1100b) at ( 1, 10) {};
+                \node [style=transition, scale=0.5] (a1100c) at ( 0, 14) {};
+                \node [style=site] (1100) at (0, 12) {$1100$};
+            \end{pgfonlayer}
+            \begin{pgfonlayer}{edgelayer}
+                \draw [style=sitemap, opacity=0.5, bend left=15] (0) to (A);
+                \draw [style=sitemap, opacity=0.5, bend left=15] (1) to (A);
+                \draw [style=sitemap, opacity=0.5, bend left=15] (00) to (B);
+                \draw [style=sitemap, opacity=0.5, bend left=15] (10) to (B);
+                \draw [style=sitemap, opacity=0.5, bend left=15] (11) to (B);
+                \draw [style=sitemap, opacity=0.5, bend left=15] (100) to (C);
+                \draw [style=sitemap, opacity=0.5, bend left=15] (110) to (C);
+                \draw [style=sitemap, opacity=0.5, bend left=15] (1100) to (D);
+                \draw [style=transitionmap, opacity=0.5, bend left=15] (a00) to (a);
+                \draw [style=transitionmap, opacity=0.5, bend left=15] (a10) to (a);
+                \draw [style=transitionmap, opacity=0.5, bend left=15] (a11) to (a);
+                \draw [style=transitionmap, opacity=0.5, bend left=15] (a100a) to (b);
+                \draw [style=transitionmap, opacity=0.5, bend left=15] (a100b) to (b);
+                \draw [style=transitionmap, opacity=0.5, bend left=15] (a110a) to (b);
+                \draw [style=transitionmap, opacity=0.5, bend left=15] (a110b) to (b);
+                \draw [style=transitionmap, opacity=0.5, bend left=15] (a1100a) to (c);
+                \draw [style=transitionmap, opacity=0.5, bend left=15] (a1100b) to (c);
+                \draw [style=transitionmap, opacity=0.5] (a1100c) to (d);
+
+                \draw [style=arrow, draw=ForestGreen, line width=1.5, bend left=15] (A) to (a);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5, bend right=15] (A) to (a);
+                \draw [style=arrow, draw=gray!80, bend right=30] (A) to (b);
+                \draw [style=arrow, draw=gray!80, bend right=30] (A) to (c);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5] (a) to (B);
+                \draw [style=arrow, draw=gray!80] (B) to (b);
+                \draw [style=arrow, draw=gray!80] (b) to (C);
+                \draw [style=arrow, draw=gray!80] (C) to (c);
+                \draw [style=arrow, draw=gray!80] (c) to (D);
+                \draw [style=arrow, bend left=25, draw=ForestGreen, line width=1.5] (B) to (d);
+                \draw [style=arrow, bend left=10, draw=ForestGreen, line width=1.5] (B) to (d);
+                \draw [style=arrow, bend left=25, draw=ForestGreen, line width=1.5] (d) to (D);
+
+                \draw [style=arrow, draw=ForestGreen, line width=1.5, bend left=15] (0) to (a00);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5, bend right=15] (0) to (a00);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5] (0) to (a10);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5, bend left=15] (1) to (a11);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5, bend right=15] (1) to (a11);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5] (1) to (a10);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5] (a00) to (00);
+                \draw [style=arrow, draw=gray!80] (a10) to (10);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5] (a11) to (11);
+                \draw [style=arrow, draw=gray!80] (00) to (a100a);
+                \draw [style=arrow, draw=gray!80] (10) to (a100b);
+                \draw [style=arrow, draw=gray!80] (10) to (a110a);
+                \draw [style=arrow, draw=gray!80] (11) to (a110b);
+                \draw [style=arrow, draw=gray!80, bend left=30] (1) to (a100a);
+                \draw [style=arrow, draw=gray!80, bend left=10] (0) to (a100b);
+                \draw [style=arrow, draw=gray!80, bend right=10] (1) to (a110a);
+                \draw [style=arrow, draw=gray!80, bend right=30] (0) to (a110b);
+                \draw [style=arrow, draw=gray!80] (a100a) to (100);
+                \draw [style=arrow, draw=gray!80] (a100b) to (100);
+                \draw [style=arrow, draw=gray!80] (a110a) to (110);
+                \draw [style=arrow, draw=gray!80] (a110b) to (110);
+                \draw [style=arrow, draw=gray!80] (100) to (a1100a);
+                \draw [style=arrow, draw=gray!80] (110) to (a1100b);
+                \draw [style=arrow, draw=gray!80, bend right=5] (1) to (a1100a);
+                \draw [style=arrow, draw=gray!80, bend left=5] (0) to (a1100b);
+                \draw [style=arrow, draw=gray!80] (a1100a) to (1100);
+                \draw [style=arrow, draw=gray!80] (a1100b) to (1100);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5, bend left=15] (00) to (a1100c);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5, bend right=15] (11) to (a1100c);
+                \draw [style=arrow, draw=ForestGreen, line width=1.5] (a1100c) to (1100);
+            \end{pgfonlayer}
+        \end{tikzpicture}
+    }
+\end{center}
+Minimal, rooted subspaces of minimum size are highlighed in green in both cases.
+It is easy to see that the assembly index of $1100$ is $c_{\mathcal{B}}(1100) = 3$ while the index of $4$ is $c_{\mathcal{N}}(4) = 2$, so of course $c_{\mathcal{N}}(4) \le c_{\mathcal{B}}(1100)$.
+The only reason these two indices are directly comparable is that $\mathcal{B}$ maps onto $\mathcal{N}$, and as such the entire space $\mathcal{N}$ is the image of $\mathcal{B}$.
+If this were not the case, special care would have to be taken to ensure that only transitions in $f(\mathcal{B})$ were considered.
 
 Our final bound is a special case of the lower bound derived from an assembly map; however, it represents an upper bound.
-Given an assembly space with no directed loops, which we refer to as \textbf{acyclic}, we can form an analogous assembly space which has a tree-like structure by duplicating sites that participate in more than one transition.
+Given an assembly space with no directed loops, which we refer to as \textbf{acyclic}, we can form an analogous assembly space which has a tree-like structure by duplicating sites that participate in more than one pathway.
 We refer to such a space as the \textit{split-branch} representation of the space.

### 2021-06-03 papers/gomen/alife2019/reviews/response-to-reviews.md
Track ALIFE 2019 abstract

---
title: "Inferring a Graph's Topology from Games Played on It" Response to Reviewers
date: 21 May 2019
---

# Reviewer 1 (Ay or Polani?)

The paper describes the use of mutual information between agents paying games in different network topologies to infer the structure of the network. The authors show how the degree of effectiveness of the method varies strongly with the game being played and to some degree with the graph density.

The objective to connect topology and functional connectivity is of great interest in complex systems study, and the authors are able two show a number of cases in which the task can be solved. Still, for each game and network there is always some regions in which the connection between mutual information and connectivity cannot allow to reconstruct the network. **Maybe one of the more important limitations of the paper is that the authors offer little insight about what is happening in those cases.**

## Major Suggestions

As the authors describe its system as a sort of parallel Glauber Dynamics in a maximum entropy distribution (equation 4), maybe the authors could complement their analysis by comparing what happens in games with better known models as the Ising model (which could be simulated using an appropriate matrix G in equation 1), and maybe compare the AUC values for different values of beta in comparison with the behavior of well known information theoretic parameters of the model (entropy, heat capacity, mutual information, or even transfer entropy as in https://doi.org/10.1103/PhysRevLett.111.177203 ). Also, the use of better known topologies (like a lattice topology) could be helpful in connecting the results with other well known phenomena, like critical phase transitions

>   I think all of this is reasonable, but the Ising model is maybe a bit outside the scope of this. I'm sure we could concoct a payoff matrix that reproduces the Ising model, but I doubt it would live inside the T-S parameterization. I think most of these ideas would be great for the full journal article we are preparing. I've added the following:
>
>   >   **Page 5-6 (Conclusion)**:
>   >
>   >   The dynamics of the models we considered here are similar in many respects to the classic Ising model, with $\beta$ acting much like temperature and the payoff matrix \cref{eq:game} behaving similarly to interaction strengths. It's reasonable to expect that analogues of heat capacity, entropy, etc$\ldots$ could be related in some way to the effectiveness of the network inference. Comparing the AUC with some of these thermodynamic analogues is a tantalizing possibility for a future work.
>
>   As for lattice topologies, $50$ nodes doesn't factor well — either $5 \times 10$ or $2 \times 25$. I went ahead and simulated the dynamics on a $5 \times 10$ lattice and included it in the paper.

In the discussion, the authors claim that there is few reason to expect the TE to behave differently than mutual information because the current strategy is not used for updating to the new strategy. I do not think that this must be the case (since the current strategy could affect future strategies indirectly from correlations in the network), and maybe the authors should test transfer entropy in some cases to test this (or be more careful about the claim)

>   I'm going to ease up the **one** sentence in which I mention transfer entropy. I knew when I wrote it people would complain, but I'm almost certain it won't do much for us.
>
>   
>
>   >   **Page 5 (Conclusion):**
>   >
>   >   Transfer entropy is really a special case of CMI; it would condition on the target agent's previous strategies. Both approaches are worth exploring more rigorously.

Finally, the authors may be interested in testing or citing other information theoretic approaches that are more focused to capture causal interactions in the network, like causal information flows https://doi.org/10.1142/S0219525908001465 or interventional versions of information theory in general (ISBN: 9780521895606)

>   I'll add a few sentences about interventional methods to the discussion section as possible future directions.
>
>   >   **Page 5 (Conclusion):**
>   >
>   >   In this work, we were interested in methods that required only observation of the system. However, it is well understood that observation alone, particularly in the case of large systems wherein only a small portion of the state space can be explored, are inadequate for extracting causal relationships between components of a system. Interventional methods, such as \citep{Ay2008-jc}, are much more effective in such cases, provided you have the ability to control aspects of the system. Subsequent work may explore such an approach.

## Minor Suggestions

Other small corrections needed:
- The labels of the axes of the figures (specially Figure 1) are hard to read and should use a larger font.

    >   Bumped up the font sizes and emboldened in Fig. 1.

- Figures 2-4 are hard to read in black and white, the authors should choose a colormap that can be read also when printed in black and white.

    >   Pick a better color scheme. It now prints well and is color-blind friendly.

- Variable T is used twice for different purposes (eq 1 and eq 7), one should be changed to avoid confusion.

  >   How can this possibly confuse people? I hate everyone. I changed the $T$ in eq. 7 to $R$ (for real) and then $N$ in eq. 7 to $F$ (fake). I also explain the notation in the subsequent paragraph.

- When introducing the S-T plot, maybe for clarity the authors could refer to eq 1.

  >   We now refer to eq. 1.

# Reviewer 2 (Lizier)

The authors provide an interesting investigation of "effective network" inference of graph structure from time series of strategies of agents playing games on this structure. They use pairwise lagged mutual information for the inference, and experiment with game parameters across the space of prisoner's dilemma, hawk-dove, stag-hunt and harmony games. They seek to reveal where in the parameter space the inference is successful or otherwise in revealing the structure, showing interesting differences across this space, and large influence of average degree regardless of structure class.

Network inference is certainly a topical issue across many areas, particularly neuroscience as highlighted by the authors, and the paper is made well in scope for ALife by combining this with dynamics of networked game theory. The paper is on the short side, yet it is quite a solid piece with good experimental work presented, and is well written, so should clearly be accepted.

## Minor Suggestions

I have a number of suggestions that could be incorporated in a camera-ready version. I'll list the more interesting / longer points first, but all are fairly straightforward. (I'm also going to apologize that it's me reviewing your papers, *again*, and that I'm referring to some of my own papers below - that's mainly to provide further info, not to insist on additional citations!)

Most importantly, I'd suggest changing the nomenclature of the network inference here from "effective" to "functional", as neuroscientists get very picky about having these terms used correctly. The distinction is subtle: functional networks capture statistical relationships between the source and target, whereas effective networks additionally provide a more holistic model which explains and in some sense could reproduce the dynamics. Functional relationships are often undirected (e.g. correlation or MI) but not always. Earlier pieces I wrote, e.g. the review in sec 7.2 of our "Information flow in complex systems" book, equated functional with undirected, but that's not an accurate reflection of community consensus. Effective network inference is not only about having directionality, but importantly about making a minimal model that can explain and replicate the dynamics. Pairwise measures don't do that. This is why the consensus now is that pairwise transfer entropy should be seen as functional, not effective (despite some earlier work labeling it as such, e.g. our book, and the Vicente and Ito references you have). More holistic effective approaches (holistic as in taking into account the parent nodes as a whole set, like a multivariate transfer entropy as per the Rubinov 2011 or Sun 2015 articles, or a model based approach like DCM) provide a unified model of how the target updates its dynamics based on the set of parent sources. So lagged MI here is functional (even though the lag gives it some direction), not effective because it's looking at the sources individually (like TE) rather than as a set. With pairwise TE you might still be able to slip through calling it effective because that distinction is still argued from some quarters, but that definitely won't fly for MI, even lagged. I hope that makes sense.

>   Changed "effective" to "functional".

Bottom of p. 2 defining graph types -- the parameters for each graph type aren't defined here (e.g. m and p); those definitions should be added for completeness. Also, while I can guess at the cycle and wheel structures, the names alone leave some ambiguity, e.g.: I assume the nodes in the cycle are connected to the two nearest neighbors only? The wheel is a hub and spoke model, plus nearest neighbors? That should all be much more clear than it is.

>   Describe the topologies in more detail.
>
>   >   **Page 2-3 (Results):**
>   >
>   >   We were interested in the relationship between the form of the game $\mathcal{G}$, the topology of the graph $G$, and the rule parameter $\beta$. To explore this, we considered $50$ agents playing on graphs with one of 5 types of topology: a.) Barabási-Albert graphs, b.) Erdős-Rényi graphs, and the c.) cycle, d.) wheel and e.) lattice topologies. The Barabási-Albert model (Barabási and Albert, 1999)  generates random graphs using preferential attachment; as new nodes are iteratively added to the graph they are randomly connected to $m$ existent nodes with a bias toward those with higher degree; we considered only $m\in\{1,5\}$ in this work. The Erdős-Rényi model (Erdős and Rényi, 1959) starts with the full set of nodes and adds an edge between each pair of distinct nodes with probability $p$. We chose $p\in\{0.04,0.18\}$ to ensure that the edge density of the Barabási-Albert and Erdős-Rényi graphs are comparable. The cycle, wheel and $5 \times 10$ non-periodic lattice topologies, on the other hand, are non-random topologies, and are depicted in \ref{fig:topologies}.
>
>   And I added a figure depicting the topologies. (**Page 3**).

p. 4 "This suggests that the differences in the Barabási-Albert and Erdős-Rényi graphs may only be an edge density effect" - this looks to be a good observation. Perhaps that we only have 50 nodes means the degree distribution of BA can't look dissimilar enough to ER to make a difference to the dynamics here? It may even be worth plotting the degree distributions to check; in any case, it may be useful to speculate on whether they could be more different in larger networks.

>   The graphs are pretty topologically distinct. Still I modified that paragraph to reflect the new ER simulations and commented on this.
>
>   >   **Page 4-5 (Discussion):**
>   >
>   >   This brings us to the final factor involved in determining the efficacy of the classification: the edge density of the graph. When we compare, for example, the Barabási-Albert graphs with $m=1$ (fig. 3(a-b)) to the Erdős-Rényi graphs with $p=0.04$ (fig. 4(a-b)), we see almost identical structure in the $\overline{AUC}$ heatmaps. On average the Erdős-Rényi graphs have the same edge density to their Barabási-Albert counterparts, i.e. they have about the same number of edges. The cycle graph (fig. 5(a-b)) has the same edge density to the Barabási-Albert graph (\mbox{$m=1$}), and again we see almost identical heatmaps. By increasing the edge parameters for the Barabási-Albert and Erdős-Rényi graphs, $m$ and $p$ respectively, we can see a similar comparison for yet denser graphs (fig. 3(c-d) and  fig. 4(c-d)). Again, the Barabási-Albert ($m=5$) and Erdős-Rényi ($p=0.18$) graphs have similar edge density. What's more, the same qualitative change is seen for a single type of topology when the edge density changes. For example, comparing fig. 3(a) to 3(c) or fig. 4(a) to 4(c), we see fewer harmony and prisoner's dilemma games admit a faithful inference. The same phenomenon is observed in comparing cycles, lattices and wheels, (fig. 5), which further supports the claim. The graphs have remarkably distinct topologies even with only $50$-nodes. For example, it is difficult to find any similarity between the Barabási-Albert and cycle graphs other than edge density. However, it is entirely plausible that some other topological similarity between the graphs is causing these effects. Increasing the size of the graph should lead to increasingly divergent topological features. That would allow us to test this claim more fully.

p. 5 "Since our agents don’t use their current strategy to determine their next, there are few reasons to expect TE to be more effective." I don't think that's true here. The next strategy of each agent is computed as a stochastic update/change (or lack thereof) to their current strategy, so the current strategy seems to be a large, if not the largest, factor in computing their next strategy. It also influences their neighbor's strategies, which in turn influence it, so has an indirect effect there also. As such, TE may better elucidate the effect of source agents on those dynamic updates, given that it looks at those effects in the context of the past strategy and allows you to directly see how the source influenced that state update (rather than only looking to the relationship of what comes next). I'm not suggesting that you add TE for this paper, the MI investigation here is enough and is giving interesting insights; just that the assessment/conclusion of TE not helping I think is off-target.

>   >   **Page 5 (Conclusion):**
>   >
>   >   Transfer entropy is really a special case of CMI; it would condition on the target agent's previous strategies. Both approaches are worth exploring more rigorously.

p. 5 "Since our graphs have 50 nodes, that computation was infeasible. Alternative methods of computing CMI may make it viable for future work" This feasibility issue with large multivariate calculations is really important, and was one of the drivers for the iterative CMI/TE approaches (greedily building up a parent set) proposed in Rubinov 2011 and Sun 2015, which you already reference, plus others referred to in sec 7.2 of our book above. As such, it would be useful to specifically refer to those approaches as having been proposed to handle that problem.

>   Mention the iterative CMI methods from Rubinov and Sun.
>
>   >   **Page 5 (Conclusion)**:
>   >
>   >   Alternative methods of computing CMI, such as the iterative approaches of (Lizier and Rubinov, 2012; Sun et al., 2015), may make it viable for future work.

## Minor Suggestions

I presume (2), (3) are only meant to sum over edges this node i is a part of? The maths makes it look like all edges; it would be better if the sum was over nodes j, such that (i,j) \in E.

>   Clarify this notation, apparently it's not as clear as I thought.
>
>   >   **Page 2 (Methods):** 
>   >
>   >   The game is played in rounds starting with each agent's strategy selected uniformly at random. In each round, the agents play with their neighbors $N_i = \{j~|~(i,j) \in E\}$ and accumulate payoff
>   >   $$
>   >       P_i(s_1, \ldots, s_n) = \sum_{j \in N_i} \mathcal{G}_{{s_i}{s_j}}
>   >   $$

p.1 "when agents’ perception of the which game their playing is allowed to change" -> "when agents’ perception of which game they're playing is allowed to change" (note: 2 word changes there)

>   Typo...

p.2 - "We consider predictors with AUC < 0.5 as high-quality, although the classification criterion must be switched to φ_ij ≤ θ " - this is unclear. From later text I gather you mean they could be considered high quality if you invert the decision they provide, but that should be made more clear here.

>   I knew this was a bit unclear. Clarified?
>
>   >   **Page 2 (Methods):**
>   >
>   >   A predictor which is no better than uniformly random will yield a perfect diagonal with $AUC=0.5$. Better predictors will yield curves which deviate from the diagonal with $|AUC - 0.5| \gg 0$. We consider predictors with $AUC \ll 0.5$ to be of high-quality because the ROC curve reflects over the diagonal if we change the classification criterion from $\phi_{i,j} \geq \theta$ to $\phi_{ij} \leq \theta$. In other words, the predictor was good, but we were using the wrong criterion. It is important to note that this analysis does not tell us what the threshold $\theta$ should be, though in principle it can be determined. For now, it is sufficient to know only that such a threshold exists.

References:
- Capitalization is strange on many references, e.g. Bach

    >   I don't see anything wrong with the capitalization.

- Rubinov author names are garbled :)

    >   Fixed! (This is actually Lizier and Rubinov!!!)

# Additional Changes

I decided to using $p=0.04$ and $p=0.18$ for the edge probabilities for Erdős-Rényi graphs to make comparisons between them and the Barabási-Albert graphs more direct. This way they have the same edge densities on average, and the result is that heat maps are almost identical!

### 2021-06-03 papers/gomen/alife2019/main.tex
Track ALIFE 2019 abstract

\documentclass[letterpaper]{article}

\usepackage{natbib,alifeconf}
\usepackage{amsmath,amssymb}
\usepackage{blindtext}
\usepackage{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage[font=small]{caption}
\usepackage{xcolor}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{xfrac}

\newcommand{\BA}{Barab\'{a}si-Albert~}
\newcommand{\BAbox}{\mbox{\BA}}
\newcommand{\ER}{Erd\H{o}s-R\'{e}nyi~}
\newcommand{\ERbox}{\mbox{\ER}}

\setlength{\textfloatsep}{0pt plus 0.0pt minus 2.0pt}
\makeatletter
\g@addto@macro\normalsize{%
  \setlength\abovedisplayskip{5pt}
  \setlength\belowdisplayskip{5pt}
  \setlength\abovedisplayshortskip{5pt}
  \setlength\belowdisplayshortskip{5pt}
}
\makeatother

\title{Inferring a Graph's Topology from Games Played on It}
\author{Douglas G. Moore and Sara I. Walker\\ \mbox{} \\
BEYOND Center, Arizona State University, Tempe, AZ 85281\\
douglas.g.moore@asu.edu\\
sara.i.walker@asu.edu}

\begin{document}
\maketitle

\begin{abstract}
We consider an iterated model of agents playing a two-player game on a graph. The agents change their strategies as the game progresses based on anticipated payoffs. Using only the time series of the agents' strategies, we determine the pair-wise mutual information between all agents in the graph, and use these values as a predictors of the graph's topology. From this, we assess the influence of various model parameters on the effectiveness of mutual information at recovering the actual causal structure. It is found that the degree to which the functional connectivity reflects the actual causal structure of the graph strongly depends on which game is being played and how the agents are changing their strategies. Further, there is evidence that the edge density of the graph may also have some impact on the accuracy of the inferred network. This approach allows us to better connect the dynamics of the systems under study with the difference in their functional and actual connectivity, and has broad implications for the interpretation and application of information-based network inference. The methods and analyses described can be generalized and applied to other types of network models.
\end{abstract}

\section{Introduction}\label{sec:intro}

There is a wealth of literature on using information-theoretic tools to infer the network topology of collections of interacting random variables, particularly in neuroscience \citep{Ito2011-yi, Vicente2011-mj,Lizier2012-nf,Ver_Steeg2012-sl,Banerji2013-wd,Sun2014-ib,Sun2015-xs}. In many of these works, the phrase ``functional connectivity'' is used to underscore the fact that the actual causal interactions are not always readily inferred from the dynamics of the variables. This is often considered yet another example of the inequivalence of correlation and causation. While it appears that functional connectivity is a useful construct in neuroscience, that may not be the case is other fields. However, it is interesting to explore the conditions under which the actual and functional connectivity may coincide.

We consider a somewhat unorthodox model system to explore whether and when information-theoretic tools recapitulate the actual topology of a causal graph. Agents are situated on the vertices of a graph, and allowed to repeatedly play a two-player, two-strategy, symmetric game. In each round of the game, the agents may change their strategies based on their anticipated payoff. Treating the strategies of the agents as random variables in time, when can we confidently infer the actual connectivity of the graph? This model system was inspired by conversations with colleagues who explored the dynamics of games when agents' perception of which game they're playing is allowed to change \citep{Antonioni2018-cc}. Such a system is intrinsically interesting to consider, but it has value beyond that; namely in potential applications. Biologist have modeled interacting cells \citep{Hummert2014-gz}, organisms \citep{Smith_John_Maynard1979-hr, Smith1982-le, S_E_Riechert2003-bg, Nowak2004-rq} and even cancer \citep{Bach2001-vs,Gatenby2003-ha,Basanta2008-ta,Dingli2009-bd} as game-playing agents, and game theory has of course found innumerable applications in economics. In both cases, the strategies of the agents may be readily apparent, while the network itself is obscured. The ability to infer functional or actual connectivity based solely on the strategies could lead to more impactful methods of intervening on these systems.

From a technical perspective, this model offers a number of useful features: the graph's topology can be varied, the rules the agents use to update their strategies can be changed, and the space of graphs is nicely parameterized by two bounded variables. Altogether, this provides a number of ways to tweak the system and observe changes in the efficacy of network inference. Further, because this model is a particular type of Boolean network, it seems reasonable that the results and methods herein could be extrapolated and applied to more generic settings.

In this work, we describe the basic formalism, and present early results from simulations\footnote{All code used for these simulations is publicly available at \url{https://github.com/dglmoore/gomen}.}. We observe that the efficacy of the network reconstruction is dependent on the game the agents are playing, the rule they are using to update their strategies, and possibly the density of edges in the graph. We conclude with a number of possible future directions.

\section{Methods}
\label{sec:methods}

Consider a finite collection of agents $\{A_1, \ldots, A_n\}$. Each agent $A_i$ is situated at a vertex $v_i$ of some \textit{simple}\footnote{\textit{Simple} here means an undirected graph with no self-loops and at most one edge between any two given vertices.} graph $G=(V,E)$ with vertices $V=\{1,\dots,n\}$ and edges ${E \subset V \times V}$. The agents then play some, two-player, two-strategy, symmetric game with each of their neighbors. We restrict the games to those characterized by a payoff matrix of the form
\begin{equation}
    \label{eq:game}
    \mathcal{G} = \begin{array}{c|cc}
      & 0 & 1 \\\hline
    0 & 1 & S \\
    1 & T & 0
    \end{array}
\end{equation}
with $-1 \leq S \leq 1$ and $0 \leq T \leq 2$. The elements of this matrix $\mathcal{G}_{ab}$ specify the payoff received by the agent should they play strategy $a$ against an opponent playing strategy $b$. It is assumed throughout that all players are knowingly playing the same game, and that the game does not change. The strategy played by $A_i$ is denoted $s_i$ and can be either $0$ or $1$, sometimes referred to as \textit{cooperate} or \textit{defect}, respectively. The collection of strategies played by all of the agents is denoted $\bm{s} = (s_1,\ldots,s_n)$.

The game is played in rounds starting with each agent's strategy selected uniformly at random. In each round, the agents play with their neighbors $N_i = \{j~|~(i,j) \in E\}$ and accumulate payoff
\begin{equation}
    P_i(s_1, \ldots, s_n) = \sum_{j \in N_i} \mathcal{G}_{{s_i}{s_j}}
\end{equation}
We write this as $P_i(\bm{s})$ for compactness. Since the agents know which game they are playing, they may also consider the \textit{counterfactual} payoff they would have received had they played their alternative strategy $\hat{s}_i$:
\begin{equation}
    \bar{P}_i(\bm{s}) = P_i(s_1, \ldots, \hat{s}_i, \ldots, s_n) = \sum_{j \in N_i} \mathcal{G}_{{\hat{s}_i}{s_j}}.
\end{equation}
Based on the difference between counterfactual payoffs ${\Delta P_i(\bm{s})=\bar{P}_i(\bm{s})-P_i(\bm{s})}$, each agent may stochastically change its strategy for the next round with probability
\begin{equation}
    \label{eq:sigmoid}
    q_i(\beta; \bm{s}) = \frac{1}{1 + \exp{\left(-\beta \Delta P_i(\bm{s})\right)}},\quad \beta > 0.
\end{equation}
In words, agent $A_i$ will use strategy $\hat{s}_i$ in the next round with probability $q_i(\beta; \bm{s})$. All agents then synchronously update their strategies, and a new round is ready to begin. This process is iterated $t$ times, and a time series of strategies is generated $\{\bm{s}_0, \bm{s}_1, \ldots, \bm{s}_t\}$.

The outstanding question is to what degree this time series can be used to infer the topology of the underlying graph. A number of information-theoretic tools have been proposed for assessing connectivity in similar situations. The most popular, particularly among neuroscientists, is transfer entropy or some variation thereof \citep{Ito2011-yi, Vicente2011-mj, Orlandi2014-bh}. However, in this initial work we decided to consider a simpler measure. We start with
\begin{equation}
    I(s_i^+,s_j) = \sum_{s_i^+,s_j}p(s_i^+,s_j)\log{\frac{p(s_i^+,s_j)}{p(s_i^+)p(s_j)}},
\end{equation}
the mutual information between agent $A_i$'s next strategy $s_i^+$ and agent $A_j$'s current strategy $s_j$. Since we know that edges of the graph are undirected, we construct a measure that is symmetric in the agents:
\begin{equation}
    \phi_{ij} = \frac{1}{2}(I(s_i^+, s_j) + I(s_j^+,s_i)).
\end{equation}
This value is computed for every pair of distinct agents, $i \ne j$ for $i,j \in V$, and used as a predictor for the existence of an edge in the graph. If $\phi_{ij} \geq \theta$ for some threshold $0 \leq \theta \leq 1$, we predict that the edge $(i,j)$ exists, and that it otherwise does not. In a binary classification process such as this, one method of characterizing the effectiveness of the classification is in terms of the true-positive rate (TPR) and false-positive rate (FPR)
\begin{equation}
    TPR = \frac{TP}{R} \qquad and \qquad FPR = \frac{FP}{F}.
\end{equation}
Here the $TPR$ is the ratio of the number of edges \textit{correctly} predicted to exist ($TP$) and the actual number of existent edges ($R$), while the $FPR$ is the ratio of the number of edges \textit{incorrectly} predicted to exist ($FP$) and the number of possible edges which \textit{do not} exist ($F$). The value of the threshold can be varied continuously over its range $\theta \in [0,1]$, yielding a receiver operating characteristic (ROC) curve in the \mbox{$TPR$-$FPR$} space (\cref{fig:rocs}). The area under the curve (AUC) acts as a summary statistic for the quality of the classification. A predictor which is no better than uniformly random will yield a perfect diagonal with $AUC=0.5$. Better predictors will yield curves which deviate from the diagonal with $|AUC - 0.5| \gg 0$. We consider predictors with $AUC \ll 0.5$ to be of high-quality because the ROC curve reflects over the diagonal if we change the classification criterion from $\phi_{i,j} \geq \theta$ to $\phi_{ij} \leq \theta$. In other words, the predictor was good, but we were using the wrong criterion. It is important to note that this analysis does not tell us what the threshold $\theta$ should be, though in principle it can be determined. For now, it is sufficient to know only that such a threshold exists.

\section{Results}\label{sec:results}

\begin{figure}[!h]
    \begin{tabular}{ccc}
        \multicolumn{2}{c}{\BAbox} & \\
        {\footnotesize (a)\quad$m=1$} & {\footnotesize (b)\quad$m=5$} & {\footnotesize (c)\quad Cycle} \\
        \includegraphics[width=0.14\textwidth]{"topologies/ba1"} &
        \includegraphics[width=0.14\textwidth]{"topologies/ba5"} &
        \includegraphics[width=0.14\textwidth]{"topologies/cycle"} \\
        \multicolumn{2}{c}{\ERbox} & \\
        {\footnotesize (d)\quad$p=0.04$} & {\footnotesize (e)\quad$p=0.18$}& {\footnotesize (f)\quad Wheel} \\
        \includegraphics[width=0.14\textwidth]{"topologies/er0.04"} &
        \includegraphics[width=0.14\textwidth]{"topologies/er0.18"} &
        \includegraphics[width=0.14\textwidth]{"topologies/wheel"} \\
        \multicolumn{3}{c}{\footnotesize (g)\quad Lattice} \\
        \multicolumn{3}{c}{\includegraphics[width=0.14\textwidth]{"topologies/lattice"}} \\
    \end{tabular}
    \caption{\label{fig:topologies}
    Samples of the topologies considered. The \BA (a-b) and \ER graphs (d-e) are generated non-deterministically according to edge density parameters $m$ and $p$ respectively. The cycle (c), wheel (f) and $5 \times 10$ lattice (g) topologies have only one representative each. \\}
\end{figure}

We were interested in the relationship between the form of the game $\mathcal{G}$, the topology of the graph $G$, and the rule parameter $\beta$. To explore this, we considered $50$ agents playing on graphs with one of 5 types of topology: \mbox{a.) \BAbox} graphs, \mbox{b.) \ERbox} graphs, and the \mbox{c.) cycle}, \mbox{d.) wheel} and \mbox{e.) lattice} topologies. The \BAbox model \citep{Barabasi1999-lx} generates random graphs using preferential attachment; as new nodes are iteratively added to the graph they are randomly connected to $m$ existent nodes with a bias toward those with higher degree; we considered only $m\in\{1,5\}$ in this work. The \ERbox model \citep{Erdos1959-bd} starts with the full set of nodes and adds an edge between each pair of distinct nodes with probability $p$. We chose $p\in\{0.04,0.18\}$ to ensure that the edge density of the \BAbox and \ERbox graphs are comparable. The cycle, wheel and $5 \times 10$ non-periodic lattice topologies, on the other hand, are non-random topologies, and are depicted in \ref{fig:topologies}.

Once the graphs were constructed, we considered all games of the form \cref{eq:game} with $S \in \{-1.0, -0.9, \ldots, 1.0\}$ and $T \in \{0.0, 0.1, \ldots, 2.0\}$. We then generated $100$ graphs according to each of the parameters above for each combination of game and topology. For the cycle, wheel and lattice topologies, there is only one graph (up to isomorphism) for a given number of vertices, so we reran the simulations on the same topology $100$ times. We simulated $10$ rounds of play starting from $100$ initial conditions selected uniformly at random. The initial conditions were generated independently for each simulation, i.e. each combination of game, graph and rule parameter. The time series of strategies in each simulation of $10$ rounds with $100$ replicates was used to generate an ROC curve. The $100$ ROC curves for each game and topology combination (one for each randomly generated graph) were point-wise averaged to yield a mean ROC curve. Finally, the AUC was computed for each mean curve, and a scaled deviation of that value from the worst-case value of $0.5$:
\begin{equation}
    \label{eq:aucbar}
    \overline{AUC} = 2|AUC - 0.5|
\end{equation}
was plotted as a heatmap on an $S$-$T$ plot (\cref{fig:ba}, \cref{fig:er} and \cref{fig:fixed}). Here $S$ and $T$ refer to the parameters which specify a game as in \cref{eq:game}. In other words, each point in the plot corresponds to a different game with the color roughly characterizing the effectiveness of $\phi_{ij}$ as a predictor for the existence of the edge $(i,j)$ in the graph.

\begin{figure}[!t]
    \begin{tabular}{cc}
        {\footnotesize (a) Harmony} & {\footnotesize (b) Hawk-Dove} \\
        \includegraphics[width=0.21\textwidth]{"ROC/h"} &
        \includegraphics[width=0.21\textwidth]{"ROC/hd"} \\
        {\footnotesize (c) Stag-Hunt} & {\footnotesize (d) Prisoner's Dilemma} \\
        \includegraphics[width=0.21\textwidth]{"ROC/sh"} &
        \includegraphics[width=0.21\textwidth]{"ROC/pd"}
    \end{tabular}
    \caption{\label{fig:rocs}
    Receiver operating characteristic curves for four canonical games with $(T,S)$ parameterizations of (a) $(\sfrac{1}{2},\sfrac{1}{2})$, (b) $(\sfrac{3}{2},\sfrac{1}{2})$, (c) $(\sfrac{1}{2},\sfrac{-1}{2})$ and (d) $(\sfrac{3}{2},\sfrac{-1}{2})$ as played by $50$ agents on \BAbox graphs with $m=5$. In all cases, the agents employ a threshold function with rule parameter $\beta=1.0$. Each plot summarizes the results of simulations run on $100$ randomly generated graphs. The black curve is the point-wise mean of the $100$ resulting ROC curves, while the blue and orange curves are those with the greatest and least AUC, respectively. The dashed gray line represents the curve for a predictor which is no better than chance.\\}
\end{figure}

\section{Discussion}\label{sec:discussion}

\begin{figure}[!t]
    \begin{tabular}{cc}
        {\footnotesize (a) $m=1,~\beta=1$} & {\footnotesize (b) $m=1,~\beta=10$} \\
        \includegraphics[width=0.21\textwidth]{"heatmap/BarabasiAlbert_1_01"} &
        \includegraphics[width=0.21\textwidth]{"heatmap/BarabasiAlbert_1_10"} \\
        {\footnotesize (c) $m=5,~\beta=1$} & {\footnotesize (d) $m=5,~\beta=10$} \\
        \includegraphics[width=0.21\textwidth]{"heatmap/BarabasiAlbert_5_01"} &
        \includegraphics[width=0.21\textwidth]{"heatmap/BarabasiAlbert_5_10"}
    \end{tabular}
    \caption{\label{fig:ba}
    $\overline{AUC}$ heatmaps for games played on \BA random graphs. Each row corresponds to a different connection parameter $m\in\{1,5\}$, while the columns refer to the rule parameter used by the agents $\beta\in\{1,10\}$. Each point in the plot corresponds to a different game parameterized as in \cref{eq:game} by $S$ and $T$. For each game, $100$ random graphs were selected and an average ROC curve was generated. The color represents how much the $AUC$ under the mean curve differs from the uniformly random predictor as in \cref{eq:aucbar}. \\}
\end{figure}

There are a number of notable features apparent in \cref{fig:ba}. The plots are roughly symmetric across their diagonals so that opposite quadrants have similar characteristics. The nice thing about these $S$-$T$ parameterization is that each of the quadrants corresponds to a common two-player, two-strategy, symmetric game. Counter-clockwise from the top-right quadrant, the games are \mbox{\textit{Hawk-Dove}}, \textit{Harmony}, \mbox{\textit{Stag-Hunt}} and \textit{Prisoner's Dilemma}. The interesting point to note is that the games opposite one another have the same number of pure-strategy Nash equilibria: Harmony and Prisoner's Dilemma each have one while \mbox{Hawk-Dove} and \mbox{Stag-Hunt} have two. On its face, this may not appear to be relevant to the problem of inferring the topology of the graph. However, the Nash equilibria play a crucial role given how the agents are updating their strategies: over time, the agents tend to settle on playing an equilibrium strategy. This process happens fairly quickly, typically within the \mbox{$10$ rounds} of play simulated in this study. In effect, the simulations of the Harmony and Prisoner's Dilemma reach equilibrium and remain there, though with some amount of noise induced by the agents' strategy update rule. However, the transition to equilibrium takes longer for \mbox{Hawk-Dove} and \mbox{Stag-Hunt} because they have two equilibria. The resulting time series then provides more information about the interactions between agents. One additional factor to consider here is that in the two-equilibrium games, it is possible for domains to form wherein agents in a given domain all play the same equilibrium strategy while agents in neighboring domains play a different strategy. The stability of these domains and the impact they have on the graph inference problem is something to be investigated in future work.

One apparent problem with the above interpretation is it suggests that each of the four quadrants of the heatmap should be filled with the same $\overline{AUC}$ value, e.g. that every harmony game should have the same $\overline{AUC} \sim 0$. Of course, that is clearly not the case (\cref{fig:ba}(a)). Notice though that the classification improves as the game moves away from the negatively-slopped diagonal within the Harmony and Prisoner's Dilemma quadrants. This effect is due to the agents using a stochastic update rule which is dependent on the difference in payoffs of two strategies. As the game moves further from the negatively-slopped diagonal, the payoff differences make differentiating between the strategies more difficult in games where there is only one equilibrium. As a result, the agents spend more time in transition to equilibrium and consequently provide more information about the topology of the graph. If this analysis is correct, we should expect to see that increasing the rule parameter $\beta$ allows the agents to differentiate smaller payoff differences, and the quadrants of these heatmaps should tend to become more homogeneous. This is exactly what we see, particularly when edge density of the graphs is low (\cref{fig:ba}, \cref{fig:er} and \cref{fig:fixed}).

\begin{figure}[!t]
    \begin{tabular}{cc}
        {\footnotesize (a) $p=0.04,~\beta=1$} & {\footnotesize (b) $p=0.04,~\beta=10$} \\
        \includegraphics[width=0.21\textwidth]{"heatmap/ErdosRenyi_0.04_01"} &
        \includegraphics[width=0.21\textwidth]{"heatmap/ErdosRenyi_0.04_10"} \\
        {\footnotesize (c) $p=0.18,~\beta=1$} & {\footnotesize (d) $p=0.18,~\beta=10$} \\
        \includegraphics[width=0.21\textwidth]{"heatmap/ErdosRenyi_0.18_01"} &
        \includegraphics[width=0.21\textwidth]{"heatmap/ErdosRenyi_0.18_10"}
    \end{tabular}
    \caption{\label{fig:er}
    $\overline{AUC}$ heatmaps for games played on \ER random graphs. Each row corresponds to a different connection probability $p\in\{0.04,0.18\}$, while the columns refer to the rule parameter used by the agents $\beta\in\{1,10\}$.\\}
\end{figure}

\begin{figure}[!h]
    \begin{tabular}{cc}
        {\footnotesize (a) Cycle, $\beta=1$} & {\footnotesize (b) Cycle, $\beta=10$} \\
        \includegraphics[width=0.21\textwidth]{"heatmap/Cycle_01"} &
        \includegraphics[width=0.21\textwidth]{"heatmap/Cycle_10"} \\
        {\footnotesize (c) Lattice, $\beta=1$} & {\footnotesize (d) Lattice, $\beta=10$} \\
        \includegraphics[width=0.21\textwidth]{"heatmap/Lattice_01"} &
        \includegraphics[width=0.21\textwidth]{"heatmap/Lattice_10"} \\
        {\footnotesize (e) Wheel, $\beta=1$} & {\footnotesize (f) Wheel, $\beta=10$} \\
        \includegraphics[width=0.21\textwidth]{"heatmap/Wheel_01"} &
        \includegraphics[width=0.21\textwidth]{"heatmap/Wheel_10"}
    \end{tabular}
    \caption{\label{fig:fixed}
    $\overline{AUC}$ heatmaps for games played on the cycle, wheel and lattice topologies. Each row corresponds to a different topology while the columns refer to the rule parameter used by the agents $\beta\in\{1,10\}$. The edge density of the topologies increases down the column, i.e. the cycle has fewer edges than the lattice which has fewer edges than the wheel. \\}
\end{figure}

This brings us to the final factor involved in determining the efficacy of the classification: the edge density of the graph. When we compare, for example, the \BAbox graphs with $m=1$ (\cref{fig:ba}(a-b)) to the \ERbox graphs with $p=0.04$ (\cref{fig:er}(a-b)), we see almost identical structure in the $\overline{AUC}$ heatmaps. On average the \ERbox graphs have the same edge density to their \BAbox counterparts, i.e. they have about the same number of edges. The cycle graph (\cref{fig:fixed}(a-b)) has the same edge density to the \BAbox graph (\mbox{$m=1$}), and again we see almost identical heatmaps. By increasing the edge parameters for the \BAbox and \ERbox graphs, $m$ and $p$ respectively, we can see a similar comparison for yet denser graphs (\mbox{\cref{fig:ba}(c-d)} and \mbox{\cref{fig:er}(c-d)}). Again, the \BAbox ($m=5$) and \ERbox ($p=0.18$) graphs have similar edge density. What's more, the same qualitative change is seen for a single type of topology when the edge density changes. For example, comparing \cref{fig:ba}(a) to \ref{fig:ba}(c) or \cref{fig:er}(a) to \ref{fig:er}(c), we see fewer harmony and prisoner's dilemma games admit a faithful inference. The same phenomenon is observed in comparing cycles, lattices and wheels (\cref{fig:fixed}), which further supports the claim. The graphs have remarkably distinct topologies even with only $50$-nodes. For example, it is difficult to find any similarity between the \BAbox and cycle graphs other than edge density. However, it is entirely plausible that some other topological similarity between the graphs is causing these effects. Increasing the size of the graph should lead to increasingly divergent topological features. That would allow us to test this claim more fully.

\section{Conclusion}\label{sec:conclusion}

From all of these results, however incomplete, we can begin to draw some insight. It seems profoundly important that in order to be confident that the reconstructed topology -- that is the inferred causal structure of the system -- is the actual topology, an outside observer must be privy to the inner workings of the agents. What game are they playing, and how are they deciding which strategy to use next? Of course, the simple retort to this is that reconstructions are failing for the one-equilibrium games because the time series are not diverse enough. If the observer could assess this in advance, it might temper or bolster their confidence. However, it cannot be understated that the rule parameter plays some role in the diversity of the time series. If the rule is too stochastic, the time series will be riddled with \textit{biased} noise. One possibility is to use similar information-theoretic tools to infer which game is being played. It's been shown in previous work that dynamical agents operating under different rules show distinct patterns of information transfer \citep{Valentini2018-qb}. If the observer could first apply such a method to determine the game\footnote{It may not be necessary to know precisely which game is being played. Perhaps knowing the number of equilibria is sufficient?}, rule, and noise profile, they may be able to yield more faithful reconstructions of the topology.

From here there are a number of avenues for further research. The mutual information is a somewhat simplistic measure for applications like this. We chose it in part because of this simplicity. Two alternative measures, for example, might be conditional mutual information (CMI) or transfer entropy (TE), \citep{Schreiber2000-ir}. In preliminary work, we briefly explored both. The conditional mutual information approach was problematic in that it required more substantial computational overhead than we had available at the time. One method of using CMI is to compute $I(s_i^+,s_j|\bm{s}_{ij})$ where $\bm{s}_{ij} = \{s_k | k \ne i, k \ne j\}$, that is to say condition the pair-wise mutual information on the strategies of all other agents. Since our graphs have $50$ nodes, that computation was infeasible using direct approaches. Alternative methods of computing CMI, such as the iterative approaches of \citep{Lizier2012-nf,Sun2015-xs}, may make it viable for future work. Transfer entropy is a special case of CMI; it would condition on the target agent's previous strategies. Both approaches are worth exploring more rigorously.

In this work, we were interested in methods that required only one only observe a system and not intervene on it, as in many cases only observation is accessible to the researcher. However, it is well understood that observation alone, particularly in the case of large systems wherein only a small portion of the state space can be explored, is inadequate for extracting causal relationships between components of a system. Interventional methods, such as \citep{Ay2008-jc}, are much more effective in such cases, provided you have the ability to control aspects of the system. Subsequent work may explore such an approach.

The dynamics of the models we considered here are similar in many respects to the classic Ising model, with $\beta$ acting much like temperature and the payoff matrix \cref{eq:game} behaving similarly to interaction strengths. It is reasonable to expect that analogues of heat capacity, entropy, and other thermodynamic measures could be related in some way to the effectiveness of the network inference. Comparing the AUC with some of these thermodynamic analogues is a possibility for a future work.

Another advance could be to look at other methods of quantifying the efficacy of the edge classifications. As the reader may have noticed, we never considered complete graphs. The reason for this is that to construct the ROC curves, you have to compute the false-positive rate. This value is undefined if your dataset has no negative cases. In our application, that means there must be pairs of agents that are not connected.

Two of the most egregious assumptions we've made in this work are that every agent is using the same rule to update its strategy, and every pair of agents is playing the same game. There is little reason to expect that real-world systems behave in this manner, and either assumption can be relaxed. For example, we could associate a different game with each edge. We have no expectation for how this would affect the results, but will explore it in the future.

Finally, as with virtually every simulation study, there is room for more fine-grained parameter sweeps. Our sampling of the $S$-$T$ space of games was rather coarse; we limited ourselves to an unreasonably small number of initial conditions ($100$ of the $2^{50}$ possible) for each graph, and we considered only a handful of graph topologies. All of this will be greatly expanded in future work.

Ultimately, we see that the difference in functional and actual connectivity can sometimes be tied directly to the dynamical structure of the system. It may be impossible to know how similar the functional and actual connectivity of these types of networks are without detailed knowledge of the dynamics of the agents in the system. This may not be a surprise to some, but it is important that researchers to acknowledge it explicitly. Without that, it can be all too easy to blindly apply these network inference methods and over interpret the results, a sin of which at least the first author is guilty.

\section{Acknowledgements}
D.G.M. and S.I.W. would like to acknowledge the Lifelong Learning Machines program from DARPA/MTO for funding this work. D.G.M also acknowledges Cole Mathis for the conversations about game theory which inspired this work.

\footnotesize
\bibliographystyle{apalike}
\bibliography{gomen.bib}

\end{document}
